### 2021-02-18 outputs/paper/paper.Rmd
Commit for intervention decision

---
title: "COVID Shutdown Regulations on Restaurants Decreases xx% of Average Total Sales in Ontario"
author: "Hong Shi, Hong Pan, Yixin Guan"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Since 2020, the world-wide COVID-19 pandemic has greatly influenced public health and healthcare, resulting in governments to impose regulations on social gatherings to eliminate further outbreaks. In Ontario, the provincewide stay at home order and shutdown restrictions on businesses and facilities has limited economic activities into a recession. This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months reopening. The experiment results show that shutdown regulations on restaurants have decresed xxx%....."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

# Introduction

1. show current covid situations and policy regulations from world wide perspective to Ontario specific.

2. some context of economics effects on Ontario, preferably specific to covid effect on restaurant

3. however, current data include not only the shutdown effect, but also the covid effect (counterfeit counterfactual), Inferring causality will require that you rule out other potential factors that could have affected the outcome under consideration.(close of restaurants etc.) Does not make sense to compare the restaurant situations before COVID and during COVID.

4. As a result, to give an accurate estimate of the counterfactual, we need to identify the treatment & control group (2 cities) under current COVID outbreak, with similar restaurant operating situations. We selected Peterborough and Brantford.(could leave this part to discussion)
SAME IN 3 WAYS: (1).avg characteristics identical (through )
 (2). treatment should not affect the comparison group either directly or indirectly ( by city distance of 200+ km unlikely to travel to another city for a meal) However, there might be overestimate of the reopening effect on restaurants since people living near Peterborough while still having their regions' restaurants shutdown might choose to go to Peterborough, increasing sales of Peterborough restaurants.
 (3). Outcome of units in control group should change the same way as outcomes in treatment group (e.g. Provincial subsidy applied to the whole Ontario restaurant business)

Sampling methods and randomizations: Yixin

Data & Survey:
Discussioin Part:
1.Summarize, then
2. mention the selection of cities (limitations)
3. sampling methods (limitations)
4. Need to address internal validity and external validity
Internal validity:Internal validity means that the estimated impact of the program is
net of all other potential confounding factors—or, in other words, that
the comparison group provides an accurate estimate of the counterfactual,
so that we are estimating the true impact of the program.
Basically true since the selection of these two cities ensures the similarity in turn of either city size , population, etc. and restaurant operating situation (through ).

External validity:
External validity means that the evaluation sample accurately represents
the population of eligible units.

Somehow limited, results may not be extrapolated to the entire population of interest, i.e. Restaurant all over Ontario. This is a single-tier relative small size city level experiment. May not generalized to townships, or cosmopolitan city like Toronto...

5. Tradeoff between reopening (economy) and covid cases (public health and healthcare). Should carefully consider....

# Data
```{r}
citation("cansim")
```

&nbsp; &nbsp; Our data explores shutdown effects on restaurant businesses in Ontario. We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `scales` [@cite_scales], `here` [@cite_here]. We used R packages `cansim` [@cite_cansim] and packagesxxx to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra] to format the document.
## Intervention

&nbsp; &nbsp; Partnered with the Ontario government, we want to examine the shutdown effects on restaurant businesses in Ontario. The plan of the experimental design was to reopen all restaurants (i.e. enable the dine-in option) in particular Ontario regions, while enforcing current provincewide shutdown restrictions (i.e. disable the dine-in option) on restaurants in the rest of Ontario regions. And after the three-month reopening, we compare restaurant operating situations in reopened regions with those in shutdown regions through data collected from online surveys of restaurant owners.

&nbsp; &nbsp; However, due to current COVID pandemic, any loosening of shutdown restrictions increases chances of COVID exposures, resulting in challenges on public health and healthcare of reopened regions. It is highly risky and hasty to reopen a large area of Ontario regions for the sole purpose of our experiment. Therefore, we mindfully chose Peterborough, a relative small size Single-tier^[Ontario's Municipal Act, 2001 defines a single-tier municipality as "a municipality, other than an upper-tier municipality, that does not form part of an upper-tier municipality for municipal purposes"] city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population. Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns. In our experiment, we assigned restaurants in Peterborough as the treatment group and those in Brantford as the control group. We also ensured restaurants within these two cities to have equal opportunities receiving government support (e.g. subsidies, grants, etc.) to estimate the true impact of shutdown effects on restaurant businesses after three-month reopening in Peterborough.

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

# Appendix {-}

\newpage

# References

### 2021-02-18 scripts/2178 draft.Rmd
Commit for intervention decision

---
title: 
author: "Hong Pan"
date: "`r format(Sys.time(), '%d %B %Y')`"

abstract: 
thanks: 'Code and data are available at: https://github.com/HongTrista/folder.'
bibliography: references.bib

output:
  bookdown::pdf_document2:
  toc: no

header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}
---

```{r}
#### Workspace setup ####
# install.packages("ggplot2")
library(ggplot2) #for drawing nice figures

#install.packages("ggpubr")
library(ggpubr) #for combing figures in one graph

#install.packages("knitr")
library(knitr) # create table

# install.packages("tidyverse")
library(tidyverse) #filter dataset

install.packages("kableExtra")
library(kableExtra)# position of table

```

#import dataset
```{r}
simulated_dataset<-read_csv('~/Desktop/simulated_data.csv')
```

# layoff

```{r}

ggarrange(p1, p2, ncol = 2, nrow = 1)

simulated_dataset%>%
  ggplot(aes(q3_layoff, fill =q1_city)) + 
  geom_bar(position = "dodge")+
  facet_wrap(~q2_type)+
  ylab("Number of responses")+
  xlab("Number of laid-offs")+
  ggtitle('Layoff situation in Peterborough')+
  theme_minimal()

#Takeaways: 
#1. Brantford(shutdown city): overall, except for the value of 0, other levels are all larger than Peterborough. 
# By segment, although quick service type has a higher number to lay off 1 to 4 employees, it has a lower number of laying more than 10  and a higher number of without laying people.

#2. Peterborough(reopen city): In both types of services, the highest proportion of without firing people. However, table-services perform worse than quick-services.
#3. Conclude: Brantford is suffering from Covid 19
```

#total sales & revenue & cost

```{r}
#total sales
simulated_dataset%>%
  ggplot(aes(q4_total_sales, fill =q1_city)) + 
  geom_bar(position = "dodge")+
  ylab("Number of responses")+
  xlab("Total sales")+
  ggtitle('The total sales in the two cities compared to the previous month')+
  scale_x_discrete(limits = c("Lose more than 10%", "Lose 5% ~ 10%", "Roughly unchanged","Earn 5% ~ 10%","Earn more than 10%"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90))

#revenue
simulated_dataset%>%
  ggplot(aes(q6_revenue, fill =q1_city)) + 
  geom_bar(position = "dodge")+
  ylab("Number of responses")+
  xlab("Revenue")+
  ggtitle('Revenue changes due to covid 19')+
  scale_x_discrete(limits = c("Decreased more than 25%", "Decreased by 5% – 25%", "Roughly unchanged","Increased by  5% – 25%",
                              "Increased more than 25%","Prefer not to say"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90))

#Cost:

simulated_dataset%>%
  ggplot(aes(q11_cost, fill =q1_city)) + 
  geom_bar(position = "dodge")+
  ylab("Number of responses")+
  xlab("Cost")+
  ggtitle('Degree of cost increase')+
  scale_x_discrete(limits = c("0 – 25%", "25% - 50%", "More than 50%","Our costs have decreased after the pandemic",
                              "Prefer not to say"))+
  theme_minimal()+
   theme(axis.text.x = element_text(angle = 90))

#Takeaways (total sales):
#1. In Brantford, the vast majority of restaurants are losing money more than 5% compared to last month's sales.
#2. In Peterborough (Peterborough), a large proportion of restaurants have started to get bettered, and most restaurants can maintain the status of the previous month and even start to earn income.

#Takeaways(revenue):
#Although there are some positives responses, most of the restaurants have lost revenue to a certain extent. Especially in Brantford, the entire city is shut down, and most restaurants lose more than 25%. Although the situation in Peterborough is better by comparison, most restaurants have lost revenue from 5%-25%.

#Takeaways(cost):
#Two cities have a very close result, but overall, around 80% of the restaurant's responses that their cost has increased. And, the highest proportion replies their cost increased within 25%.

#Conclude:
# Although most restaurants in the two cities suffer from the pandemic, reopened can help the restaurant reduce their pressure to some extent.

```

```{r}
#Peterborough
p_table <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q4_total_sales))%>%
  mutate(pct=round(Freq/sum(Freq)*100))

label_p<-paste(p_table$Var1,p_table$pct)%>%
  paste("%",sep = "")
#pie(slices,labels = label_p,col=rainbow(length(label_p)),
   # main = "Pie chart of total sales in Peterborough")

#Brantford
b_table <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q4_total_sales))%>%
  mutate(pct=round(Freq/sum(Freq)*100))

label_b<-paste(b_table$Var1,b_table$pct)%>%
  paste("%",sep = "")
#pie(slices,labels = label_p,col=rainbow(length(label_p)),
    #main = "Pie chart of total sales in Brantford")

#Side-By-Side Pie Charts
par(mfrow = c(1,3))
pie(p_table$Freq,labels = label_p,col=rainbow(length(label_p)),
    main = "Pie chart of total sales in Peterborough",cex=0.6,cex.main=1)
pie(b_table$Freq,labels = label_b,col=rainbow(length(label_b)),
    main = "Pie chart of total sales in Brantford",cex=0.6,cex.main=1)

#Takeaways:

```

#survival

```{r}

data.frame(table(simulated_dataset$q7_survive,simulated_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var1)) +
    geom_bar(stat = "identity")+
  facet_wrap(~Var2)+
  theme(axis.text.x = element_text(angle = 90))+
  scale_x_discrete(limits = c("Less than 3 months", "3 to 6 months", "Longer than 6 months","Unknown","Prefer not to say"))+
  ylab("Number of responses")+
  xlab("Expected survival time")

#Takeaways:
# 40% of restaurants in Brantford need help! The data clearly shows many restaurants are quickly approaching permanent closures. We are now two months into the shutdown, which is too late for many, but countless companies can still be saved if we move fast enough to help them.

# The situation in Peterborough is much better. Around half of the restaurants said they would survive more than 6 months.

```

# operation
```{r}
simulated_dataset%>%
  ggplot(aes(q8_operation, fill =q1_city)) + 
  geom_bar()+
  facet_wrap(~q2_type)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of responses")+
  xlab("Cost")+
  ggtitle('Current profitability of overall operation')+
  scale_x_discrete(limits = c("Operating at a loss", "Breaking even", "Profit between 0% and 2%","Profit between 2% and 5%","Profit of 5% or more","Prefer not to say"))

simulated_dataset%>%
  ggplot(aes(q8_operation, fill =q1_city)) + 
  geom_bar(position = "dodge")+
  facet_wrap(~q2_type)+
  ylab("Number of responses")+
  xlab("Cost")+
  ggtitle('Current profitability of overall operation')+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_x_discrete(limits = c("Operating at a loss", "Breaking even", "Profit between 0% and 2%","Profit between 2% and 5%","Profit of 5% or more","Prefer not to say"))

#Takeaways:
# Table-service restaurants more suffer in shut down city.

```

#q9:recover
```{r}
#need to reorder the column in table
t1<-simulated_dataset%>%
  filter(q1_city=="Peterborough")

table(t1$q13_CEWS,t1$q9_recover)%>%
  prop.table()%>%
  kable("html", align = 'clc', caption = 'Peterborough')%>%
  kable_styling(full_width = F, position = "float_left")

t2<-simulated_dataset%>%
  filter(q1_city=='Brantford')

table(t2$q13_CEWS,t2$q9_recover)%>%
  prop.table()%>%
  kable("html", align = 'clc', caption = 'Brantford')%>%
  kable_styling(full_width = F, position = "right")

#Takeaway:
#1. For both cities, we can see that around 35% of the restaurants that received wage subsidies said they would back to normal operation before between a year and 18 months, followed by around 12% of restaurants that said they need 7-12 months to recover.
#This illustrates how much the pandemic has hit the foodservice industry.

#2. Under the circumstance of receiving a wage subsidy, comparing Peterborough with Brantford, we can see that Peterborough has a higher percentage indicating that they will recover in less than 6 months. 
```

#q12: government support
```{r}
p3<-simulated_dataset%>%
  filter(simulated_dataset$q1_city=="Peterborough")%>%
  ggplot(aes(q12_support, fill =q12_support)) + 
  geom_bar()+
  facet_wrap(~q2_type)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of responses")+
  xlab("Need government support or not")+
  ggtitle('Peterborough: whether need support')+
  scale_x_discrete(limits = c("Yes", "No", "I do not know"))+
  ylim(0,25)

p4<-simulated_dataset%>%
  filter(simulated_dataset$q1_city=="Brantford")%>%
  ggplot(aes(q12_support, fill =q12_support)) + 
  geom_bar()+
  facet_wrap(~q2_type)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of responses")+
  xlab("Need government support or not")+
  ggtitle('Brantford: whether need support')+
  scale_x_discrete(limits = c("Yes", "No", "I do not know"))+
  ylim(0,25)

ggarrange(p3, p4, ncol = 2, nrow = 1)

#Takeaway:
#For both cities, in the face of these pressing financial challenges, this is not surprising that around 60% of survey respondents said their foodservice business requires additional financial support. By segment, table-service restaurants and quick-service restaurant's situations are quite similar in Peterborough.  But in Brantford, we can see table service restaurants are suffering from the city shutdown and more difficulty than quick-service restaurants.

```

### 2021-02-18 scripts/test_script.Rmd
Commit for intervention decision

---
title: "Test script"
author: "Hong Shi"
date: "2/8/2021"
output: pdf_document
---
```{r}
library(tidyverse)
library(rvest)
```
```{r}
raw_data <- read_html("https://en.wikipedia.org/wiki/List_of_cities_in_Ontario")
write_html(raw_data, "inputs/wiki/ontariocities.html")
```
```{r}
#Read in our saved data
raw_data <- read_html("inputs/wiki/ontariocities.html")
parse_data_inspection <- 
  raw_data %>% 
  html_nodes("td:nth-child(7) , .headerSort:nth-child(7) , td:nth-child(8) , td:nth-child(4) , td:nth-child(3) , td:nth-child(2) , td:nth-child(1) , .headerSort:nth-child(8) , .headerSort:nth-child(4) , .headerSort:nth-child(3) , .headerSort:nth-child(2) , .headerSort:nth-child(1)") %>% 
  html_text()

```

```{r}
head(parse_data_inspection,18)
```
```{r}
parse_data_inspection
parse_data_inspection2 <- slice(parse_data_inspection, 1:312)
```

```{r}
class(parse_data_inspection)
```

```{r}
parsed_data <- tibble(raw_text = parse_data_inspection) %>% 
  slice(1:312)
parsed_data
```
```{r}
spread(parsed_data, key = "raw_text")
```

```{r}
library(tidyr)
```
```{r}
df_long <- pivot_longer()
```

```{r}
df <- tibble(
  x = 1:3,
  y = c("a", "d,e,f", "g,h"),
  z = c("1", "2,3,4", "5,6")
)
df
```

### 2021-02-18 scripts/ver2_test_script.Rmd
Commit for intervention decision

---
title: "STATCAN_test"
author: "Hong Shi"
date: "2/12/2021"
output: pdf_document
---

```{r}
library(tidyverse)
library(here)
```

```{r}

```

```{r}
# We get the Employment by industry, annual, census metropolitan areas from Statistics Canada:
# https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=1410009801
# install.packages("cansim")
library(cansim)
library(ggrepel)
statscan_employment <- get_cansim("282-0131") # This is the CANSIM table code of the employment data 
```
```{r}
# have a glance of the data
head(statscan_employment)
```

```{r}
# save the raw data of Employment by industry, annual, census metropolitan areas 
write_csv(statscan_employment, here::here("inputs/data/raw_statscan_employment.csv"))
```
```{r}
statscan_employment <- readr::read_csv(here::here("inputs/data/raw_statscan_employment.csv"))
```

```{r}
# We would like to filter out the employment information:
# 1. In Ontario, 
# 2. Belongs to accommodation and food services category according to (NAICS) the North American Industry Classification System
# 3. In 2016 ( since we would use population density data in 2016 to perform city selection as treatment city and control city)
cleaned_statscan_employment <- 
  statscan_employment %>% 
  filter(
    grepl("Ontario", statscan_employment$GEO) &
    grepl("Accommodation and food services", statscan_employment$`North American Industry Classification System (NAICS)`) &
    grepl("^2016", statscan_employment$REF_DATE)
    )
# save the cleaned data
write_csv(cleaned_statscan_employment, here::here("inputs/data/cleaned_statscan_employment.csv"))
```

```{r}
# Read in the Population and Dwelling Count Highlight Tables, 2016 Census downloaded from Statistics Canada
# to get the population density data
# Link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/hlt-fst/pd-pl/Table.cfm?Lang=Eng&T=311&SR=1&S=87&O=A&RPP=9999&PR=35#details-panel2
# Note: We applied the filter on geography: provinces and territories to Ontario
raw_2016_census <- readr::read_csv(here::here("inputs/data/T31120210212123500.CSV")) # The original name of Population and Dwelling Count Highlight Tables, 2016 Census from Statistics Canada
```
```{r}
# We would like to filter out the census information:
# 1. In "City" of the CSD, DPL (census subdivision, designated place) type
cleaned_2016_census <- 
  raw_2016_census %>% 
  filter(
    grepl("City", raw_2016_census$`CSD, DPL Type`) 
    )
```

## Part 2 intervention decision

```{r}
# compare the number of observations between the cleaned_statscan_employment dataset and the cleaned_2016_census dataset
count(cleaned_statscan_employment) < count(cleaned_2016_census)
# We notice that the employment information is not available for all cities in the employment by industry dataset. 
# So we have to select the treatment city and the control city with employment information available
select_employment <- 
  cleaned_statscan_employment %>% 
  select(GEO, VALUE) %>% 
  filter(GEO != "Ottawa-Gatineau, Ontario/Quebec" & GEO != "Ottawa-Gatineau, Quebec part, Ontario/Quebec")
# Remove the Gatineau employment data since it is out of Ontario province

# We notice that the NAICS data about employment could be collected in city groups ( e.g. St. Catharines and Niagara are collected in a single subgroup)
city_groups <-
  cleaned_statscan_employment %>% 
  filter(grepl("-", cleaned_statscan_employment$GEO)) # Cities within the city group are separated by "-"
head(city_groups)

# So instead of directly using the Population density per square kilometer, we would like to select "the Land area in square kilometres, 2016" and "Population, 2016" to calculate the the weighted average of population density in the city groups.
select_census_poparea <- 
  cleaned_2016_census %>% 
  select( City = `Geographic name`, Population = `Population, 2016`, Area = `Land area in square kilometres, 2016`)
head(select_census_poparea)

select_census <- 
   cleaned_2016_census %>% 
  select( City = `Geographic name`, Population_Density = `Population density per square kilometre, 2016`)
head(select_census)
```

```{r}
library(stringr)
```

```{r}
# split the column name in select_employment dataset to remove "Ontario" province separated by comma
select_employment$City <- str_split_fixed(select_employment$GEO, ",", 2)[,1] #[,1] means to only keeps the city names column
# Drop the GEO column 
# Ref link to drop the column: https://stackoverflow.com/questions/6286313/remove-an-entire-column-from-a-data-frame-in-r
select_employment$GEO <- NULL

# change Ottawa-Gatineau into Ottawa since already removed Gatineau 
# Ref link to reassign value:https://www.edureka.co/community/35430/how-change-the-value-variable-using-programming-data-frame
select_employment$City[select_employment$City == "Ottawa-Gatineau"] <- "Ottawa"

unique(cleaned_statscan_employment$SCALAR_FACTOR)
# Multiply the employment value by 1000 since the scalar factor is in thousands 
select_employment$Employment <- select_employment$VALUE * 1000
# Drop the VALUE column
select_employment$VALUE <- NULL
select_employment
```
```{r}
# We would manually sum up the population and land area of 
# 1. St. Catharines and Niagara
# 2. Kitchener, Cambridge, and Waterloo
# And then calculate the population density of cities, including these city groups
# Ref link to add observations to a data frame: https://www.dummies.com/programming/r/how-to-add-observations-to-a-data-frame-in-r/

Catharines_Niagara <-
  select_census %>% 
  filter( City == "St. Catharines" | City == "Niagara Falls")

Catharines_Niagara
select_census <- 
  rbind(select_employment, c(
    "St. Catharines-Niagara",

  ))

```

```{r}
# join two dataset to create a dataset that contains cities with population density and employment in Accommodation and food services available 
popdensity_employment <- merge(select_census, select_employment, by = "City")
popdensity_employment
```

```{r}
# Plot a Employment vs Population Density graph to detect cities with similar restaurant operating situation 
# (i.e. number of people served by restaurant staffs per square kilometers) by finding cities located closed to data points 
# 
ggplot( data = popdensity_employment, mapping = aes(x = Employment, y = Population_Density)) +
  geom_point( )+
  theme_minimal() + 
  geom_label_repel(aes( label = City)) +
  geom_smooth( method = "lm", formula = y~x)
```

```{r}
# The figure shows that Toronto has very high population density and employment in accommodation and food services, and it makes sense that Toronto is the most populous city in Canada
# Since we would like to select two cities with similar population density and employment as the treatment and control group, we remove Toronto from the graph due to no comparable restaurant operating situation with other cities.
popdensity_employment <- 
  popdensity_employment %>% 
  filter( City !="Toronto")

ggplot( data = popdensity_employment, mapping = aes(x = Employment, y = Population_Density)) +
  geom_point( )+
  theme_minimal() + 
  geom_label_repel(aes( label = City)) 
  #geom_smooth( method = "lm", formula = y~x)
#ggsave("city_selection.png")
```

```{r}
popdensity_employment$density_employment <- 
  popdensity_employment$Population_Density/ popdensity_employment$Employment
popdensity_employment
```
```{r}
# we would also like to compare the similarity between Brantford and Peterborough in turns of population and land area
select_census_poparea %>% 
  filter( City == "Brantford"| City == "Peterborough")
# The result shows that Brantford and Peterborough are similar cities in turns of population and area, expect that Brantford is slightly bigger and populus
```

```{r}
library(rvest)
```
```{r}
raw_census_data <- read_html("https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/hlt-fst/pd-pl/Table.cfm?Lang=Eng&T=311&SR=1&S=87&O=A&RPP=9999&PR=35#details-panel2")
write_html(raw_census_data, here("inputs/htmls/census.html"))
```

```{r}
parse_census_data <- 
  raw_census_data %>% 
  html_nodes("#COLGROUP2 , #COLGROUP1 , .text-left , #tablesort div , #tPopDwell .text-right") %>% 
  html_text()
```

```{r}
head(parse_census_data,100)
```

### 2021-02-18 scripts/00_cansim_employment_data_import.R

@@ -1,0 +1,33 @@
+#### Preamble ####
+# Purpose: Use cansim to get the employment by industry, annual, census metropolitan areas data
+# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
+# Date:  20 February 2021
+# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+
+
+#### Workspace set-up ####
+
+# Get data from Statistics Canada through package cansim
+
+# install.packages("cansim")
+
+library(tidyverse)
+library(cansim)
+library(here)
+
+
+#### Get Data ####
+
+# We get the Employment by industry, annual, census metropolitan areas from Statistics Canada:
+# https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=1410009801
+
+statscan_employment <- get_cansim("282-0131") # This is the CANSIM table code of the employment data 
+
+# have a glance of the data
+head(statscan_employment)
+
+# save the raw data of Employment by industry, annual, census metropolitan areas 
+write_csv(statscan_employment, here::here("inputs/data/raw_statscan_employment.csv"))
+

### 2021-02-18 scripts/01_employment_census_data_cleaning.R

@@ -1,0 +1,68 @@
+#### Preamble ####
+# Purpose: Clean the cansim employment data and the Canadian 2016 census data
+# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
+# Date:  20 February 2021
+# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# 1. Need to have downloaded the raw data in "00_cansim_employment_data_import.R" and saved it to inputs/data
+# 2. Need to have downloaded the Population and Dwelling Count Highlight Tables, 2016 Census data from Statistics Canada
+#    with the filter on geography: provinces and territories to Ontario and save "T31120210212123500.CSV" to inputs/data
+
+#### Workspace setup ####
+
+library(tidyverse)
+library(here)
+
+
+#### Read in the raw data ####
+
+# The NAICS employment data
+statscan_employment <- readr::read_csv(here::here("inputs/data/raw_statscan_employment.csv"))
+
+# Read in the Population and Dwelling Count Highlight Tables, 2016 Census downloaded from Statistics Canada
+
+# Unfortunately, we did not find a convenient way to scape (Requires many manipulations of cleanning data) 
+# or directly load the 2016 Cencus data in R
+# so we manually downloaded the data from Statistics Canada and saved it into inputs/data 
+# The name of the original table is "T31120210212123500.CSV"
+
+# Link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/hlt-fst/pd-pl/Table.cfm?Lang=Eng&T=311&SR=1&S=87&O=A&RPP=9999&PR=35#details-panel2
+# Note: We applied the filter on geography: provinces and territories to Ontario
+
+raw_2016_census <- readr::read_csv(here::here("inputs/data/T31120210212123500.CSV")) 
+
+
+#### Data cleaning ####
+
+# For NAICS employment data
+
+# We would like to filter out the employment information:
+# 1. In Ontario, 
+# 2. Belongs to accommodation and food services category according to (NAICS) the North American Industry Classification System
+# 3. In 2016 ( since we would use population density data in 2016 to perform city selection as treatment city and control city)
+cleaned_statscan_employment <- 
+  statscan_employment %>% 
+  filter(
+    grepl("Ontario", statscan_employment$GEO) &
[…]

### 2021-02-18 scripts/02_city_selection.R

@@ -1,0 +1,136 @@
+#### Preamble ####
+# Purpose: Provide codes for selecting two similar cities as the treatment group (reopen city) and the control group (shutdown city)
+# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
+# Date:  20 February 2021
+# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded the cleaned employment data and census data in "01_employment_census_data_cleaning.R" 
+#   and saved it to inputs/data
+
+#### Workspace setup ####
+
+library(tidyverse)
+library(here)
+library(ggrepel)
+library(stringr)
+
+# Read in the cleaned data
+
+# Employment data
+cleaned_statscan_employment <- readr::read_csv(here::here("inputs/data/cleaned_statscan_employment.csv"))
+  
+# Census data
+
+cleaned_2016_census <- readr::read_csv(here::here("inputs/data/cleaned_2016_census.csv"))
+
+
+#### City selection ####
+
+# compare the number of observations between the cleaned_statscan_employment dataset and the cleaned_2016_census dataset
+
+count(cleaned_statscan_employment) < count(cleaned_2016_census)
+
+# We notice that the employment information is not available for all cities in the employment by industry dataset. 
+# So we have to select the treatment city and the control city with employment information available
+select_employment <- 
+  cleaned_statscan_employment %>% 
+  select(GEO, VALUE) %>% 
+  filter(GEO != "Ottawa-Gatineau, Ontario/Quebec" & GEO != "Ottawa-Gatineau, Quebec part, Ontario/Quebec")
+# Remove the Gatineau employment data since it is out of Ontario province
+
+
+# We notice that the NAICS data about employment could be collected in city groups 
+# ( e.g. St. Catharines and Niagara are collected in a single subgroup)
+city_groups <-
+  cleaned_statscan_employment %>% 
+  filter(grepl("-", cleaned_statscan_employment$GEO)) # Cities within the city group are separated by "-"
+head(city_groups$GEO)
+
+# Since cities within these city groups have large differences in turns of demographics and land areas, 
+# it is not proper to consider these city groups as a whole in the selection of cities, so we opt these city groups out of our study
+
+# We would like to get the population density in one tibble for determining the selection of cities
[…]

### 2021-02-18 scripts/2178 draft.R

@@ -1,0 +1,130 @@
+#### Preamble ####
+# Purpose: This script simulates the responses to a survey about restaurants in Toronto.
+# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
+# Data:  "`r format(Sys.time(), '%d %B %Y')`"
+# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - None
+
+
+
+#### Workspace setup ####
+
+
+
+
+#### Simulate questions ####
+# Q1: Which city are you in? 
+# Q2: Which best describes the nature of your restaurant?
+# Q3: How many employees have you laid off because of COVID 19?
+# Q4: How was your total sales volume this month compare to the last month? 
+# Q5: To what extent, the number of your orders have decreased after the pandemic?
+# Q6: To what extent, your revenue changed after the pandemic?
+# Q7: If current conditions continue, how long do you expect your business to survive before you will have to close down permanently? 
+# Q8: Which best describes the current profitability of your overall operations.
+# Q9: How many months do you expect it will take your business to return to profitability?
+# Q10:How much loans have you received for the COVID related reasons?
+# Q11:Does your foodservice business require additional financial support beyond what is currently available to you through government programs in order to survive?
+# Q12:Is your business receiving the Canada Emergency Wage Subsidy(CEWS)?
+# Q13: Have signed up for the lease subsidy introduced by the government last year?
+# Q14: Including the above governmental programs (if applicable), how much grants have you received for the COVID related reasons?
+# Q15: To what extent, your costs have increased after the pandemic?
+
+
+# Do this one for treated and one for control and then bring them together
+
+#### Treatment group(Brantford) ####
+set.seed(8888)
[…]

### 2021-02-19 outputs/paper/paper.Rmd
Commit for Discussion

@@
 title: "COVID Shutdown Regulations on Restaurants Decreases xx% of Average Total Sales in Ontario"
-author: "Hong Shi, Hong Pan, Yixin Guan"
-thanks: "Code and data are available at: LINK."
+author: "Hong Shi, Hong Pan, Yixin Guan, Babak Mokri"
+thanks: "Code and data are available at: https://github.com/honn-ishinn/restaurants_covid_shutdown"
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 library(tidyverse)
+library(bookdown)
 library(palmerpenguins)
+library(stringr)
+library(ggrepel)
+library(here)
+library(kableExtra)
 ```
@@
 
-1. show current covid situations and policy regulations from world wide perspective to Ontario specific.
-
-2. some context of economics effects on Ontario, preferably specific to covid effect on restaurant
-
-3.
-however, current data include not only the shutdown effect, but also the covid effect (counterfeit counterfactual), Inferring causality will require that you rule out other potential factors that could have affected the outcome under consideration.(close of restaurants etc.) Does not make sense to compare the restaurant situations before COVID and during COVID.
-
-4.
-As a result, to give an accurate estimate of the counterfactual, we need to identify the treatment & control group (2 cities) under current COVID outbreak, with similar restaurant operating situations.
-We selected Peterborough and Brantford.(could leave this part to discussion)
-SAME IN 3 WAYS: (1).avg characteristics identical (through )
- (2).
-treatment should not affect the comparison group either directly or indirectly ( by city distance of 200+ km unlikely to travel to another city for a meal) However, there might be overestimate of the reopening effect on restaurants since people living near Peterborough while still having their regions' restaurants shutdown might choose to go to Peterborough, increasing sales of Peterborough restaurants.
- (3). Outcome of units in control group should change the same way as outcomes in treatment group (e.g. Provincial subsidy applied to the whole Ontario restaurant business)
-
-Sampling methods and randomizations: Yixin
-
-Data & Survey:
-Discussioin Part:
-1.Summarize, then
-2. mention the selection of cities (limitations)
-3. sampling methods (limitations)
-4. Need to address internal validity and external validity
-Internal validity:Internal validity means that the estimated impact of the program is
-net of all other potential confounding factors—or, in other words, that
-the comparison group provides an accurate estimate of the counterfactual,
-so that we are estimating the true impact of the program.
-Basically true since the selection of these two cities ensures the similarity in turn of either city size , population, etc. and restaurant operating situation (through ).
-
-External validity:
-External validity means that the evaluation sample accurately represents
-the population of eligible units.
-
-Somehow limited, results may not be extrapolated to the entire population of interest, i.e.
-Restaurant all over Ontario.
-This is a single-tier relative small size city level experiment.
-May not generalized to townships, or cosmopolitan city like Toronto...
-
-5. Tradeoff between reopening (economy) and covid cases (public health and healthcare). Should carefully consider....
-
 # Data
-```{r}
-citation("cansim")
-```
 
 &nbsp; &nbsp; Our data explores shutdown effects on restaurant businesses in Ontario.
-We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `scales` [@cite_scales], `here` [@cite_here].
+We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `here` [@cite_here].
 We used R packages `cansim` [@cite_cansim] and packagesxxx to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra] to format the document.
+
 ## Intervention
@@
 Therefore, we mindfully chose Peterborough, a relative small size Single-tier^[Ontario's Municipal Act, 2001 defines a single-tier municipality as "a municipality, other than an upper-tier municipality, that does not form part of an upper-tier municipality for municipal purposes"] city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
-Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns.
+Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns[@cite_impact].
 In our experiment, we assigned restaurants in Peterborough as the treatment group and those in Brantford as the control group.
@@
 
-Our data is of penguins (Figure \@ref(fig:bills)).
+# Discussion
 
-```{r bills, fig.cap="Bills of penguins", echo = FALSE}
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = FALSE) +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+## Determine the Treatment Group and Control Group
+
+To obtain an accurate estimate of the shutdown effect on restaurant businesses, average characteristics of restaurants in the reopening city and those in the shutdown city need to be identical in the absence of the reopen intervention under current COVID outbreak.
+Since businesses in the food service industry are highly labor intensive [@cite_labor], the `total employment` on food service between selected cities is preferred to be equal as the identical characteristic.
+Besides, `population density` ( `Total Population`/ `Total Land Area in squared kilometers`) also has significant organizational life-cycle effects[@cite_density].
+At different population density levels, competitions for food services varies, leading to different restaurants mortality rates even without the reopen intervention.
+As a result, total employment on food service and population density serve as primary restaurant operation characteristics for the selection of treatment city and control city.
+
+```{r selectsetup, include=FALSE}
+
+# Employment data
+cleaned_statscan_employment <- readr::read_csv(here::here("inputs/data/cleaned_statscan_employment.csv"))
+# Census data
+cleaned_2016_census <- readr::read_csv(here::here("inputs/data/cleaned_2016_census.csv"))
 ```
 
-Talk more about it.
+```{r selectclean, include=FALSE}
+select_employment <- 
+  cleaned_statscan_employment %>% 
+  select(GEO, VALUE) %>% 
+  filter(GEO != "Ottawa-Gatineau, Ontario/Quebec" & GEO != "Ottawa-Gatineau, Quebec part, Ontario/Quebec")
+# Remove the Gatineau employment data since it is out of Ontario province
 
-Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)
+# We would like to get the population density in one tibble for determining the selection of cities
+select_census <- 
+  cleaned_2016_census %>% 
+  select( City = `Geographic name`, Population_Density = `Population density per square kilometre, 2016`)
 
-```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}
+# split the column name in select_employment dataset to remove "Ontario" province separated by comma
 
-# This needs to be about the random data tha tI sasmpled?
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = FALSE) +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+select_employment$City <- str_split_fixed(select_employment$GEO, ",", 2)[,1] #[,1] means to only keeps the city names column
+# Drop the GEO column 
+# Ref link to drop the column: https://stackoverflow.com/questions/6286313/remove-an-entire-column-from-a-data-frame-in-r
+select_employment$GEO <- NULL
+
+# change Ottawa-Gatineau into Ottawa since already removed Gatineau 
+# Ref link to reassign value:https://www.edureka.co/community/35430/how-change-the-value-variable-using-programming-data-frame
+select_employment$City[select_employment$City == "Ottawa-Gatineau"] <- "Ottawa"
+
+unique(cleaned_statscan_employment$SCALAR_FACTOR)
+# Multiply the employment value by 1000 since the scalar factor is in thousands 
+select_employment$Employment <- select_employment$VALUE * 1000
+# Drop the VALUE column
+select_employment$VALUE <- NULL
+
+# join two dataset to create a dataset that contains cities with population density and employment in Accommodation and food services available
+
+popdensity_employment <- merge(select_census, select_employment, by = "City")
+
+# filter out Toronto since there is no comparable city with Toronto
+popdensity_employment <- 
+  popdensity_employment %>% 
+  filter( City !="Toronto")
 ```
 
-Talk way more about it.
+```{r selectplot, fig.align='center', fig.cap="Population Density vs Employment on Accommodation and Food Services in Ontario Cities in 2016", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
 
-# Model
+# Highlight cities chosen for our experiment
+highlight_city <- popdensity_employment %>% 
+  filter(City =="Brantford"|City =="Peterborough")
 
-\begin{equation}
-Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
-\end{equation}
+ggplot( data = popdensity_employment, mapping = aes(x = Employment, y = Population_Density)) +
+  geom_point( )+
+  geom_point(data = highlight_city,
+             aes(x = Employment, y = Population_Density),
+             color="red",
+             size = 2)+
+  theme_minimal() + 
+  geom_label_repel(aes( label = City)) +
+  labs(
+    title = "Population Density vs Total Employment on Accommodation and Food Services",
+    x = "Employment",
+    y = "Population Density"
+  )
+```
 
-Equation \@ref(eq:bayes) seems useful, eh?
+We used the employment by industry data and 2016 Census data available at Statistics Canada to identify cities with similar total employment on food service and population density.
+The above point graph(Figure \@ref(fig:selectplot)) indicates that Brantford and Peterborough have similar characteristics affecting the restaurant operations.
+In addition, the coefficient of the graph $$\frac{Population\:Density}{Total \:Employment}=\frac{Total\:Population/Total\:Land\:Area}{Total\:Employment}$$, which could be interpreted as the number of people served by a restaurant employee per square kilometers, helps to identify the restaurant operating situation in designated regions.
+Similar coefficients between Brantford and Peterborough (0.306 vs 0.308) also suggest close restaurant characteristics.
+Besides, there is neither significant demographics nor land areas difference between these two cities, so we consider these two cities as a valid comparison group and reopened Peterborough as the treatment group while maintaining Brantford shutdown as the control group.
 
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
+Extra concerns when determining the treatment group and control group:
 
-# Results
+* The employment data at Statistics Canada uses the NAICS (North American Industry Classification System) standard and assigns employment services to Accommodation and Food Service category.
+So there is less employment in food services.
+We took the convention that the ratio between the accommodation employment and the food service employment between Peterborough and Brantford is the same.
 
-# Discussion
+* Since the distance between Brantford and Peterborough is more than 200 kilometers apart, residents in Brantford are unlikely to travel such long distance solely for a dine-in meal.
+So the treatment of reopening Peterborough would not affect the mealing behavior in Brantford.
+However, residents in shutdown regions near Peterborough might go for dine-in meals, increasing sales in Peterborough restaurants.
+The actual shutdown effect on restaurants could be overestimated due to possible increase in sales from nearby shutdown regions' residents.
 
-## First discussion point
+* The mindful comparison between cities' similarities on employment, population density, etc.
+ensures the internal validity of our experiment so that we could accurately estimate the true impact of the shutdown restriction on restaurant.
+However, the shutdown effect evaluation may not be generalized to the entire population of interest, i.e.
+all restaurants in Ontario such as township regions or cosmopolitan city Toronto.
 

### 2021-02-19 scripts/02_city_selection.R

@@ -102,11 +102,23 @@ popdensity_employment <-
   popdensity_employment %>% 
   filter( City !="Toronto")
 
+# Highlight cities chosen for our experiment
+highlight_city <- popdensity_employment %>% 
+  filter(City =="Brantford"|City =="Peterborough")
+
 ggplot( data = popdensity_employment, mapping = aes(x = Employment, y = Population_Density)) +
   geom_point( )+
+  geom_point(data = highlight_city,
+             aes(x = Employment, y = Population_Density),
+             color="red",
+             size = 2)+
   theme_minimal() + 
-  geom_label_repel(aes( label = City)) 
-#geom_smooth( method = "lm", formula = y~x)
+  geom_label_repel(aes( label = City)) +
+  labs(
+    title = "Population Density vs Total Employment on Accommodation and Food Services in Ontario Cities",
+    x = "Employment",
+    y = "Population Density"
+  )
 
 # As we could see from the graph, the data points representing Bratford and Peterborough lies closely with each other
 # Meaning that they have similar population density and accommodation and food service employment, 

### 2021-02-19 scripts/2178 draft.R

@@ -1,130 +1,0 @@
-#### Preamble ####
-# Purpose: This script simulates the responses to a survey about restaurants in Toronto.
-# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
-# Data:  "`r format(Sys.time(), '%d %B %Y')`"
-# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 
-# - None
-
-
-
-#### Workspace setup ####
-
-
-
-
-#### Simulate questions ####
-# Q1: Which city are you in? 
-# Q2: Which best describes the nature of your restaurant?
-# Q3: How many employees have you laid off because of COVID 19?
-# Q4: How was your total sales volume this month compare to the last month? 
-# Q5: To what extent, the number of your orders have decreased after the pandemic?
-# Q6: To what extent, your revenue changed after the pandemic?
-# Q7: If current conditions continue, how long do you expect your business to survive before you will have to close down permanently? 
-# Q8: Which best describes the current profitability of your overall operations.
-# Q9: How many months do you expect it will take your business to return to profitability?
-# Q10:How much loans have you received for the COVID related reasons?
-# Q11:Does your foodservice business require additional financial support beyond what is currently available to you through government programs in order to survive?
-# Q12:Is your business receiving the Canada Emergency Wage Subsidy(CEWS)?
-# Q13: Have signed up for the lease subsidy introduced by the government last year?
-# Q14: Including the above governmental programs (if applicable), how much grants have you received for the COVID related reasons?
-# Q15: To what extent, your costs have increased after the pandemic?
-
-
-# Do this one for treated and one for control and then bring them together
-
-#### Treatment group(Brantford) ####
-set.seed(8888)
[…]

### 2021-02-22 scripts/03_mapping_SAC_postalcode.R
Commit for sampling method

@@ -1,0 +1,68 @@
+#### Preamble ####
+# Purpose: Sampling Method: Get mapping document for CMA and postal code
+# Author: Yixin Guan, Hong Pan, Hong Shi, Babak Mokri
+# Date:  21 February 2021
+# Contact: yixin.guan@mail.utoronto.ca, hong.pan@mail.utoronto.ca, lancehong.shi@mail.utoronto.ca, b.mokri@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: 
+# Need to have downloaded the Postal Code Conversion File (PCCF) 
+# UofT library Login Required: 
+# https://mdl.library.utoronto.ca/sites/default/files/mdldata/restricted/canada/national/statcan/postalcodes/pccf/2016/2020nov/pccfNat_fccpNat_112020.zip
+# Then saved the file as "pccf.txt" into "inputs/data"
+
+#### Workspace Setup ####
+
+library(here)
+library(tidyverse)
+
+
+
+#### Getting mapping document for CMA and postal code ####
+
+# Postal Code Conversion File (PCCF), Reference Guide:
+# https://mdl.library.utoronto.ca/sites/default/files/mdldata/open/canada/national/statcan/postalcodes/pccf/2016/2020nov/PCCF_202011-eng.pdf
+
+# Postal Code Conversion File (PCCF) - Login Required:
+# https://mdl.library.utoronto.ca/sites/default/files/mdldata/restricted/canada/national/statcan/postalcodes/pccf/2016/2020nov/pccfNat_fccpNat_112020.zip
+
+# In order to get a list of postal codes in a CMA, PCCF is required and downloaded. The first five lines are showed below.
+
+pccf_txt <- readLines(here("inputs/data/pccf.txt"))
+pccf_txt[1:5]
+
+# According to the Reference Guide, the first 6 characters are postal code. 
+# Statistical Area Classification(SAC) code (incluides CMA/CA) starts from the 99th characters and followed by 3 characters. 
+# Postal code and and SAC are extract when each line is gone through.
+
+postalCode <- 0
+#fsa <- 0
+#CSDname <- 0
+SAC <- 0
+
+for(i in 1:length(pccf_txt)) {
+  postalCode[i] <- substr(pccf_txt[i],1,6)
+  #  fsa[i] <- substr(pccf_txt[i],7,9)
+  #  CSDname[i] <- substr(pccf_txt[i],23,92)
[…]

### 2021-02-22 scripts/04_get_restaurants_data.R

@@ -1,0 +1,103 @@
+#### Preamble ####
+# Purpose: Sampling Method: Get a list of restaurants of Brantford and Peterborough using Yelp API
+# Author: Yixin Guan, Hong Shi, Babak Mokri, Hong Pan
+# Date:  21 February 2021
+# Contact: yixin.guan@mail.utoronto.ca, lancehong.shi@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# Need to have downloaded the "mapping_SAC_postalcode.csv" in "03_mapping_SAC_postalcode.R" and saved it to inputs/data
+
+
+####  Workspace Setup ####
+
+library(here)
+library(tidyverse)
+library(httr)
+library(xml2)
+
+
+
+# In order to make an request using Yelp API, a Yelp developer account and a API Key have to be created. 
+
+token <- "shSjf2t4b6wdrVtwf4kGvhZtOkR5c01gStUBs5S4In7dU5heYqd0eIymikqX2v-xN7OEqY_AgfZ0d9CvXGVj5nUYAZ7A9rWjGOtL7qu6H5RlnrQaW_zuYMbTb7opYHYx"
+
+# Setup for searching restaurants in Brantford, Ontario
+
+yelp <- "https://api.yelp.com"
+term <- "restaurants"
+Brantford_location <- "Brantford, Ontario"
+categories <- "Restaurants"
+limit <- 50
+radius <- 40000
+
+restaurantName <- vector()
+postalCode <- vector()
+restaurantAddress <- vector()
+phoneNum <- vector()
+
+# Since each page only showed 50 results, and there are more resturuants in the two cities. We use "offset" to find all the records. 
+
+# Get all 133 restaurants in Peterborough
+for(n in seq(0, 133, 50)) {
+  url <- modify_url(yelp, path = c("v3", "businesses", "search"),
+                    query = list(term = term, location = Brantford_location, 
+                                 limit = limit,
+                                 radius = radius,
+                                 offset = n))
+  res <- GET(url, add_headers('Authorization' = paste("bearer", token)))
+  
+  results <- content(res)
+  len <- length(results$businesses)
+  for(i in 1:len) {
+    address <- paste(results$businesses[[i]]$location$display_address[[1]], results$businesses[[i]]$location$display_address[[2]], results$businesses[[i]]$location$display_address[[3]])
+    restaurantName <- append(restaurantName, results$businesses[[i]]$name)
[…]

### 2021-02-22 scripts/05_get_restaurant_survey_list.R

@@ -1,0 +1,82 @@
+#### Preamble ####
+# Purpose: Sampling Method: Get the list of restaurants for sampling
+# Author: Yixin Guan, Hong Shi, Babak Mokri, Hong Pan
+# Date:  21 February 2021
+# Contact: yixin.guan@mail.utoronto.ca, lancehong.shi@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# Need to have downloaded the "mapping_SAC_postalcode.csv" in "03_mapping_SAC_postalcode.R" and saved it to inputs/data
+# Need to have downloaded the "restaurant_data.csv" in "04_get_restaurants_data.R" and saved it to inputs/data
+
+
+####  Workspace Setup ####
+
+library(here)
+library(tidyverse)
+library(kableExtra)
+
+# Read in the cleaned data
+
+# Mapping data
+
+mapping <- readr::read_csv(here::here("inputs/data/mapping_SAC_postalcode.csv"))
+
+# Restaurant data
+
+restaurantList <- readr::read_csv(here::here("inputs/data/restaurant_data.csv"))
+
+# Join the mapping data and restaurant data to ensure restaurants we would sample are indeed in Brantford and Peterborough
+
+
+joined_tibble <- inner_join(
+  mapping,
+  restaurantList,
+  by = c("postal_Code" = "restaurantPostalCode"))
+
+# check number of restaurants within these two cities after the inner join
+# Note: SAC 543 stands for Brantford, SAC 529 stands for Peterborough
+
+joined_tibble %>%
+  group_by(SAC) %>%
+  summarise(count=n())
+
+set.seed(8888)
+
+#Randomly find 100 restaurants whose postal code is in Brantford CMA and the phone number is not missing.  
+brantfordRandomRestaurant <- joined_tibble %>%
+  filter(SAC == "543" & phoneNumber != '') %>%
+  sample_n(100)
+
+#Randomly find 100 restaurants whose postal code is in Peterborough CMA and the phone number is not missing.  
+peterboroughRandomRestaurant <- joined_tibble %>%
+  filter(SAC == "529" & phoneNumber != '') %>%
+  sample_n(100)
+
+#create a list to give the survey staff with the name, phone number, city and the postal codes of the restaurants
[…]

### 2021-02-23 outputs/paper/paper.Rmd
Commit for sampling method

@@
 &nbsp; &nbsp; Our data explores shutdown effects on restaurant businesses in Ontario.
-We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `here` [@cite_here].
+We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here].
 We used R packages `cansim` [@cite_cansim] and packagesxxx to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra] to format the document.
@@
 subsidies, grants, etc.) to estimate the true impact of shutdown effects on restaurant businesses after three-month reopening in Peterborough.
+
+## Sampling Methods
+
+This experiment considered all Ontario restaurants as its target population.
+The frame population was decided by randomly selecting 100 restaurants from Brantford and 100 from Peterborough.
+To ensure the external validity of the experiment, we used the following steps to find these restaurants:
+
+1. Scrape the postal codes of all restaurants located within the circle of the Brantford City Centre to a 40 km radius on Yelp. And then use the same method for Peterborough.
+
+2. Acquire a list of postal codes in Brantford CMA and Peterborough CMA from the Postal Code Conversion File (PCCF) retrieved from the University of Toronto Library[@cite_uoftlibrary].
+
+3. Compare the two lists and eliminate the restaurants with postal codes outside of Peterborough CMA and the Brantford CMA.
+
+4. Randomly select 100 restaurants from Brantford and 100 restaurants from Peterborough to form the frame population.
+
+```{r samplingtable, fig.cap='Sampling Results Summary', echo=FALSE }
+tibble(
+  'City' = list('Brantford', 'Peterborough'), 
+  'Survey Administered' = list(100, 100),
+  'Total Sample Collected' = list(45, 48),
+  'Telephone Survey' = list(40, 41),
+  'Online Survey' = list(5, 7)
+) %>%
+  kbl(caption = 'Sampling Results Summary',
+      align = "cccc") %>%
+  kable_styling(latex_options = "hold_position")
+```
+
+We used telephone interviews and online questionnaire methods to administer the survey.
+The telephone interview served as the primary channel and an online survey option was provided when respondents could not or prefer not to be interviewed over the phone.
+As shown in the above table (Table \@ref(tab:samplingtable)), our sampled population included 45 valid responses in Brantford and 48 collected from Peterborough, among which, 5 were collected via the online survey in Brantford and 7 were collected via the online survey in Peterborough.
+Surveys that were not answered or have incomplete answers were treated as nonresponses and were not included in the dataset for further analysis.
+The surveys were administered in the following steps:
+
+1. The phone number of the restaurants was scraped from Yelp while we determined the frame population.
+
+2.
+Working from 2 pm to 4 pm, half of the survey staff called the Brantford restaurants, and the other half called the Peterborough restaurants simultaneously to avoid sampling bias.
+Each phone call took around 15 minutes to complete.
+All restaurants on the pre-determined list were reached within one week.
+
+3.
+When the call was connected, the survey staff would provide a brief introduction of the survey purpose and indicate that the survey was sponsored by the Ontario government.
+See Appendix A for details.
+
+4.
+To ensure the quality and accuracy of the data collection, the survey staff would ask if the respondent at the restaurant worked at a management-level position in the restaurant or was familiar with the restaurant’s sales performance.
+If the respondent answered no, the survey staff would ask the caller to pass the call to the relevant staff in the restaurant.
+If that staff was not available, the survey staff will schedule another call or provide the online questionnaire based on the preference identified by the respondent.
+Respondents who were interested in answering the questions via online questionnaires could leave their email addresses and have two weeks to complete the survey questions.
+
+5. Respondents who were not reached by phone for the first time were called again in the following week. Restaurants that did not respond to the second call were documented as “nonresponse”.
+
+6.
+To address privacy concerns and to increase the response rate, the respondents were notified before the survey that all answers were recorded anonymously.
+The respondents were told at the beginning of the telephone survey that they could terminate the survey anytime if they want to.
+The respondents were also notified before the survey that they would have a chance to win a 50-dollar gift card if they fully participated.
+
+The survey incurred a total cost of \$20,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
+A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.
 
@@
 
-## Second discussion point
+## Sampling Method
+
+The sampling methods of this experiment were accompanied by some inevitable limitations and biases:
+
+* The list of restaurants in Brantford and Peterborough may not be accurately represented on Yelp.
+Some restaurants may not be registered on Yelp and some may not have updated their information on time.
+What is more, restaurants would only appear in the Yelp query when it has been reviewed by one of its users, which suggests that certain new restaurants may not be on the list.
+These limitations may result in the exclusion bias of our sample.
+
+* The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations.
+Restaurants that lost their businesses during the pandemic could not be captured with the current method.
+However, these may be the ones that are most severely impacted.
+
+* The sampling methods bore self-selection bias.
+From a psychological standpoint, respondents may have a stronger desire to respond to the survey if they have a strong opinion to express about their situations.
+The results showed that restaurant owners in Brantford faced a steeper sales decrease, and we expect that this may contribute to the higher survey response rate in Brantford.
+
+* The accuracy of the responses may be hindered by the difficulties in reaching the management staff of restaurants.
+The phone numbers scraped from Yelp was usually used for food ordering and the staff who picked up the phone may not know the sales status.
+However, we do not believe this would significantly skew the result.
+According to Statistics Canada, 98.5% of restaurants in Canada have 0-99 employees[@cite_industries].
+Since food service businesses are usually small to medium size, there is a high likelihood for the survey to reach management staff in the restaurant.
+Respondents were also asked to pass the phone to management staff or leave their email to receive the online survey if they would like to do so, therefore mitigating the negative impact caused by the telephone survey method.
+
+* Respondents may react differently in a phone interview compared to an online survey.
+The two methods may have the potential to produce significantly different results even when the two surveys have the same questions [@cite_surveycompare].
+People may be more comfortable answering a certain type of question online rather than by phone call, or vice versa.
 

### 2021-02-23 outputs/paper/paper.Rmd
Commit for data part

@@
 &nbsp; &nbsp; Our data explores shutdown effects on restaurant businesses in Ontario.
-We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here].
-We used R packages `cansim` [@cite_cansim] and packagesxxx to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra] to format the document.
+We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here], `ggpubr`[@cite_ggpubr].
+We used R packages `cansim` [@cite_cansim], `httr`[@cite_httr], `xml2`[@cite_xml2] to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra], `ggrepel`[@cite_ggrepel] to format the document.
+We referenced `Impact Evaluation in Practice`[@cite_impact] and `Sampling Theory and Practice`[@cite_sampletheory] to design our experiment.
 
@@
 
-The survey incurred a total cost of \$20,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
+The survey incurred a total cost of \$10,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
 A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.

### 2021-02-23 scripts/2178_charts.Rmd
Commit for data part

---
title: "Untitled"
output: pdf_document
---
```{r}
citation("ggrepel")
```

```{r}
#### Workspace setup ####

library(here)
here()
#install.packages("tidyverse")
library(tidyverse) # used for data manipulation

#install.packages("ggpubr")
library(ggpubr) ##for combing figures in one graph

#install.packages("ggrepel")
library(ggrepel)
library(kableExtra)
```
#import dataset
```{r}
simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
```

#Q1
#```{r}
table(simulated_dataset$q1_city,simulated_dataset$q2_type)%>%
  addmargins()%>%
  kable("html", align = 'clc', caption = 'Restaurant type and quantity information table')%>%
  kable_styling(full_width = F)

#```

#Q3 layoff
```{r}
data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
    geom_bar(stat = "identity",position = position_dodge())+
   theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of responses")+
  xlab("Number of laid-offs")+
  ggtitle("Layoff situation in Peterborough")+

  guides(fill=guide_legend(title="City"))

```

#Q4 total sales
```{r}
#Peterborough
p_table <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q4_total_sales))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

label_p<-paste(p_table$Var1,"\n",p_table$pct)%>%
  paste("%",sep = "")

pie(p_table$Freq,labels = label_p,col=c("#7FC97F","#BEAED4", "#FDC086", "#FFFF99", "#386CB0" ),
    main = "Peterborough: Total sales volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.6,cex.main=1)

#Brantford
b_table <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q4_total_sales))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

label_b<-paste(b_table$Var1,"\n",b_table$pct)%>%
  paste("%",sep = "")

pie(b_table$Freq,labels = label_b,col=c("#7FC97F","#BEAED4", "#FDC086", "#FFFF99", "#666666","#386CB0"),
    main = "Brantford:Total sales volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.5,cex.main=1)

```

# q5 total cost
```{r}
#Peterborough
p_table_cost <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q5_total_cost))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

label_p<-paste(p_table_cost$Var1,"\n",p_table_cost$pct)%>%
  paste("%",sep = "")

pie(p_table_cost$Freq,labels = label_p,col=c( "#A6CEE3", "#1F78B4" ,"#B2DF8A" ,"#33A02C","#FB9A99"  ),
    main = "Peterborough: Total cost volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.6,cex.main=1)

#Brantford
b_table_cost<- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q5_total_cost))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

label_b<-paste(b_table_cost$Var1,"\n",b_table_cost$pct)%>%
  paste("%",sep = "")

pie(b_table_cost$Freq,labels = label_b,col=c("#A6CEE3", "#1F78B4" ,"#B2DF8A" ,"#FB9A99"  ),
    main = "Brantford:  Total cost volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.6,cex.main=1)

```

# Q8 Survive

```{r}
# Use

data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
    mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of responses")+
  xlab("Expected survival time")+
  ggtitle("How long can survive")+
  coord_flip()
```

```{r}
# No use

data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var1)) +
    geom_bar(stat = "identity", width = 0.55)+
  facet_wrap(~Var2)+
  scale_x_discrete(limits = c("Less than 3 months", "3 to 6 months", "Longer than 6 months","Unknown","Prefer not to say"))+
  ylab("Number of responses")+
  xlab("Expected survival time")+
  ggtitle("How long can survive")+
  theme_minimal()+
  coord_flip()

  #theme(axis.text.x = element_text(angle = 90))
```

# 10 recover
```{r}
# no use
q_10 <- data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulated_dataset$q2_type))
data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulated_dataset$q2_type))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity",position = position_dodge())+
  facet_wrap(~Var3)+
  ylab("Number of responses")+
  xlab("Number of months")+
  ggtitle("How long will it take to recover?")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90))+
   scale_x_discrete(limits = c("Six months or less","7 to 12 months","12 to 18 months","More than 18 months","Prefer not to say"))

```
```{r}
# use
data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulated_dataset$q2_type))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than 18 months","12 to 18 months","7 to 12 months","Six months or less")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
  geom_bar(stat = "identity",width = 0.8, position = position_dodge())+
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~Var3)+
  ylab("Number of responses")+
  xlab("Number of months")+
  ggtitle("How long will it take to recover?")+
  guides(fill=guide_legend(title="City"))+
  coord_flip()

```

#q13 wage

```{r}
# brewer.pal(n = 8, name = "Dark2")
#Peterborough
p_table_wage <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q13_CEWS))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

label_p<-paste(p_table_wage$Var1,"\n",p_table_wage$pct)%>%
  paste("%",sep = "")

pie(p_table_wage$Freq,labels = label_p,col=c( "#A6CEE3", "#1F78B4", "#B2DF8A" ),
    main = "Peterborough: Is your business receiving the Canada Emergency Wage Subsidy(CEWS)? ",cex=0.6,cex.main=1)

#Brantford
b_table_wage<- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q13_CEWS))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

label_b<-paste(b_table_wage$Var1,"\n",b_table_wage$pct)%>%
  paste("%",sep = "")

pie(b_table_wage$Freq,labels = label_b,col=c("#A6CEE3", "#1F78B4","#FF7F00", "#B2DF8A" ),
    main = "Brantford: Is your business receiving the Canada Emergency Wage Subsidy(CEWS)? ",cex=0.6,cex.main=1)

```
```{r}
library(forcats)
```

# 14 loans
```{r}
# no use
data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity",position = position_dodge())+
  ylab("Number of responses")+
  xlab("Grant value")+
  ggtitle("How much loans have you received for the COVID-19 related reasons?")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()

```
```{r}
?forcats::fact_reorder
```

```{r}
# use
data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity",position = position_dodge())+
  ylab("Number of responses")+
  xlab("Grant value")+
  ggtitle("How much loans have you received for the COVID-19 related reasons?")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()

```
```{r}
q_14 <- data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))
```

# Q15

```{r}
t1<-simulated_dataset%>%
  mutate(Average_value= case_when(
    q1_city=="Brantford"~ round(mean(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q11_rate_support),3),
    q1_city=="Peterborough" ~ round(mean(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q11_rate_support),3)
  ))%>%
  select(q1_city,q11_rate_support,Average_value,3)

table(t1$q1_city,t1$q11_rate_support)%>%
  addmargins()%>%
  kable("html", align = 'clc', caption = 'Number and level of ratings from two cities')%>%
  kable_styling(full_width = F)

```

### 2021-02-23 scripts/05_get_restaurant_survey_list.R

@@ -60,7 +60,7 @@ finalSurveyList <- union(brantfordRandomRestaurant, peterboroughRandomRestaurant
 
 # Save the survey list for survey staffs to contact restaurants 
 
-write.csv(finalSurveyList, here("outputs/surveylist/restaurant_survey_list.csv"))
+write.csv(finalSurveyList, here("outputs/survey/restaurant_survey_list.csv"))
 
 #### Create a simulated table showing restaurant responses####
 

### 2021-02-23 scripts/06_simulate_survey_responses.R

@@ -1,0 +1,186 @@
+#### Preamble ####
+# Purpose: This script simulates the responses to restaurant survey responses in Peterborough and Brantford.
+# Author:  Hong Pan, Hong Shi, Yixin Guan, Babak Mokri
+# Data:  "22 February 2021"
+# Contact:  hong.pan@mail.utoronto.ca， lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - None
+
+
+#### Workspace setup ####
+
+#install.packages("tibble")
+library(tibble)  # a nice way to create data frames
+library(here)
+
+
+#### Questions ####
+
+# Q1: Which city are you in?  
+# (Simulate around 50 observations for each city. According to the data scraping from Yelp, Peterborough and Brantford both have around 160 restaurants. From our research, we estimated that around 50 of 100 restaurants randomly selected would reply to our survey.)
+
+# Q2: Which best describes the nature of your restaurant?
+# (According to the dataset [Statistics Canada,2017], for each city, half of the data is simulated as table-service, and the other half is simulated as quick-service.)
+
+# Q3: How many employees have you laid off because of COVID 19?
+# (According to the data [Statistics Canada,2020 ], small layoffs have the highest proportion for restaurants of different sizes. From research, we know that Ontario has more small or medium-sized restaurants, to give a relatively small percentage for layoff more than 5 people.)
+
+# Q4: How was your total sales volume during Oct to Dec 2020 compared to July to Sept2020?
+# (The results from surveying restaurants' total sales from quarter 2[Restaurants Canada Q2, 2020] and quarter 3[Restaurants Canada Q3,2020] help to simulate the data.The better situation for reopen city.)
+
+# Q5: How was your total costs volume during Oct to Dec 2020 compared to July to Sept2020?
[…]

### 2021-02-23 scripts/07_simulate_graphs_in_paper.R

@@ -1,0 +1,24 @@
+#### Preamble ####
+# Purpose: This script create relavent graphs used in the paper.
+# Author:  Hong Pan, Hong Shi, Yixin Guan, Babak Mokri
+# Data:  "22 February 2021"
+# Contact:  hong.pan@mail.utoronto.ca， lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded the "simulated_restaurant_data.csv" in "06_simulate_survey_responses.R" and saved it to outputs/survey
+
+
+
+
+#### Workspace setup ####
+
+library(here)
+library(tidyverse) # used for data manipulation
+library(ggpubr) ##for combing figures in one graph
+library(ggrepel)
+library(kableExtra)
+
+
+
+# Referenced the following link to reorder reponses
+#https://www.r-graph-gallery.com/267-reorder-a-variable-in-ggplot2.html

### 2021-02-23 outputs/paper/paper.Rmd
Commit for Data

@@
 library(bookdown)
-library(palmerpenguins)
+library(janitor)
 library(stringr)
@@
 
+&nbsp; &nbsp; The hospitality industry which encompasses lodging, travel and tourism services, recreation, entertainment, and gastronomy has always been a significant source of employment and a reliable source of income for families for years.
+Businesses in this industry have been vigorously setting long-term goals and priorities to enhance their position in the market, customer satisfaction, and ultimately maximize profit.
+To this end, they create, shape, and influence their business capabilities such as human resources, business processes, and technological assets, deploy and implement thoughtful business solutions, and, eventually, make requisite investments with their available or credit resources.
+Although, by strategic planning there always comes a considerable contemplation of different types of risks and their sources, the unforeseen pandemic commencing in March 2020 was not identified as a considerable threat by most businesses.
+Nevertheless, even the most risk averse companies would not have the capacity to accommodate a prolonged shut down or to enforce social distancing in a sector such as hospitality where socialization is integral to the customer experience with no well defined end or clarity for the future in sight.
+
+&nbsp; &nbsp; The COVID-19 pandemic impacted many businesses - including restaurants - and resulted in mass-layoffs of workers throughout the world.
+According to HuffPost [@cite_unemployment], “Canada's unemployment rate was 13.5% in May 2020, the highest it has been since 1976” [@cite_wikiemploy].
+However, the unemployment crisis in Canada, which would result in rising rates of depression, suicide, frustration, crime, and other unprecedented social issues, was proactively considered and managed by the Government of Canada.
+The Canada Emergency Wage Subsidy (CEWS)V[@cite_CEWS] as well as the Canada Emergency Rent Subsidy (CERS) [@cite_CERS] programs were enacted swiftly and served as much needed lifelines for businesses to survive.
+The Ontario government also initiated some rules to close businesses in some regions and enforce other rules in the others.
+In addition, it provided a range of support for businesses to help them survive in this crisis.
+For example, it offered creative vehicles of financial support such as provincial tax rebates, loans and debt relief interventions, utility bill payment reductions, business grants, and low-interest loans [@cite_reopening].
+
+&nbsp; &nbsp; To help recover from the current recession, we at Petit Poll have partnered with the Ontario government to examine the effects and scope of COVID shutdown on restaurants.
+We conducted an experiment by selecting two statistically similar cities in Ontario and investigated how reopening the dine-in services for restaurants in one city has prevailed over the state of continued shutdown in another city.
+We compared unemployment rates, restaurant profitability, and the expected financial and social impact in both circumstances.
+The results showed that general satisfaction, a sense of purpose, hope, and profitability increase among the businesses that were allowed to re-open.
+The findings can be generalized to other similar businesses and their associated families and business partners in that city as well.
+In addition, the governmental support programs for small businesses in both cities contributed substantially to the social wellbeing and recovery pathway of all businesses.
+However, the higher comparative rate of COVID cases in the city under treatment resulted in general anxiety among residents, triggered the social health advocates and activists to criticize the government reopening effort, and undermined the projected benefits.
+We then came across the trade-off between opening or closing the public parts of restaurants - or other similar businesses, for which we suggested utilizing SSM (Soft System Methodology) to collect, consider and accommodate all residents' perspectives and potential viewpoints in society.
+
 # Data
@@
 &nbsp; &nbsp; Our data explores shutdown effects on restaurant businesses in Ontario.
-We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here], `ggpubr`[@cite_ggpubr].
+We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here], `ggpubr`[@cite_ggpubr], `janitor`[@cite_janitor] .
 We used R packages `cansim` [@cite_cansim], `httr`[@cite_httr], `xml2`[@cite_xml2] to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra], `ggrepel`[@cite_ggrepel] to format the document.
@@
 Therefore, we mindfully chose Peterborough, a relative small size Single-tier^[Ontario's Municipal Act, 2001 defines a single-tier municipality as "a municipality, other than an upper-tier municipality, that does not form part of an upper-tier municipality for municipal purposes"] city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
-Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns[@cite_impact].
+Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns.
 In our experiment, we assigned restaurants in Peterborough as the treatment group and those in Brantford as the control group.
@@
 subsidies, grants, etc.) to estimate the true impact of shutdown effects on restaurant businesses after three-month reopening in Peterborough.
+
+&nbsp; &nbsp; Starting from October, 2020, the Ontario government reopened Peterborough while keeping shutdown restrictions on the rest of Ontario regions.
+After a three month period in January 2021, we at Petit Poll started to conduct survey on restaurants in Peterborough and Bratford about their business performance from October to December.
+Survey results are released in February 2021.
 
@@
 A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.
+
+## Main Survey Results
+```{r, include=FALSE}
+# read in survey data
+simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
+```
+
+```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+    geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
+   theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Number of Laid-offs")+
+  ggtitle("Layoff Situation due to COVID 19")+
+
+  guides(fill=guide_legend(title="City"))
+
+```
+
+The above figure (Figure \@ref(fig:question3)) shows that restaurants in Peterborough had lower rates of layoff compared to restaurants in Brantford, suggesting families in Peterborough to have experienced better financial situations and probably less stress.
+
+```{r q41, fig.align='center', fig.cap="Peterborough: Total Sales Volume October to December vs July to September in 2020", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+#Peterborough
+p_table <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q4_total_sales))%>%
+  mutate(pct=round(Freq/sum(Freq)*100,2))
+
+label_p<-paste(p_table$Var1,"\n",p_table$pct)%>%
+  paste("%",sep = "")
+
+pie(p_table$Freq,labels = label_p,col=c("#7FC97F","#BEAED4", "#FDC086", "#FFFF99", "#386CB0" ),
+    main = "Peterborough Total Sales Volume: Reopen (Oct to Dec) vs Shutdown (July to Sept) in 2020",cex=0.6,cex.main=1)
+
+```
+From Figure \@ref(fig:q41), we notice a considerable increase in sales in Peterborough during the reopen period, which was Oct-Dec 2020.
+This indicated that if restaurants were open, people would had used their services, regardless of potential pandemic risks.
+This result confirms that the rate of 0-1 layoff in the previous question should be high in this city because restaurants need staff for their dine-in area to operate.
+
+```{r q42, fig.align='center', fig.cap="Brantford: Total Sales Volume October to December vs July to September in 2020", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+b_table <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q4_total_sales))%>%
+  mutate(pct=round(Freq/sum(Freq)*100,2))
+
+label_b<-paste(b_table$Var1,"\n",b_table$pct)%>%
+  paste("%",sep = "")
+
+pie(b_table$Freq,labels = label_b,col=c("#7FC97F","#BEAED4", "#FDC086", "#FFFF99", "#666666","#386CB0"),
+    main = "Brantford Total Sales Volume: Shutdown (Oct to Dec) vs Shutdown (July to Sept) in 2020",cex=0.5,cex.main=1)
+```
+
+On the other hand, despite the same situation during both periods (Jul-Sep and Oct-Dec), which all restaurants had been closed in Brantford, Figure \@ref(fig:q42) shows a slight decrease in sales volume for those restaurants.
+One of the reasons could have been the environmental factors.
+For example, colder weather keeps people at home, and they have more time to cook themselves.
+Or, limited gathering at parks, because of the cold weather, would result in less demand for ready foods.
+
+The increase of costs in Peterborough, as shown in Figure \@ref(fig:q42), demonstrated more activities in their restaurants.
+This change admits that the restaurants probably should have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
+According to figure 4, they must have also purchased more raw materials for their higher revenue.
+Although cost would usually impact the business unit negatively, from a broader view, these kinds of costs would be considered vital for other businesses to survive as they  insert cash flow  into other businesses and business sectors, helping them to perform and flourish.
+
+```{r q51, fig.align='center', fig.cap="Peterborough: Total Cost Volume October to December vs July to September in 2020", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+#Peterborough
+p_table_cost <- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q5_total_cost))%>%
+  mutate(pct=round(Freq/sum(Freq)*100,2))
+
+label_p<-paste(p_table_cost$Var1,"\n",p_table_cost$pct)%>%
+  paste("%",sep = "")
+
+pie(p_table_cost$Freq,labels = label_p,col=c( "#A6CEE3", "#1F78B4" ,"#B2DF8A" ,"#33A02C","#FB9A99"  ),
+    main = "Peterborough Total Cost Volume: Reopen (Oct to Dec) vs Shutdown (July to Sept) in 2020",cex=0.6,cex.main=1)
+
+```
+```{r q52, fig.align='center', fig.cap="Brantford: Total Cost Volume October to December vs July to September in 2020", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+#Brantford
+b_table_cost<- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q5_total_cost))%>%
+  mutate(pct=round(Freq/sum(Freq)*100,2))
+
+label_b<-paste(b_table_cost$Var1,"\n",b_table_cost$pct)%>%
+  paste("%",sep = "")
+
+pie(b_table_cost$Freq,labels = label_b,col=c("#A6CEE3", "#1F78B4" ,"#B2DF8A" ,"#FB9A99"  ),
+    main = "Brantford: Total Cost volume Shutdown (Oct to Dec) vs Shutdown (July to Sept) in 2020",cex=0.6,cex.main=1)
+```
 

### 2021-02-23 scripts/2178_chart_2.Rmd
Commit for Data

--- 2021-02-23 scripts/2178_charts.Rmd
@@
 ```{r}
-citation("ggrepel")
+citation("janitor")
+
 ```
@@
 #### Workspace setup ####
-
 library(here)
@@
 #install.packages("ggrepel")
-library(ggrepel)
+library(ggrepel) #edit graphs
 library(kableExtra)
+#install.packages("janitor")
+library(janitor) # Create tables
 ```
@@
 simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
+
 ```
-
-#Q1
-#```{r}
-table(simulated_dataset$q1_city,simulated_dataset$q2_type)%>%
-  addmargins()%>%
-  kable("html", align = 'clc', caption = 'Restaurant type and quantity information table')%>%
-  kable_styling(full_width = F)
-
-#```
 
@@
   theme_minimal()+
-    geom_bar(stat = "identity",position = position_dodge())+
+    geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
    theme(plot.title = element_text(hjust = 0.5)) +
-  ylab("Number of responses")+
-  xlab("Number of laid-offs")+
-  ggtitle("Layoff situation in Peterborough")+
+  ylab("Number of Responses")+
+  xlab("Number of Laid-offs")+
+  ggtitle("Layoff Situation due to COVID 19")+
 
@@
 pie(b_table$Freq,labels = label_b,col=c("#7FC97F","#BEAED4", "#FDC086", "#FFFF99", "#666666","#386CB0"),
-    main = "Brantford:Total sales volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.5,cex.main=1)
+    main = "Brantford: Total sales volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.5,cex.main=1)
 
@@
 data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
-    mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
+    mutate(Var1 = fct_relevel(Var1 ,"Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
   ggplot(aes(Var1, Freq,fill=Var2)) +
@@
   theme(plot.title = element_text(hjust = 0.5)) +
-  ylab("Number of responses")+
-  xlab("Expected survival time")+
-  ggtitle("How long can survive")+
+  ylab("Number of Responses")+
+  xlab("Expected Survival Time")+
+  ggtitle("Expected Survival Time if Current Situation Continues")+
+  guides(fill=guide_legend(title="City"))+
   coord_flip()
@@
   ggplot(aes(Var1, Freq,fill=Var1)) +
-    geom_bar(stat = "identity", width = 0.55)+
+    geom_bar(stat = "identity")+
   facet_wrap(~Var2)+
@@
   xlab("Expected survival time")+
-  ggtitle("How long can survive")+
+  ggtitle("Expected Survival Time if Current Situation Continues")+
   theme_minimal()+
-  coord_flip()
+  theme(axis.text.x=element_text(size=rel(0.8), angle=20))
 
@@
   xlab("Number of months")+
-  ggtitle("How long will it take to recover?")+
+  ggtitle("Expected Recovery Time Back to pre-COVID Situation")+
   guides(fill=guide_legend(title="City"))+
@@
 ```{r}
-t1<-simulated_dataset%>%
-  mutate(Average_value= case_when(
-    q1_city=="Brantford"~ round(mean(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q11_rate_support),3),
-    q1_city=="Peterborough" ~ round(mean(simulated_dataset[simulated_dataset$q1_city=="Peterborough",]$q11_rate_support),3)
-  ))%>%
-  select(q1_city,q11_rate_support,Average_value,3)
-
-table(t1$q1_city,t1$q11_rate_support)%>%
-  addmargins()%>%
-  kable("html", align = 'clc', caption = 'Number and level of ratings from two cities')%>%
+simulated_dataset %>%
+  tabyl(q1_city, q11_rate_support)%>%
+  adorn_totals("row")%>%
+  adorn_totals("col")%>%
+  adorn_percentages("row")%>%
+  adorn_pct_formatting(digits=2)%>%
+  adorn_ns()%>%
+  adorn_title("combined",row_name = "City", col_name = "Rating")%>%
+  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
   kable_styling(full_width = F)
-
 ```

### 2021-02-23 scripts/06_simulate_survey_responses.R

@@ -69,12 +69,8 @@ library(here)
 
 
 #### Control group(Brantford) ####
-
 set.seed(105)
-
-number_of_control<-45     
-
-#Simulate around 50 observations for each city. According to the data scraping from Yelp, Peterborough and Brantford both have around 160 restaurants. From our research, we estimated that around 50 of 100 restaurants randomly selected would reply to our survey.
+number_of_control<-45     #Simulate around 50 observations for each city. According to the data scraping from Yelp, Peterborough and Brantford both have around 160 restaurants. From our research, we estimated that around 50 of 100 restaurants randomly selected would reply to our survey.
 
 control_data<-tibble(
   group=rep("Control", number_of_control),
@@ -90,7 +86,7 @@ control_data<-tibble(
   q7_revenue=sample(c("Decreased more than 25%","Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% ~ 25%","Increased more than 25%","Prefer not to say"),
                     number_of_control, replace = TRUE, prob = c(0.42, 0.31, 0.11, 0.11, 0.02, 0.03)),
   q8_survive=sample(c("Less than 3 months","3 to 6 months","Longer than 6 months","Unknown","Prefer not to say"),
-                    number_of_control, replace = TRUE, prob = c(0.4, 0.32, 0.18, 0.05, 0.05)),
+                    number_of_control, replace = TRUE, prob = c(0.5, 0.28, 0.08, 0.09, 0.05)),
   q9_profitability=sample(c("Operating at a loss","Breaking even","Profit between 1% and 5%","Profit of 5% or more","Prefer not to say"),
                           number_of_control, replace = TRUE, prob = c(0.52, 0.2, 0.19, 0.03, 0.06)),
   q10_recover=sample(c("Six months or less","7 to 12 months","12 to 18 months","More than 18 months","Prefer not to say"),
@@ -111,9 +107,7 @@ control_data<-tibble(
 
 #### Treatment Group(Peterborough) ####
 
-number_of_treated<-48     
-
-#Simulate around 50 observations for each city. According to the data scraping from Yelp, Peterborough and Brantford both have around 160 restaurants. From our research, we estimated that around 50 of 100 restaurants randomly selected would reply to our survey.
[…]

### 2021-02-23 scripts/07_simulate_graphs_in_paper.R

@@ -17,8 +17,21 @@ library(tidyverse) # used for data manipulation
 library(ggpubr) ##for combing figures in one graph
 library(ggrepel)
 library(kableExtra)
+library(janitor)
+
+# Import Dataset
 
 
 
-# Referenced the following link to reorder reponses
+
+
+
+
+
+
+
+
+
+
+# Referenced the following link to reorder responses
 #https://www.r-graph-gallery.com/267-reorder-a-variable-in-ggplot2.html

### 2021-02-23 outputs/paper/paper.Rmd
Commit for data

@@
 pie(b_table_cost$Freq,labels = label_b,col=c("#A6CEE3", "#1F78B4" ,"#B2DF8A" ,"#FB9A99"  ),
-    main = "Brantford: Total Cost volume Shutdown (Oct to Dec) vs Shutdown (July to Sept) in 2020",cex=0.6,cex.main=1)
+    main = "Brantford: Total Cost Volume Shutdown (Oct to Dec) vs Shutdown (July to Sept) in 2020",cex=0.6,cex.main=1)
 ```
+The increase of costs in Peterborough, as shown in Figure \@ref(fig:q51), demonstrated more activities in their restaurants.
+This change admits that the restaurants probably should have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
+According to figure 4, they must have also purchased more raw materials for their higher revenue.
+Although cost would usually impact the business unit negatively, from a broader view, these kinds of costs would be considered vital for other businesses to survive as they generate cash flow into other businesses and business sectors, helping them to perform and flourish.
+
+```{r q8, fig.align='center', fig.cap="Expected Survival Time if Current Situation Continues", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+# Use
+
+data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
+    mutate(Var1 = fct_relevel(Var1 ,"Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Expected Survival Time")+
+  ggtitle("Expected Survival Time if Current Situation Continues")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+```
+
+It is very unfortunate to study Figure \@ref(fig:q8) which shows restaurants in Brantford are not that much positive to continue their business for longer times.
+This not only shows instability in their personal and family lives, which brings about more stressful situations for them, they would also inject this despondency throughout their community, leading to the emergence of general anxiety in that city.
+However, “hope” in Peterborough is prevalent among the restaurant owners.
+This could probably be an indication of happier people in that region who can better handle this unforeseen pandemic.
+
+```{r q10, fig.align='center', fig.cap="Expected Recovery Time Back to pre-COVID Situation", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+# use
+data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulated_dataset$q2_type))%>%
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than 18 months","12 to 18 months","7 to 12 months","Six months or less")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge())+
+  theme(plot.title = element_text(hjust = 0.5)) +
+  facet_wrap(~Var3)+
+  ylab("Number of responses")+
+  xlab("Number of months")+
+  ggtitle("Expected Recovery Time Back to pre-COVID Situation")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+
+```
+Although from Figure \@ref(fig:q8), we saw a pervasive gloom among the Brantford restaurants.
+Figure \@ref(fig:q8) illustrates that even if the pandemic ends immediately, many restaurants in Brantford, especially quick-service restaurants, have indicated that it is difficult to return to the state of operation before the COVID-19 outbreak.
+While for Peterborough, although some of them suspect the recovery will take more than a year to recoup with the previous situation, most of them indicated this period would be less than a year.
 

### 2021-02-24 outputs/paper/paper.Rmd
Commit for discussion

--- 2021-02-23 outputs/paper/paper.Rmd
@@
 ---
-title: "COVID Shutdown Regulations on Restaurants Decreases xx% of Average Total Sales in Ontario"
+title: "COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario"
 author: "Hong Shi, Hong Pan, Yixin Guan, Babak Mokri"
@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "Since 2020, the world-wide COVID-19 pandemic has greatly influenced public health and healthcare, resulting in governments to impose regulations on social gatherings to eliminate further outbreaks.
-In Ontario, the provincewide stay at home order and shutdown restrictions on businesses and facilities has limited economic activities into a recession.
+abstract: "Due to the world-wide COVID-19 pandemic, shutdown restrictions on businesses and facilities have limited economic activities into a recession.
 This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months reopening.
-The experiment results show that shutdown regulations on restaurants have decresed xxx%....."
+The survey result indicates that shutdown restrictions have negative impacts on restaurant employment, sales and future operation.
+However, the higher increased COVID cases in the reopened city sugguests the Ontario government to mindfully plan for futher policy decisions."
 output:
@@
 
+&nbsp; &nbsp; The COVID-19 pandemic has impacted many businesses, including restaurants, and resulted in mass-layoffs of workers throughout the world.
+According to HuffPost [@cite_unemployment], “Canada's unemployment rate was 13.5% in May 2020, the highest it has been since 1976” [@cite_wikiemploy].
+However, the unemployment crisis in Canada, which would result in rising rates of depression, suicide, frustration, crime, and other unprecedented social issues, was proactively considered and managed by the Government of Canada.
+The Canada Emergency Wage Subsidy (CEWS) [@cite_CEWS] as well as the Canada Emergency Rent Subsidy (CERS) [@cite_CERS] programs were enacted swiftly and served as much needed lifelines for businesses to survive.
+The Ontario government also provided a range of support such as provincial tax rebates, loans and debt relief interventions, utility bill payment reductions, business grants, and low-interest loans, etc[@cite_reopening].
+
+&nbsp; &nbsp; To help recover from the current recession, we at Petit Poll have partnered with the Ontario government to examine the effects and scope of COVID shutdown on restaurants.
+We conducted an experiment by selecting two statistically similar cities in Ontario and investigated how reopening the dine-in services for restaurants in one city has prevailed over the state of continued shutdown in another city.
+We compared unemployment rates, restaurant profitability, and the expected financial and social impact in both circumstances.
+The results showed that general satisfaction, a sense of purpose, hope, and profitability increase among the businesses that were allowed to re-open.
+The findings can be generalized to other similar businesses and their associated families and business partners in that city as well.
+In addition, the governmental support programs for small businesses in both cities contributed substantially to the social wellbeing and recovery pathway of all businesses.
+However, the higher comparative rate of COVID cases in the city under treatment resulted in general anxiety among residents, triggered the social health advocates and activists to criticize the government reopening effort, and undermined the projected benefits.
+We then came across the trade-off between opening or closing the public parts of restaurants - or other similar businesses, for which we suggested utilizing SSM (Soft System Methodology) to collect, consider and accommodate all residents' perspectives and potential viewpoints in society.
+
 # Data
@@
 
+&nbsp; &nbsp; Starting from October, 2020, the Ontario government reopened Peterborough while keeping shutdown restrictions on the rest of Ontario regions.
+After a three month period in January 2021, we at Petit Poll started to conduct survey on restaurants in Peterborough and Bratford about their business performance from October to December.
+Survey results are released in February 2021.
+
 ## Sampling Methods
 
-This experiment considered all Ontario restaurants as its target population.
+**This experiment considered all Ontario restaurants as its target population.
 The frame population was decided by randomly selecting 100 restaurants from Brantford and 100 from Peterborough.
-To ensure the external validity of the experiment, we used the following steps to find these restaurants:
+To ensure the external validity of the experiment, we used the following steps to find these restaurants: **
 
@@
 A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.
+
+## Main Survey Results
+```{r, include=FALSE}
+# read in survey data
+simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
+```
+
+```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+    geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
+   theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Number of Laid-offs")+
+  ggtitle("Layoff Situation due to COVID 19")+
+  guides(fill=guide_legend(title="City"))
+
+```
+
+The above figure (Figure \@ref(fig:question3)) shows that restaurants in Peterborough had lower rates of layoff compared to restaurants in Brantford, suggesting families in Peterborough to have experienced better financial situations and probably less stress.
+
+```{r q4, fig.align='center', fig.cap="Total Sales Volume Change Oct to Dec vs July to Sept in 2020", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+
+q4_table <- data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))
+data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1,"Prefer not to say", "Decreased more than 10%","Decreased 5% ~ 10%","Roughly unchanged","Increased 5% ~ 10%","Increased more than 10%")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Total Sale Change")+
+  ggtitle("Total Sales Volume Change Oct to Dec vs July to Sept in 2020")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+```
+From Figure \@ref(fig:q4), we notice a considerable increase in sales in Peterborough during the reopen period.
+This indicated that if restaurants were open, people would had used their dine-in services, regardless of potential pandemic risks.
+Besides, this result also corresponds with lower layoffs in Peterborough since restaurants need staff for their dine-in areas to operate.
+
+In contrast, continuing shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for those restaurants.
+We propose possible reasons for the decrease in restaurant sales: (1) Residents in Brantford changed their mealing behaviors to cook more by themselves, instead of relying on meals from restaurants.
+(2) The continuing shutdown resulted in closures of other businesses, so these business staffs were not contributing for the restaurant sales anymore.
+
+The increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.
+This change admits that the restaurants probably should have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
+Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
+So we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
+
+```{r q5, fig.align='center', fig.cap="Total Cost Volume Change Oct to Dec vs July to Sept in 2020", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+
+q5_table <- data.frame(table(simulated_dataset$q5_total_cost,simulated_dataset$q1_city))
+q5_table <-  q5_table %>% add_row(Var1 = "Decreased by more than 25%", Var2 = "Peterborough", Freq = 0) %>%
+  add_row(Var1 = "Decreased by more than 25%", Var2 = "Brantford", Freq = 0)
+q5_table%>%
+  mutate(Var1 = fct_relevel(Var1,"Prefer not to say","Decreased by more than 25%", "Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% ~ 25%","Increased by more than 25%")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Total Cost Change")+
+  ggtitle("Total Cost Volume Change Oct to Dec vs July to Sept in 2020")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+
+```
+The following figure (\@ref(fig:q8)) demonstrates restaurant owners' opinions towards the expected survivability of their businesses.
+It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during these continuing shutdown period.
+While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.
+```{r q8, fig.align='center', fig.cap="Expected Survival Time if Current Situation Continues", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+# Use
+
+data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
+    mutate(Var1 = fct_relevel(Var1 ,"Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Expected Survival Time")+
+  ggtitle("Expected Survival Time if Current Situation Continues")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+```
+
+```{r q10, fig.align='center', fig.cap="Expected Recovery Time Back to pre-COVID Situation", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+# use
+data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulated_dataset$q2_type))%>%
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than 18 months","12 to 18 months","7 to 12 months","Six months or less")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge())+
+  theme(plot.title = element_text(hjust = 0.5)) +
+  facet_wrap(~Var3)+
+  ylab("Number of responses")+
+  xlab("Number of months")+
+  ggtitle("Expected Recovery Time Back to pre-COVID Situation")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+
+```
+Although from Figure \@ref(fig:q8), we a pervasive gloom among the Brantford restaurants, Figure \@ref(fig:q10) illustrates that even if the pandemic ends immediately, many restaurants in Brantford, especially quick-service restaurants, have indicated that it is difficult to return to the state of operation before the COVID-19 outbreak.
+While for Peterborough, although some of them suspect the recovery will take more than a year to recoup with the previous situation, most of them indicated this period would be less than a year.
+
+In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) illustrate that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, hold negative views to recover back to pre-COVID operating situation in a short period of time.
+For restaurants in Peterborough, despite some suspicions to recoup with the pre-COVID situation in more than a year, most of them expected to recovery in less than a year.
+Therefore, we believe that the continuing shutdown in Brantford have harmed expectations of future operation possibilities in Brantford, while the reopening in Peterborough has built confidence to resolve current operation difficulties.
 
@@
 So the treatment of reopening Peterborough would not affect the mealing behavior in Brantford.
-However, residents in shutdown regions near Peterborough might go for dine-in meals, increasing sales in Peterborough restaurants.
+However, residents in shutdown regions near Peterborough might go for dine-in meals, potentially increasing sales in Peterborough restaurants.
 The actual shutdown effect on restaurants could be overestimated due to possible increase in sales from nearby shutdown regions' residents.
@@
 * The mindful comparison between cities' similarities on employment, population density, etc.
-ensures the internal validity of our experiment so that we could accurately estimate the true impact of the shutdown restriction on restaurant.
-However, the shutdown effect evaluation may not be generalized to the entire population of interest, i.e.
-all restaurants in Ontario such as township regions or cosmopolitan city Toronto.
+ensures the internal validity of our experiment so that we could accurately estimate the true impact of shutdown restrictions on restaurant.
+However, our shutdown effect evaluation may not be generalized to the entire population of interest, i.e.
+all restaurants in Ontario such as township regions or cosmopolitan city Toronto due to different levels of competitions, operating costs, etc.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Sampling Method
+## Concerns about Sampling Method
 
@@
 
-## Third discussion point
+## Survey Results and Policy Implication
 
-## Weaknesses and next steps
+According to survey questions 3-17 in section 2, Peterborough restaurants indicated to be more cheerful to carry on with their businesses in future.
+They found the COVID-19 situation remediable, demonstrated the desire to further invest in their career, and revealed to be an overall happier society compared to Brantford restaurant.
+As Dr.
+Ed Diener, a professor of psychology at the University of Virginia and the University of Utah, and a senior scientist for the Gallup Organization stated in his interview with Sherif Arafa(https://greatergood.berkeley.edu/article/item/why_governments_should_care_more_about_happiness), “The deep and long-lasting sources of happiness contribute to what we call sustainable happiness, which is lasting, not just momentary”.
+He continues “we find that sustainable happiness leads to:
+·       Better health and longevity: Happy people live longer and experience better health.
+·       Superior work performance, especially organizational citizenship.
+·       More supportive social relationships—for example, being less likely to get divorced.
+·       Better citizenship and more “prosocial” behaviors—for example, being more likely to help others, volunteer, or donate money to charity.
+·       Better mental health and resilience when confronted by stressful events—for example, being less likely to suffer from mental health problems such as depression, and more likely to bounce back after something bad happens.
+The benefits of sustainable happiness are broad and important.
+They cannot be ignored.
+To repeat: Happy people do not just feel better, but they function better in achieving the things we value.
+They help society.
+They help those around them to also lead high-quality lives.
+Happy people are not uncaring, selfish people.
+They have the energy and desire to work on societal problems as much as or more than others”.
+According to our finding in the above survey results, we believe reopening of the restaurants in Peterborough has resulted in “sustainable happiness” among restaurant owners in this city.
+Further to that, we didn’t find a substantial reason to not generalize these results to other similar businesses who need to provide physical areas to serve their clients respectively.
+Adhering to strict preventing regulations, this would include professional services like clinical treatments, open area sports and other applicable safe businesses.
+We also argue that the  resulted happiness, which was proactively forethought and managed by the Government of Canada by offering supportive programs such as Canada Emergency Wage Subsidy (CEWS), Canada Emergency Loan Subsidy (CELS), business grants and low interest loans, will not only decrease the rates of depression, suicide, frustration, crime, and other unprecedented social issues among this society, it will definitely leave a sense of trust, confidence and faith among the adolescence who usually start their career with a pat-time student work in restaurants.
+According to (https://www.sciencedaily.com/releases/2011/08/110822091859.htm), “the relative intensity of these emotions (happiness and depression among adolescents) is also important.
+The odds of drug use were notably lower for youth who reported that they were more often happy than depressed and were substantially higher for those who indicated that they were more depressed than happy”.
+To this point, we strongly believe that the value of our understudy treatment “the reopening restaurants in Peterborough” has been realized and will continue in future.
 
-Weaknesses and next steps should also be included.
+On the other hand, the result of covid cases (((((reference???))))))) revealed a new safety related concern.
+The higher rate of Corona incidents, fear and mortality among Peterborough people, compared to the residents of Brantford, take us to the emergence of a new argument, “how do you find the overall happiness among people in a city, not solely among the restaurant owners?”.
+Undoubtedly, more CORONA related cases fold up happiness and spread depression among society, which literally criticises the beneficial effects of above mentioned governmental supportive programs.
+
+Do we believe in absolute “safety first”?
+If we do, no doubt about keeping restaurants, and probably all other similar business activities, closed until the pandemic ends.
+And, the government should invest in other programs to insert hope, administer happiness and hinder the spread of depression.
+However, a controversial discussion would be “should considerate people pay for the negligence of defiant citizens who parade time to time at Yonge and Bloor streets in Toronto (in front of my apartment) to criticize wearing masks?”.
+Not good enough, some suspect the Corona vaccine contains microchips or 3D-camera to spy and scan their body for intelligent services!
+
+The goal of this paper is to report the dynamics of an intervention and to analyze how the results of a treatment - reopening the restaurants - would happen if in place.
+We observe a trade-off between the prosperity and hopefulness among the businesses in one city versus the lower number of COVID cases throughout the other city.
+We believe this would be a controversial discussion between citizens, activists and the government.
+At this situation, we recommend the “Soft System Methodology” (SSM) which “uses “systems thinking” in a cycle of action research, learning and reflection to help understand the various perceptions that exist in the minds of the different people involved in (one) situation” (http://www.construction-innovation.info/images/pdfs/Research_library/ResearchLibraryA/Refereed_Conference_papers/Five_Case_Studies.pdf).
+SSM contributes to better knowledge management, leading to better understanding of different existing viewpoints and also insights to different perspectives of communities.
+Gathering more information and context knowledge would more or less result in taking the most desired and applicable approach to enforce decisions and to better respond to the citizen’s needs.
 

### 2021-02-24 scripts/2178_chart_2.Rmd
Commit for discussion

@@
   ggtitle("Layoff Situation due to COVID 19")+
-
   guides(fill=guide_legend(title="City"))
@@
     main = "Peterborough: Total sales volume during Oct to Dec 2020 compared to July to Sept 2020",cex=0.6,cex.main=1)
+```
 
+```{r}
+# use
+q4_table <- data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))
+data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1,"Prefer not to say", "Decreased more than 10%","Decreased 5% ~ 10%","Roughly unchanged","Increased 5% ~ 10%","Increased more than 10%")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Total Sale Change")+
+  ggtitle("Total Sales Volume Change Oct to Dec vs July to Sept in 2020")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+```
+
+```{r}
 #Brantford
@@
 
+```
+
+```{r}
+# use
+q5_table <- data.frame(table(simulated_dataset$q5_total_cost,simulated_dataset$q1_city))
+q5_table <-  q5_table %>% add_row(Var1 = "Decreased by more than 25%", Var2 = "Peterborough", Freq = 0) %>%
+  add_row(Var1 = "Decreased by more than 25%", Var2 = "Brantford", Freq = 0)
+q5_table%>%
+  mutate(Var1 = fct_relevel(Var1,"Prefer not to say","Decreased by more than 25%", "Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% ~ 25%","Increased by more than 25%")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Total Cost Change")+
+  ggtitle("Total Cost Volume Change Oct to Dec vs July to Sept in 2020")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+```
+
+```{r}
 #Brantford
@@
   ggplot(aes(Var1, Freq,fill=Var2)) +
-    geom_bar(stat = "identity",position = position_dodge())+
+    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
   ylab("Number of responses")+
@@
 
-# Q15
+# Q11
 

### 2021-02-24 scripts/06_simulate_survey_responses.R

@@ -116,11 +116,11 @@ treat_data<-tibble(
   q3_layoff=sample(x=c("0","1-4","5-10","More than 10","Prefer not to say"),number_of_treated,replace = TRUE, prob = c(0.48,0.36,0.1,0.03,0.03)),
   q4_total_sales=sample(c("Increased more than 10%","Increased 5% ~ 10%","Roughly unchanged","Decreased 5% ~ 10%","Decreased more than 10%","Prefer not to say"), number_of_treated, replace = TRUE, 
                         prob = c(0.12,0.44,0.2, 0.08, 0.16,0)),
-  q5_total_cost=sample(c("Decreased more than 25%","Decreased by 5% – 25%","Roughly unchanged","Increased by  5% – 25%","Increased by more than 25% ","Prefer not to say"),number_of_treated,
+  q5_total_cost=sample(c("Decreased more than 25%","Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% ~ 25%","Increased by more than 25% ","Prefer not to say"),number_of_treated,
                        replace = TRUE, prob = c(0, 0.03, 0.32, 0.43, 0.15, 0.07)),
-  q6_order=sample(c("Decreased more than 25%","Decreased by 5% – 25%","Roughly unchanged","Increased by  5% – 25%","Increased more than 25%","Prefer not to say"),
+  q6_order=sample(c("Decreased more than 25%","Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% ~ 25%","Increased more than 25%","Prefer not to say"),
                   number_of_treated, replace = TRUE, prob = c(0.08, 0.15, 0.24, 0.39, 0.1, 0.04)),
-  q7_revenue=sample(c("Decreased more than 25%","Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% – 25%","Increased more than 25%","Prefer not to say"),
+  q7_revenue=sample(c("Decreased more than 25%","Decreased by 5% ~ 25%","Roughly unchanged","Increased by  5% ~ 25%","Increased more than 25%","Prefer not to say"),
                     number_of_treated, replace = TRUE, prob = c(0.25, 0.22, 0.26, 0.1, 0.14, 0.03)),
   q8_survive=sample(c("Less than 3 months","3 to 6 months","Longer than 6 months","Unknown","Prefer not to say"),
                     number_of_treated, replace = TRUE, prob = c(0.08, 0.27, 0.57, 0.05, 0.03)),

### 2021-02-24 scripts/07_simulate_graphs_in_paper.R

@@ -22,16 +22,113 @@ library(janitor)
 # Import Dataset
 
 
+simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
 
+# Question3 How many employees have you laid off because of COVID 19? 
 
-
-
-
-
-
-
-
+data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Number of Laid-offs")+
+  ggtitle("Layoff Situation due to COVID 19")+
+  guides(fill=guide_legend(title="City"))
 
 
 # Referenced the following link to reorder responses
 #https://www.r-graph-gallery.com/267-reorder-a-variable-in-ggplot2.html
+# Question4 How was your total sales volume during Oct to Dec 2020 compared to July to Sept 2020?
+
+q4_table <- data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))
+data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1,"Prefer not to say", "Decreased more than 10%","Decreased 5% ~ 10%","Roughly unchanged","Increased 5% ~ 10%","Increased more than 10%")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  theme_minimal()+
+  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  ylab("Number of Responses")+
+  xlab("Total Sale Change")+
+  ggtitle("Total Sales Volume Change Oct to Dec vs July to Sept in 2020")+
+  guides(fill=guide_legend(title="City"))+
+  coord_flip()
+
+#Question 5. How was your total costs volume during Oct to Dec 2020 compared to July to Sept 2020?
+
+
+q5_table <- data.frame(table(simulated_dataset$q5_total_cost,simulated_dataset$q1_city))
+
+# Even though there is no responses for "Decreased by more than 25%" in both city, we still need to include them as a option in our survey
[…]

### 2021-02-25 outputs/paper/paper.Rmd
changes: - presurvey - Discussion_ sampling limitation #2 - Discussion #3

@@
   bookdown::pdf_document2:
+    latex_engine: xelatex
 toc: FALSE
 bibliography: references.bib
+
 ---
@@
 
-**This experiment considered all Ontario restaurants as its target population.
+A presurvey with five questions was conducted before the decision on intervention was made.
+The purpose was to make sure our assumptions about the resturant similarities between Petereborough and Brantford are based on concert evidence.
+We asked selected respondents about the restaurants' location, employment, sales, service types, average price per meal per person to assess whether the resturuants in the two cities are of considerable similarities.
+
+**We considered all Ontario restaurants as its target population.
 The frame population was decided by randomly selecting 100 restaurants from Brantford and 100 from Peterborough.
@@
 
-```{r samplingtable, fig.cap='Sampling Results Summary', echo=FALSE }
+```{r presamplingtable, fig.cap='Sampling Results Summary', echo=FALSE }
 tibble(
@@
   'Survey Administered' = list(100, 100),
-  'Total Sample Collected' = list(45, 48),
-  'Telephone Survey' = list(40, 41),
-  'Online Survey' = list(5, 7)
+  'Total Sample Collected' = list(50, 55),
+  'Telephone Survey' = list(43, 47),
+  'Online Survey' = list(7, 8)
 ) %>%
@@
 The telephone interview served as the primary channel and an online survey option was provided when respondents could not or prefer not to be interviewed over the phone.
-As shown in the above table (Table \@ref(tab:samplingtable)), our sampled population included 45 valid responses in Brantford and 48 collected from Peterborough, among which, 5 were collected via the online survey in Brantford and 7 were collected via the online survey in Peterborough.
+As shown in the above table (Table \@ref(tab:presamplingtable)), our sampled population included 50 valid responses in Brantford and 55 collected from Peterborough, among which, 7 were collected via the online survey in Brantford and 8 were collected via the online survey in Peterborough.
 Surveys that were not answered or have incomplete answers were treated as nonresponses and were not included in the dataset for further analysis.
@@
 The respondents were told at the beginning of the telephone survey that they could terminate the survey anytime if they want to.
-The respondents were also notified before the survey that they would have a chance to win a 50-dollar gift card if they fully participated.
+The respondents were also notified before the survey that they would have a chance to win a 10-dollar gift card if they fully participated.
 
-The survey incurred a total cost of \$10,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
+As shown in the chart below, the results for the presurvey confirmed our initial assumptions that the restururants in Peterborough and Brantford are similar enough for further study.
+Therefore, we implemented our intervention of reopening the resturuants in Peterborough.
+
+Three month after the implementation of our intervention, we conducted our formal survey using the same sampling frame and sampling methods.
+Please see the sampling details and the response rate in the table (Table \@ref(tab:presamplingtable)) below, our sampled population included 45 valid responses in Brantford and 48 collected from Peterborough, among which, 5 were collected via the online survey in Brantford and 7 were collected via the online survey in Peterborough.
+
+```{r samplingtable, fig.cap='Sampling Results Summary', echo=FALSE }
+tibble(
+  'City' = list('Brantford', 'Peterborough'), 
+  'Survey Administered' = list(100, 100),
+  'Total Sample Collected' = list(45, 48),
+  'Telephone Survey' = list(40, 41),
+  'Online Survey' = list(5, 7)
+) %>%
+  kbl(caption = 'Sampling Results Summary',
+      align = "cccc") %>%
+  kable_styling(latex_options = "hold_position")
+```
+
+The two surveys incurred a total cost of \$10,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
 A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.
+We also gave out 50 gift cards with a total worth (\$500 CAD) as incentives for higher response rate.
 
@@
 
+* Since the results of the presurvey suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar qualities.
+However, the attributes of the restaurants (size, employments, service type, etc) were not controlled in our analysis.
+In other words, we believe the response rate within the different restaurant subgroups to be the same.
+Variations in the actual response between restaurants in two cities are unknown and may impact the internal validity of the results.
+
 * The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations.
@@
 However, these may be the ones that are most severely impacted.
+Another aspect of the survivorship bias involves the use of the same sampling frame for the presurvey and the formal survey.
+Since there is a three-month time lag, some resturuants may be closed during that time.
 
@@
 ## Survey Results and Policy Implication
-
-According to survey questions 3-17 in section 2, Peterborough restaurants indicated to be more cheerful to carry on with their businesses in future.
-They found the COVID-19 situation remediable, demonstrated the desire to further invest in their career, and revealed to be an overall happier society compared to Brantford restaurant.
-As Dr.
-Ed Diener, a professor of psychology at the University of Virginia and the University of Utah, and a senior scientist for the Gallup Organization stated in his interview with Sherif Arafa(https://greatergood.berkeley.edu/article/item/why_governments_should_care_more_about_happiness), “The deep and long-lasting sources of happiness contribute to what we call sustainable happiness, which is lasting, not just momentary”.
-He continues “we find that sustainable happiness leads to:
-·       Better health and longevity: Happy people live longer and experience better health.
-·       Superior work performance, especially organizational citizenship.
-·       More supportive social relationships—for example, being less likely to get divorced.
-·       Better citizenship and more “prosocial” behaviors—for example, being more likely to help others, volunteer, or donate money to charity.
-·       Better mental health and resilience when confronted by stressful events—for example, being less likely to suffer from mental health problems such as depression, and more likely to bounce back after something bad happens.
-The benefits of sustainable happiness are broad and important.
-They cannot be ignored.
-To repeat: Happy people do not just feel better, but they function better in achieving the things we value.
-They help society.
-They help those around them to also lead high-quality lives.
-Happy people are not uncaring, selfish people.
-They have the energy and desire to work on societal problems as much as or more than others”.
-According to our finding in the above survey results, we believe reopening of the restaurants in Peterborough has resulted in “sustainable happiness” among restaurant owners in this city.
-Further to that, we didn’t find a substantial reason to not generalize these results to other similar businesses who need to provide physical areas to serve their clients respectively.
-Adhering to strict preventing regulations, this would include professional services like clinical treatments, open area sports and other applicable safe businesses.
-We also argue that the  resulted happiness, which was proactively forethought and managed by the Government of Canada by offering supportive programs such as Canada Emergency Wage Subsidy (CEWS), Canada Emergency Loan Subsidy (CELS), business grants and low interest loans, will not only decrease the rates of depression, suicide, frustration, crime, and other unprecedented social issues among this society, it will definitely leave a sense of trust, confidence and faith among the adolescence who usually start their career with a pat-time student work in restaurants.
-According to (https://www.sciencedaily.com/releases/2011/08/110822091859.htm), “the relative intensity of these emotions (happiness and depression among adolescents) is also important.
-The odds of drug use were notably lower for youth who reported that they were more often happy than depressed and were substantially higher for those who indicated that they were more depressed than happy”.
-To this point, we strongly believe that the value of our understudy treatment “the reopening restaurants in Peterborough” has been realized and will continue in future.
-
-On the other hand, the result of covid cases (((((reference???))))))) revealed a new safety related concern.
-The higher rate of Corona incidents, fear and mortality among Peterborough people, compared to the residents of Brantford, take us to the emergence of a new argument, “how do you find the overall happiness among people in a city, not solely among the restaurant owners?”.
-Undoubtedly, more CORONA related cases fold up happiness and spread depression among society, which literally criticises the beneficial effects of above mentioned governmental supportive programs.
-
-Do we believe in absolute “safety first”?
-If we do, no doubt about keeping restaurants, and probably all other similar business activities, closed until the pandemic ends.
-And, the government should invest in other programs to insert hope, administer happiness and hinder the spread of depression.
-However, a controversial discussion would be “should considerate people pay for the negligence of defiant citizens who parade time to time at Yonge and Bloor streets in Toronto (in front of my apartment) to criticize wearing masks?”.
-Not good enough, some suspect the Corona vaccine contains microchips or 3D-camera to spy and scan their body for intelligent services!
-
-The goal of this paper is to report the dynamics of an intervention and to analyze how the results of a treatment - reopening the restaurants - would happen if in place.
-We observe a trade-off between the prosperity and hopefulness among the businesses in one city versus the lower number of COVID cases throughout the other city.
-We believe this would be a controversial discussion between citizens, activists and the government.
-At this situation, we recommend the “Soft System Methodology” (SSM) which “uses “systems thinking” in a cycle of action research, learning and reflection to help understand the various perceptions that exist in the minds of the different people involved in (one) situation” (http://www.construction-innovation.info/images/pdfs/Research_library/ResearchLibraryA/Refereed_Conference_papers/Five_Case_Studies.pdf).
-SSM contributes to better knowledge management, leading to better understanding of different existing viewpoints and also insights to different perspectives of communities.
-Gathering more information and context knowledge would more or less result in taking the most desired and applicable approach to enforce decisions and to better respond to the citizen’s needs.
+-	Staffing implications 
+•	Policy implications: The Government of Ontario should continue the existing supports provided to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
+Reopening the restaurants may lead to increased employment in the corresponding area.
+-	Restaurant sales implementation 
+•	The Government should expect better sales for reopened restaurants.
+However, it is important to acknowledge that economy would take a long time to reach pre-pandemic performance.
+Continued support to restaurants may still be needed.
+-	Future projects of restaurants  
+•	Rebuilding business confidence is a crucial aspect of short-term business recovery and long-term economic stability.
+The Government should carefully monitor business projection and equip businesses with tailored supports based on their recovery needs.
+-	Striking a balance between COVID-19 cases
+•	While reopening leads to increased employment, improved restaurant sales, positive business confidence, and ultimately increased government revenue, the impact of the reopening of restaurants needs to be assessed against the situation of the pandemic.
+By closely monitoring the development of confirmed COVID-19 cases during the intervention period, we found a more rapid spread of COVID-19 cases in Peterborough compared to Brantford.
+Although more quantitative and qualitative research needs to be conducted to determine if the surge is related to the reopening intervention, the results serve as an alarming-clock for policymakers and the public.
+•	The government should strike a balance between economic recovery and public health and safety.
+The health and safety of Ontarians should always be the top priority for the government.
+The Government should carefully monitor and assess the impact of COVID-19 cases and adjust its reopening policies accordingly.
+•	In the case of reopening and possible reclosing of restaurants in a region, the government should clearly and effectively communicate the risks and harms of COVID-19 resurgence and its willingness and devotion to addressing business concerns.
 

### 2021-02-25 outputs/paper/paper.Rmd
Commit for survey screenshots

@@
 toc: FALSE
+
+header-includes:
+  \usepackage{float}
+  \floatplacement{figure}{H}
+
 bibliography: references.bib
@@
 
-# Appendix {-}
+# Appendix A
+
+Link to access the first survey about restaurant business conditions conducted in September, 2020:
+https://docs.google.com/forms/d/1Bl8CbJiN8sUbhsDdnzqP4ifIyE9KT8iJgYI9ldcR2g8
+
+```{r survey1s, echo=FALSE,fig.align='center',fig.cap="Scripts to contact with restaurant owners in the first survey", out.width = '80%'}
+# Referenced this link to include image in R markdown
+# https://stackoverflow.com/questions/25166624/insert-picture-table-in-r-markdown
+knitr::include_graphics(here("outputs/images/survey1_script.png"))
+```
+
+```{r survey1c, echo=FALSE,fig.align='center',fig.cap="Consent form of the first survey", out.width = '80%'}
+knitr::include_graphics(here("outputs/images/survey1_script.png"))
+```
+
+```{r survey1q, echo=FALSE, fig.align='center', fig.cap="Survey questions in the first survey", out.width = '80%'}
+knitr::include_graphics(here("outputs/images/survey1_question.png"))
+```
+```{r survey1t, echo=FALSE, fig.align='center', fig.cap="Thanks section of the first survey", out.width = '80%'}
+knitr::include_graphics(here("outputs/images/survey1_thanks.png"))
+```
+
+# Appendix B
+
+Link to access the second survey about impact of COVID-19 on restaurants conducted in January, 2021:
+https://docs.google.com/forms/d/1FXSeKFkvCtM41k9xFYjQQ_eDGdBs9skVYZ3zU5LNRgY
+
+```{r survey2s, echo=FALSE, fig.align='center', fig.cap="Scripts to contact with restaurant owners in the second survey", out.width = '80%'}
+knitr::include_graphics(here("outputs/images/survey2_script.png"))
+```
+
+```{r survey2c, echo=FALSE,fig.align='center',fig.cap="Consent form of the second survey", out.width = '80%'}
+knitr::include_graphics(here("outputs/images/survey2_consent.png"))
+```
+
+```{r survey2q1toq4, echo=FALSE,fig.align='center',fig.cap="Survey questions 1 - 4 in the second survey", out.width = '60%'}
+knitr::include_graphics(here("outputs/images/survey2_q1q4.png"))
+```
+
+```{r survey2q5toq8, echo=FALSE,fig.align='center',fig.cap="Survey questions 5 - 8 in the second survey", out.width = '100%'}
+knitr::include_graphics(here("outputs/images/survey2_q5q8.png"))
+```
+```{r survey2q9toq12, echo=FALSE,fig.align='center',fig.cap="Survey questions 9 - 12 in the second survey", out.width = '100%'}
+knitr::include_graphics(here("outputs/images/survey2_q9q12.png"))
+```
+
+```{r survey2q13toq15, echo=FALSE,fig.align='center',fig.cap="Survey questions 13 - 15 in the second survey", out.width = '60%'}
+knitr::include_graphics(here("outputs/images/survey2_q13q14q15.png"))
+```
+
+```{r survey2t, echo=FALSE, fig.align='center', fig.cap="Thanks section of the second survey", out.width = '80%'}
+knitr::include_graphics(here("outputs/images/survey2_thanks.png"))
+```
 

### 2021-02-25 outputs/paper/paper.Rmd
Commit for content structure

@@
 author: "Hong Shi, Hong Pan, Yixin Guan, Babak Mokri"
-thanks: "Code and data are available at: https://github.com/honn-ishinn/restaurants_covid_shutdown"
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months reopening.
-The survey result indicates that shutdown restrictions have negative impacts on restaurant employment, sales and future operation.
+The survey result indicates that shutdown restrictions have negative impacts on restaurant employment, sales and operating confidence.
 However, the higher increased COVID cases in the reopened city sugguests the Ontario government to mindfully plan for futher policy decisions."
@@
 &nbsp; &nbsp; To help recover from the current recession, we at Petit Poll have partnered with the Ontario government to examine the effects and scope of COVID shutdown on restaurants.
-We conducted an experiment by selecting two statistically similar cities in Ontario and investigated how reopening the dine-in services for restaurants in one city has prevailed over the state of continued shutdown in another city.
-We compared unemployment rates, restaurant profitability, and the expected financial and social impact in both circumstances.
-The results showed that general satisfaction, a sense of purpose, hope, and profitability increase among the businesses that were allowed to re-open.
-The findings can be generalized to other similar businesses and their associated families and business partners in that city as well.
-In addition, the governmental support programs for small businesses in both cities contributed substantially to the social wellbeing and recovery pathway of all businesses.
-However, the higher comparative rate of COVID cases in the city under treatment resulted in general anxiety among residents, triggered the social health advocates and activists to criticize the government reopening effort, and undermined the projected benefits.
-We then came across the trade-off between opening or closing the public parts of restaurants - or other similar businesses, for which we suggested utilizing SSM (Soft System Methodology) to collect, consider and accommodate all residents' perspectives and potential viewpoints in society.
+We conducted an experiment by selecting two single tier cities, namely Peterborough and Brantford, ^[Ontario's Municipal Act, 2001 defines a single-tier municipality as "a municipality, other than an upper-tier municipality, that does not form part of an upper-tier municipality for municipal purposes"] with similar restaurant operating situations in Ontario and investigated how reopening the dine-in services for restaurants in Peterborough has prevailed over the state of continued shutdown in Brantford through surveys.
+The results showed that continuing shutdown has negatively impact the employment, sales volume and operating confidence on restaurant businesses in Brantford.
+In addition, the governmental support programs contributed substantially to restaurant businesses in both reopened and shutdown cities.
+However, the higher increased COVID cases in Peterborough demonstrates the drawback of the reopening, and the Ontario government should hold a clear measure between public health and economic recovery before further policy implementations.
+
+&nbsp; &nbsp; We organize he rest of paper as follows: In Data section, we first discuss interventions of the experiment.
+Next, we introduce sampling methods and survey methodologies to collect the data.
+And then, we discuss main findings from survey results.
+In Discussion section, we would elaborate on concerns about the intervention on city selections, sampling methods and survey methodologies.
+And we also propose our thoughts on further policy implications.
+In Appendix, we include screenshots of survey contents.^[ Code and data are available at the GitHub repo: https://github.com/honn-ishinn/restaurants_covid_shutdown"]
 
@@
 It is highly risky and hasty to reopen a large area of Ontario regions for the sole purpose of our experiment.
-Therefore, we mindfully chose Peterborough, a relative small size Single-tier^[Ontario's Municipal Act, 2001 defines a single-tier municipality as "a municipality, other than an upper-tier municipality, that does not form part of an upper-tier municipality for municipal purposes"] city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
+Therefore, we mindfully chose Peterborough, a relative small size Single-tier city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
 Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns.
@@
 
-## Sampling Methods
+## Sampling Method and Survey Methodology
 
@@
 -	Staffing implications 
-•	Policy implications: The Government of Ontario should continue the existing supports provided to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
+*	Policy implications: The Government of Ontario should continue the existing supports provided to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
 Reopening the restaurants may lead to increased employment in the corresponding area.
 -	Restaurant sales implementation 
-•	The Government should expect better sales for reopened restaurants.
+*	The Government should expect better sales for reopened restaurants.
 However, it is important to acknowledge that economy would take a long time to reach pre-pandemic performance.
@@
 -	Future projects of restaurants  
-•	Rebuilding business confidence is a crucial aspect of short-term business recovery and long-term economic stability.
+*	Rebuilding business confidence is a crucial aspect of short-term business recovery and long-term economic stability.
 The Government should carefully monitor business projection and equip businesses with tailored supports based on their recovery needs.
 -	Striking a balance between COVID-19 cases
-•	While reopening leads to increased employment, improved restaurant sales, positive business confidence, and ultimately increased government revenue, the impact of the reopening of restaurants needs to be assessed against the situation of the pandemic.
-By closely monitoring the development of confirmed COVID-19 cases during the intervention period, we found a more rapid spread of COVID-19 cases in Peterborough compared to Brantford.
+
+```{r covidcase, fig.align='center', fig.cap="Total Confirmed COVID-19 cases in Peterborough and Brantford", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+  ggplot(data=covid_tracking,aes(x=track_date))+
+    geom_smooth(aes(y=covid_cases_p,color="Peterborough"))+
+    geom_smooth(aes(y=covid_cases_b,color="Brantford"))+
+    theme_minimal()+
+    scale_color_manual("City",breaks = c("Peterborough","Brantford"),
+                       values = c("red","blue"))+
+    xlab("Tracking date")+
+    scale_y_continuous("Cumulative number of confirmed cases",limits=c(0,800))+
+    labs(title = " Confirmed COVID-19 cases in Peterborough and Brantford")+
+    scale_x_date(date_labels = "%Y %b %d")+
+   theme(plot.title = element_text(hjust = 0.5)) +
+    guides(color=guide_legend(override.aes=list(fill=NA)))
+```
+
+*	While reopening leads to increased employment, improved restaurant sales, positive business confidence, and ultimately increased government revenue, the impact of the reopening of restaurants needs to be assessed against the situation of the pandemic.
+By closely monitoring the development of confirmed COVID-19 cases during the intervention period, we found a more rapid spread of COVID-19 cases in Peterborough compared to Brantford (Figure).
 Although more quantitative and qualitative research needs to be conducted to determine if the surge is related to the reopening intervention, the results serve as an alarming-clock for policymakers and the public.
-•	The government should strike a balance between economic recovery and public health and safety.
+*	The government should strike a balance between economic recovery and public health and safety.
 The health and safety of Ontarians should always be the top priority for the government.
 The Government should carefully monitor and assess the impact of COVID-19 cases and adjust its reopening policies accordingly.
-•	In the case of reopening and possible reclosing of restaurants in a region, the government should clearly and effectively communicate the risks and harms of COVID-19 resurgence and its willingness and devotion to addressing business concerns.
+*	In the case of reopening and possible reclosing of restaurants in a region, the government should clearly and effectively communicate the risks and harms of COVID-19 resurgence and its willingness and devotion to addressing business concerns.
 

### 2021-02-25 scripts/09_simulate_covid_cases.R

@@ -1,0 +1,86 @@
+#### Preamble ####
+# Purpose: This script simulate the covid cases from October to December in 2020 in Peterborough and Brantford and plot the covid trend graph.
+# Author:  Hong Shi, Hong Pan, Yixin Guan, Babak Mokri
+# Data:  "25 February 2021"
+# Contact: lancehong.shi@mail.utoronto.ca, hong.pan@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - None 
+
+
+
+#### Workspace setup ####
+
+library(tidyverse)
+library(here)
+
+#### Simulate the covid cases ####
+
+set.seed(9)
+# We assume the reopening in Peterborough to have higher reported COVID cases each day, 
+# there are 92 days from October to December, we divide them into half and expect more reported covid cases in later half period
+
+p_first46days <- rnorm(n = 46, mean = 5, sd = 3) %>% round(digits = 0) %>% abs()
+p_last46days <- rnorm(n = 46, mean = 8, sd = 4) %>% round(digits = 0) %>% abs()
+
+
+b_first46days <- rnorm(n = 46, mean = 2.5, sd = 2) %>% round(digits = 0) %>% abs()
+b_last46days <- rnorm(n = 46, mean = 3.5, sd = 2) %>% round(digits = 0) %>% abs()
+
+
+p_daily <- c(p_first46days,p_last46days)
+b_daily <- c(b_first46days,b_last46days)
+
+# Referenced the following link to get the approximate COVID cases in late September, 2020
+# https://localcovidtracker.ca/
+p_case <- 160
+b_case <- 180
+p_track <- c(0)
+b_track <- c(0)
+
+# Referenced the following link to append the value into vector
+# https://stackoverflow.com/questions/22235809/append-value-to-empty-vector-in-r
+for (i in 1:(length(p_daily)-1))
+  p_track[i+1] <- p_track[i]+p_daily[i] 
+
+for (i in 1:(length(b_daily)-1))
+  b_track[i+1] <- b_track[i]+b_daily[i]
+
+# total confirmed covid cases
+p_total <- p_case + p_track
+b_total <- b_case +b_track
+
+track_date <- seq(as.Date("2020/10/01"), as.Date("2020/12/31"), by = "day")
+
+# create the tibble of simulate cumulative covid cases
+
+covid_tracking <- 
+  data.frame(tibble(
[…]

### 2021-02-25 scripts/simulate_survey1_data.R
survey2

@@ -1,0 +1,89 @@
+#### Preamble ####
+# Purpose: This script simulates the responses to a survey about restaurants in Toronto.
+# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
+# Data:  "`r format(Sys.time(), '%d %B %Y')`"
+# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - None
+
+
+#### Workspace setup ####
+#install.packages("tibble")
+library(tibble)
+
+
+#### Questions ####
+
+# Q1: Where is your restaurant located?  
+
+# Q2: How many employees do your restaurant currently have? (Restaurant means the entity in your current location, a chain restaurant could have any entities)
+
+# Q3: Which of the following category best describe your restaurant in terms of formality?
+
+# Q4: On average, how much sales has you restaurant made monthly in the past three months? 
+
+# Q5: Which best describes the nature of your restaurant? 
+
+# Q6: How many customers could your restaurant serve at the same time? (You may skip this question if your restaurant is in quick-service)
+
+
+#### Simulate questions ####
+
+## Peterborough ##
+
+set.seed(1225)
+number_of_observation_P<-50
+
+peterborough_data<-tibble(
+  q1_city=rep("Peterborough",number_of_observation_P),
+  q2_employees=sample(x=c("Less than 5","5 -10","10 - 30","30 - 50","Prefer not to say"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.35,0.2,0.1,0.1)),
+  q3_category=sample(x=c("Fine Dining","Casual Dining"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.75)),
+  q4_sales=sample(x=c("$0 - $25,000","$25,000 - $50,000","$50,000 - $80,000","$80,000 - $110,000","$110,000 - $150,000","$150,000 or above","Prefer not to say"),
+                  size = number_of_observation_P,replace = TRUE,prob = c(0.22,0.3,0.15,0.1,0.03,0.0,0.2)),
[…]

### 2021-02-25 scripts/simulate_survey1_data.R
test

@@ -78,7 +78,7 @@ write.csv(simulated_survey1_dataset, '~/Desktop/simulated_survey1_dataset.csv')
 
 
 
-
+##
 
 
 

### 2021-02-26 outputs/paper/paper.Rmd
Commit for data findings

@@
 A presurvey with five questions was conducted before the decision on intervention was made.
-The purpose was to make sure our assumptions about the resturant similarities between Petereborough and Brantford are based on concert evidence.
+The purpose was to make sure our assumptions about the resturant similarities between Peterborough and Brantford are based on concert evidence.
 We asked selected respondents about the restaurants' location, employment, sales, service types, average price per meal per person to assess whether the resturuants in the two cities are of considerable similarities.
@@
 
+```{r}
+simulated_dataset %>%
+  tabyl(q1_city, q11_rate_support)%>%
+  adorn_totals("row")%>%
+  adorn_totals("col")%>%
+  adorn_percentages("row")%>%
+  adorn_pct_formatting(digits=2)%>%
+  adorn_ns()%>%
+  adorn_title("combined",row_name = "City", col_name = "Rating")%>%
+  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
+  kable_styling(full_width = F)
+```
+
+ As an agent to gather relevant feedback to the Ontario Government, we asked restaurants how they found the governmental support programs so far.
+According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
+```{r}
+# use
+data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
+#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
+  ylab("Number of responses")+
+  xlab("Options")+
+  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
+  guides(fill=guide_legend(title="City"))+
+  theme_minimal()+
+  theme(axis.text.x = element_text(angle = 0))+
+  coord_flip()
+```
+
+According to figure 14, Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants.
+It is reasonable for Brantford restaurants to have utilized less of this grant because CEWS covers the wages partially and yet, the employer should pay the rest of the employee’s salary.
+This is also consistent with the results in figure 3 where they indicated to have had more layoffs.
+
 # Discussion
@@
 
-* Since the results of the presurvey suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar qualities.
+* Since the results of the presurvey suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar **qualities**.
 However, the attributes of the restaurants (size, employments, service type, etc) were not controlled in our analysis.
@@
 
-* The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations.
+* **The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations.
 Restaurants that lost their businesses during the pandemic could not be captured with the current method.
@@
 Another aspect of the survivorship bias involves the use of the same sampling frame for the presurvey and the formal survey.
-Since there is a three-month time lag, some resturuants may be closed during that time.
+Since there is a three-month time lag, some restaurants may be closed during that time.**
 
@@
 -	Striking a balance between COVID-19 cases
+
+```{r}
+# readin the covid tracking data
+covid_tracking <- readr::read_csv(here::here("inputs/data/simulated_covid_data.csv"))
+```
 

### 2021-02-26 scripts/2178_chart_2.Rmd
Commit for data findings

@@
     main = "Peterborough: Is your business receiving the Canada Emergency Wage Subsidy(CEWS)? ",cex=0.6,cex.main=1)
+```
 
+```{r}
+# use
+data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
+#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
+  ylab("Number of responses")+
+  xlab("Options")+
+  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
+  guides(fill=guide_legend(title="City"))+
+  theme_minimal()+
+  theme(axis.text.x = element_text(angle = 0))+
+  coord_flip()
+```
+
+```{r}
 #Brantford

### 2021-02-26 scripts/08_create_graphs_in_paper.R

@@ -103,7 +103,7 @@ data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulat
   guides(fill=guide_legend(title="City"))+
   coord_flip()
 
-# Question 11 11. To what extent do you feel the government financial support programs helped your business survive? (1 being bad, 5 being excellent.)
+# Question 11. To what extent do you feel the government financial support programs helped your business survive? (1 being bad, 5 being excellent.)
 
 simulated_dataset %>%
   tabyl(q1_city, q11_rate_support)%>%

### 2021-02-26 outputs/paper/paper.Rmd
Commit for data discussion

@@
   \floatplacement{figure}{H}
+
+always_allow_html: yes
 
@@
 
+```{r}
+data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
+  ylab("Number of responses")+
+  xlab("Grant value")+
+  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
+  guides(fill=guide_legend(title="City"))+
+  theme_minimal()+
+  theme(axis.text.x = element_text(angle = 0))+
+  coord_flip()
+
+```
+As shown in figure 15, Peterborough restaurants have received more business loans than restaurants in Brantford.
+Since loans have to be paid back, businesses operating at low operating expectation are less likely to apply for the loans.
+And this corresponds with our previous findings of the expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) as mentioned before.
+
+**They probably see a brighter future for their business to think out their repayments accordingly.
+However, Brantford restaurants which according to figure 8 are less hopeful to their business in future, probably mutter “It is never too late to mend” and refrain adding to their liabilities, though the loan’s interest be very low.**
+
 # Discussion

### 2021-02-26 outputs/paper/paper.Rmd
Edit graphs

--- 2021-02-26 outputs/paper/paper.Rmd
@@
 header-includes:
-  \usepackage{float}
-  \floatplacement{figure}{H}
+ - \usepackage{float}
+ - \floatplacement{figure}{H}
+ - \floatplacement{table}{H}
+
+always_allow_html: yes
 
@@
 
-&nbsp; &nbsp; We organize he rest of paper as follows: In Data section, we first discuss interventions of the experiment.
+&nbsp; &nbsp; We organize the rest of paper as follows: In Data section, we first discuss interventions of the experiment.
 Next, we introduce sampling methods and survey methodologies to collect the data.
@@
 
-```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=7, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
 data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
@@
 
-The increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.
-This change admits that the restaurants probably should have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
-Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
-So we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
-
 ```{r q5, fig.align='center', fig.cap="Total Cost Volume Change Oct to Dec vs July to Sept in 2020", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
@@
 ```
-The following figure (\@ref(fig:q8)) demonstrates restaurant owners' opinions towards the expected survivability of their businesses.
-It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during these continuing shutdown period.
-While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.
+
+The increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.
+This change admits that the restaurants probably should have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
+Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
+So we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
+
 ```{r q8, fig.align='center', fig.cap="Expected Survival Time if Current Situation Continues", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
@@
 ```
+The figure (\@ref(fig:q8)) shown above demonstrates restaurant owners' opinions towards the expected survivability of their businesses.
+It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during these continuing shutdown period.
+While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.
 
@@
 
-```{r}
-simulated_dataset %>%
+```{r q11,echo=FALSE }
+t1<-simulated_dataset %>%
   tabyl(q1_city, q11_rate_support)%>%
@@
   adorn_ns()%>%
-  adorn_title("combined",row_name = "City", col_name = "Rating")%>%
-  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
+  adorn_title("combined",row_name = "City", col_name = "Rating")
+
+kable(t1, caption = 'Number or percentage of each rating level')%>%
   kable_styling(full_width = F)
+
 ```
@@
  As an agent to gather relevant feedback to the Ontario Government, we asked restaurants how they found the governmental support programs so far.
-According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
-```{r}
-# use
+According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure (Table \@ref(tab:q11)) also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
+```{r q14, fig.align='center', fig.cap="Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+
 data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
-#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","I do not know","No","Yes"))%>%
   ggplot(aes(Var1, Freq,fill=Var2)) +
@@
 
-According to figure 14, Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants.
+According to Figure \@ref(fig:q14), Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants.
 It is reasonable for Brantford restaurants to have utilized less of this grant because CEWS covers the wages partially and yet, the employer should pay the rest of the employee’s salary.
 This is also consistent with the results in figure 3 where they indicated to have had more layoffs.
+
+```{r q15, fig.align='center', fig.cap="How much loans have you applied for the COVID-19 related reasons?", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
+  ylab("Number of responses")+
+  xlab("Grant value")+
+  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
+  guides(fill=guide_legend(title="City"))+
+  theme_minimal()+
+  theme(axis.text.x = element_text(angle = 0))+
+  coord_flip()
+
+```
+As shown in Figure \@ref(fig:q15), Peterborough restaurants have received more business loans than restaurants in Brantford.
+Since loans have to be paid back, businesses operating at low operating expectation are less likely to apply for the loans.
+And this corresponds with our previous findings of the expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) as mentioned before.
+
+**They probably see a brighter future for their business to think out their repayments accordingly.
+However, Brantford restaurants which according to figure 8 are less hopeful to their business in future, probably mutter “It is never too late to mend” and refrain adding to their liabilities, though the loan’s interest be very low.**
 

### 2021-02-26 outputs/paper/paper.Rmd
Change title

@@
 
-```{r q15, fig.align='center', fig.cap="How much loans have you applied for the COVID-19 related reasons?", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+```{r q15, fig.align='center', fig.cap="Loan amount applied", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
 data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
@@
   xlab("Grant value")+
-  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
+  ggtitle("Loan amount applied for COVID-19 related reasons")+
   guides(fill=guide_legend(title="City"))+

### 2021-02-26 outputs/paper/paper.Rmd
Commit for Sampling Method

--- 2021-02-26 outputs/paper/paper.Rmd
@@
 header-includes:
-  \usepackage{float}
-  \floatplacement{figure}{H}
+ - \usepackage{float}
+ - \floatplacement{figure}{H}
+ - \floatplacement{table}{H}
 
@@
 ```{r setup, include=FALSE}
+# May install the following displaying tables
+# Reference: https://bookdown.org/yihui/bookdown/html-widgets.html
+# install.packages("webshot")
+# webshot::install_phantomjs()
+
 knitr::opts_chunk$set(echo = TRUE)
@@
 library(here)
+library(janitor)
 library(kableExtra)
+library(finalfit)
 ```
@@
 We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here], `ggpubr`[@cite_ggpubr], `janitor`[@cite_janitor] .
-We used R packages `cansim` [@cite_cansim], `httr`[@cite_httr], `xml2`[@cite_xml2] to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra], `ggrepel`[@cite_ggrepel] to format the document.
+We used R packages `cansim` [@cite_cansim], `httr`[@cite_httr], `xml2`[@cite_xml2] to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra], `ggrepel`[@cite_ggrepel], `finalfit`[@cite_finalfit] to format the document.
 We referenced `Impact Evaluation in Practice`[@cite_impact] and `Sampling Theory and Practice`[@cite_sampletheory] to design our experiment.
@@
 
-&nbsp; &nbsp; Starting from October, 2020, the Ontario government reopened Peterborough while keeping shutdown restrictions on the rest of Ontario regions.
-After a three month period in January 2021, we at Petit Poll started to conduct survey on restaurants in Peterborough and Bratford about their business performance from October to December.
-Survey results are released in February 2021.
+&nbsp; &nbsp; In September, 2020, we at Petit Poll conducted the first survey on restaurants in Peterborough and Brantford to examine their business conditions before the experiment.
+Starting from October, 2020, the Ontario government reopened Peterborough while keeping shutdown restrictions on the rest of Ontario regions.
+After a three month period in January 2021, we at Petit Poll started to conduct survey on restaurants in Peterborough and Brantford about their business performance from October to December.
+Survey results were released in February 2021.
 
@@
 
-A presurvey with five questions was conducted before the decision on intervention was made.
-The purpose was to make sure our assumptions about the resturant similarities between Peterborough and Brantford are based on concert evidence.
-We asked selected respondents about the restaurants' location, employment, sales, service types, average price per meal per person to assess whether the resturuants in the two cities are of considerable similarities.
+&nbsp; &nbsp; As we would like to understand the effect of COVID shutdowns on restaurant businesses in Ontario, we considered all restaurants in Ontario as our target population.
+According to our intervention, the frame population are all restaurants in Peterborough and Brantford.
+And approaches to obtain the sampled population is described as follow:
 
-**We considered all Ontario restaurants as its target population.
-The frame population was decided by randomly selecting 100 restaurants from Brantford and 100 from Peterborough.
-To ensure the external validity of the experiment, we used the following steps to find these restaurants: **
-
-1. Scrape the postal codes of all restaurants located within the circle of the Brantford City Centre to a 40 km radius on Yelp. And then use the same method for Peterborough.
+1.
+Scrape postal codes of all restaurants located within the circle of the Brantford City Centre to a 40 km radius on Yelp.
+And then apply the same method for Peterborough.^[Land areas of both Brantford and Peterborough are less than 100 kilometer squares, so searching restaurants 40 km within the city center almost ensures to include all restaurants in Peterborough and Brantford]
 
@@
 
-3. Compare the two lists and eliminate the restaurants with postal codes outside of Peterborough CMA and the Brantford CMA.
+3.
+Compare these two lists and eliminate restaurants with postal codes outside of Peterborough CMA and Brantford CMA to get the list of all restaurants in Brantford and Peterborough as the frame population.
 
-4. Randomly select 100 restaurants from Brantford and 100 restaurants from Peterborough to form the frame population.
+4. Randomly select 100 restaurants from Brantford and 100 restaurants from Peterborough to form the sampled population.
 
-```{r presamplingtable, fig.cap='Sampling Results Summary', echo=FALSE }
+&nbsp; &nbsp; The first survey was conducted before the decision on intervention to ensure our assumptions about restaurant similarities between Peterborough and Brantford are based on concert evidence.
+We asked selected respondents about the restaurants' employment, average monthly sales, nature and category of restaurant, restaurant capacity to examine restaurant similarities between these two cities.
+
+```{r presamplingtable, fig.cap='Sampling Summary of the First Survey', echo=FALSE }
 tibble(
@@
 ) %>%
-  kbl(caption = 'Sampling Results Summary',
+  kbl(caption = 'Sampling Summary of the First Survey',
       align = "cccc") %>%
@@
 
-We used telephone interviews and online questionnaire methods to administer the survey.
+&nbsp; &nbsp; We used telephone interviews and online questionnaire methods to administer the survey.
 The telephone interview served as the primary channel and an online survey option was provided when respondents could not or prefer not to be interviewed over the phone.
@@
 Surveys that were not answered or have incomplete answers were treated as nonresponses and were not included in the dataset for further analysis.
-The surveys were administered in the following steps:
+The surveys were administered in following steps:
 
-1. The phone number of the restaurants was scraped from Yelp while we determined the frame population.
+1. Scraped phone numbers of restaurants from Yelp while we determined the frame population.
 
@@
 3.
-When the call was connected, the survey staff would provide a brief introduction of the survey purpose and indicate that the survey was sponsored by the Ontario government.
-See Appendix A for details.
+When the call was connected, the survey staff would provide a brief introduction of the survey purpose and indicate that the survey was sponsored by the Ontario government.^[Scripts used to approach respondents are included in Appendix A and B ].
 
@@
 The respondents were told at the beginning of the telephone survey that they could terminate the survey anytime if they want to.
-The respondents were also notified before the survey that they would have a chance to win a 10-dollar gift card if they fully participated.
+The respondents were also notified before the survey that they would have a chance to win a 50-dollar gift card if they fully participated.
+```{r survey1data, include=FALSE}
+simulated_survey1_dataset <- read.csv( here('outputs/survey/simulated_first_survey.csv'))
+```
+
+```{r survey1, tab.cap="Summary Statistics for the First Survey", echo = FALSE, message = FALSE, warning=FALSE}
+f_survey <- simulated_survey1_dataset %>% 
+  summary_factorlist("q1_city", c("q3_category","q5_nature","q2_employees","q4_sales","q6_customers"),
+                     p = FALSE, 
+                     add_dependent_label = TRUE,
+                     dependent_label_prefix = "",
+                     add_col_totals = TRUE,
+                     include_row_missing_col = FALSE,
+                     col_totals_rowname = "",
+                     total_col = FALSE) %>%
+  rename(
+    Responses = ` `
+  )
+f_survey$q1_city <- NULL
+#  f_survey$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
+ f_survey <- f_survey[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
+    mutate(` ` = c("Total Samples","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","",""))
+
+kable( f_survey[,c(4,1,2,3)],caption = "Summary Statistics of the First Survey",
+       booktabs = TRUE,
+       valign='t') 
+```
 
@@
 
-Three month after the implementation of our intervention, we conducted our formal survey using the same sampling frame and sampling methods.
+After three months of our intervention, we conducted our formal survey using the same sampling frame and sampling methods.
 Please see the sampling details and the response rate in the table (Table \@ref(tab:presamplingtable)) below, our sampled population included 45 valid responses in Brantford and 48 collected from Peterborough, among which, 5 were collected via the online survey in Brantford and 7 were collected via the online survey in Peterborough.
@@
 ) %>%
-  kbl(caption = 'Sampling Results Summary',
+  kbl(caption = 'Sampling Summary of the Second Summary',
       align = "cccc") %>%
@@
 
-The two surveys incurred a total cost of \$10,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
+The two surveys incurred a total cost of \$15,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
 A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.
@@
 # read in survey data
-simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
+simulated_dataset<-read_csv(here('outputs/survey/simulated_second_survey.csv'))
 ```
@@
 
+Compared to Peterborough, restaurants in Brantford have much higher number of laid-offs (Figure \@ref(fig:question3)), suggesting the continuing shutdown greatly affected the 
 The above figure (Figure \@ref(fig:question3)) shows that restaurants in Peterborough had lower rates of layoff compared to restaurants in Brantford, suggesting families in Peterborough to have experienced better financial situations and probably less stress.
@@
 ```
-Although from Figure \@ref(fig:q8), we a pervasive gloom among the Brantford restaurants, Figure \@ref(fig:q10) illustrates that even if the pandemic ends immediately, many restaurants in Brantford, especially quick-service restaurants, have indicated that it is difficult to return to the state of operation before the COVID-19 outbreak.
-While for Peterborough, although some of them suspect the recovery will take more than a year to recoup with the previous situation, most of them indicated this period would be less than a year.
 
@@
 For restaurants in Peterborough, despite some suspicions to recoup with the pre-COVID situation in more than a year, most of them expected to recovery in less than a year.
-Therefore, we believe that the continuing shutdown in Brantford have harmed expectations of future operation possibilities in Brantford, while the reopening in Peterborough has built confidence to resolve current operation difficulties.
+Therefore, we believe that the continuing shutdown in Brantford have harmed expectations of future operation possibilities in Brantford, while the reopening in Peterborough could build confidence to alleviate current operation difficulties.
 
-```{r}
+```{r q11, tab.cap="Satisfaction Level of Government Financial Support Programs on Restaurants", echo = FALSE, message = FALSE, warning=FALSE}
 simulated_dataset %>%
@@
   adorn_title("combined",row_name = "City", col_name = "Rating")%>%
-  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
+  rename(
+    `Terrible` = `1`,
+    `Poor` = `2`,
+    `Fair` = `3`,
+    `Good` = `4`,
+    `Excellent` = `5`
+  ) %>% 
+  kable("html", align = 'ccccccc', caption = 'Satisfaction Level of Government Financial Support Programs on Restaurants') %>% 
   kable_styling(full_width = F)
@@
 
- As an agent to gather relevant feedback to the Ontario Government, we asked restaurants how they found the governmental support programs so far.
-According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
-```{r}
+ As agents to gather relevant feedbacks to the Ontario Government, we asked restaurants how they found the governmental support programs so far.
+The survey results (Table \@ref(tab:q11)) shows that both cities generally stated the effectiveness of the governmental support programs, **nevertheless, this figure  also implies to their satisfaction and also appreciation for these programs by business entities in both cities.**
+
+```{r q14, fig.align='center', fig.cap="Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
 # use
@@
 
-```{r}
+```{r q15, fig.align='center', fig.cap="Loan amount applied", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
 data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
@@
 
-## Determine the Treatment Group and Control Group
+## Survey Results and Policy Implication
+Staffing implications 
+* Our survey found restaurants in Peterborough had lower rates of layoff compared to restaurants in Brantford, suggesting that reopening restaurants may lead to more employment in the industry. 
+*	Policy implications: The Government of Ontario should continue the existing supports provided to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
+Reopening the restaurants may lead to increased employment in the corresponding area.
+Restaurant sales implementation 
+* We found a considerable increase in sales in Peterborough during the reopening period and a slight decrease in Brantford, possibly due to seasonal fluctuations.
+The results showed that reopening could lead to more business revenue for the restaurants.
+*	Policy implication: The Government should expect better sales for reopened restaurants.
+However, it is important to acknowledge that the economy would take a long time to reach pre-pandemic performance.
+Continued support to restaurants may still be needed in the near future.
+Future projects of restaurants  
+* Restaurants in Peterborough showed more optimism about their future success, while restaurants in Brantford were less confident.
+The reopening and the subsequent increase in revenue had instilled hope for the businesses.
+* Government implication: Rebuilding business confidence is a crucial aspect of short-term business recovery and long-term economic stability.
+The Government should carefully monitor business projection and equip businesses with tailored supports based on their recovery needs.
+Dependence on government support 
+* Compared with Peterborough, Bradford restaurants showed higher dependence on government programs, possibly due to the lack of strong revenue streams.
+We also found that restaurants in Peterborough are leveraging the CEWS and government loan programs more, which may be a result of increased employment and confidence in their abililties to pay back the loans.
+* Policy implication: When implementing reopening policies, the government could leverage more direct non-repayable funding support and reasonably reduce the use of indirect low-interest loans for the reopened business.
+Striking a balance between COVID-19 cases
+
+```{r coviddata, include=FALSE}
+# readin the covid tracking data
+covid_tracking <- readr::read_csv(here::here("inputs/data/simulated_covid_data.csv"))
+```
+
+```{r covidcase, fig.align='center', fig.cap="Total Confirmed COVID-19 cases in Peterborough and Brantford", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+  ggplot(data=covid_tracking,aes(x=track_date))+
+    geom_smooth(aes(y=covid_cases_p,color="Peterborough"))+
+    geom_smooth(aes(y=covid_cases_b,color="Brantford"))+
+    theme_minimal()+
+    scale_color_manual("City",breaks = c("Peterborough","Brantford"),
+                       values = c("red","blue"))+
+    xlab("Tracking date")+
+    scale_y_continuous("Cumulative number of confirmed cases",limits=c(0,800))+
+    labs(title = " Confirmed COVID-19 cases in Peterborough and Brantford")+
+    scale_x_date(date_labels = "%Y %b %d")+
+   theme(plot.title = element_text(hjust = 0.5)) +
+    guides(color=guide_legend(override.aes=list(fill=NA)))
+```
+
+*	While reopening leads to increased employment, improved restaurant sales, positive business confidence, and ultimately increased government revenue, the impact of the reopening of restaurants needs to be assessed against the situation of the pandemic.
+By closely monitoring the development of confirmed COVID-19 cases during the intervention period, we found a more rapid spread of COVID-19 cases in Peterborough compared to Brantford (Figure).
+Although more quantitative and qualitative research needs to be conducted to determine if the surge is related to the reopening intervention, the results serve as an alarming-clock for policymakers and the public.
+*	The government should strike a balance between economic recovery and public health and safety.
+The health and safety of Ontarians should always be the top priority for the government.
+The Government should carefully monitor and assess the impact of COVID-19 cases and adjust its reopening policies accordingly.
+*	In the case of reopening and possible reclosing of restaurants in a region, the government should clearly and effectively communicate the risks and harms of COVID-19 resurgence and its willingness and devotion to addressing business concerns.
+
+## Limitations in Determine the Treatment Group and Control Group
 
@@
 ensures the internal validity of our experiment so that we could accurately estimate the true impact of shutdown restrictions on restaurant.
-However, our shutdown effect evaluation may not be generalized to the entire population of interest, i.e.
+However, our shutdown effect evaluations may not be generalized to the entire population of interest, i.e.
 all restaurants in Ontario such as township regions or cosmopolitan city Toronto due to different levels of competitions, operating costs, etc.
 
-## Concerns about Sampling Method
+## Limitations in Sampling Method
 
@@
 
-* Since the results of the presurvey suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar **qualities**.
+* Since results of the first survey before implementing our experiment suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar **qualities**.
 However, the attributes of the restaurants (size, employments, service type, etc) were not controlled in our analysis.
@@
 
-## Survey Results and Policy Implication
--	Staffing implications 
-*	Policy implications: The Government of Ontario should continue the existing supports provided to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
-Reopening the restaurants may lead to increased employment in the corresponding area.
--	Restaurant sales implementation 
-*	The Government should expect better sales for reopened restaurants.
-However, it is important to acknowledge that economy would take a long time to reach pre-pandemic performance.
-Continued support to restaurants may still be needed.
--	Future projects of restaurants  
-*	Rebuilding business confidence is a crucial aspect of short-term business recovery and long-term economic stability.
-The Government should carefully monitor business projection and equip businesses with tailored supports based on their recovery needs.
--	Striking a balance between COVID-19 cases
-
-```{r}
-# readin the covid tracking data
-covid_tracking <- readr::read_csv(here::here("inputs/data/simulated_covid_data.csv"))
-```
-
-```{r covidcase, fig.align='center', fig.cap="Total Confirmed COVID-19 cases in Peterborough and Brantford", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
-  ggplot(data=covid_tracking,aes(x=track_date))+
-    geom_smooth(aes(y=covid_cases_p,color="Peterborough"))+
-    geom_smooth(aes(y=covid_cases_b,color="Brantford"))+
-    theme_minimal()+
-    scale_color_manual("City",breaks = c("Peterborough","Brantford"),
-                       values = c("red","blue"))+
-    xlab("Tracking date")+
-    scale_y_continuous("Cumulative number of confirmed cases",limits=c(0,800))+
-    labs(title = " Confirmed COVID-19 cases in Peterborough and Brantford")+
-    scale_x_date(date_labels = "%Y %b %d")+
-   theme(plot.title = element_text(hjust = 0.5)) +
-    guides(color=guide_legend(override.aes=list(fill=NA)))
-```
-
-*	While reopening leads to increased employment, improved restaurant sales, positive business confidence, and ultimately increased government revenue, the impact of the reopening of restaurants needs to be assessed against the situation of the pandemic.
-By closely monitoring the development of confirmed COVID-19 cases during the intervention period, we found a more rapid spread of COVID-19 cases in Peterborough compared to Brantford (Figure).
-Although more quantitative and qualitative research needs to be conducted to determine if the surge is related to the reopening intervention, the results serve as an alarming-clock for policymakers and the public.
-*	The government should strike a balance between economic recovery and public health and safety.
-The health and safety of Ontarians should always be the top priority for the government.
-The Government should carefully monitor and assess the impact of COVID-19 cases and adjust its reopening policies accordingly.
-*	In the case of reopening and possible reclosing of restaurants in a region, the government should clearly and effectively communicate the risks and harms of COVID-19 resurgence and its willingness and devotion to addressing business concerns.
+**High response rate:**
 

### 2021-02-26 scripts/survey1_graphs.Rmd
Commit for Sampling Method

---
title: "Untitled"
output: pdf_document

header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}
---

```{r,include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
#### Workspace setup ####
library(janitor) # Create tables
library(tidyverse)
library(kableExtra)

```

#import dataset
```{r}
simulated_survey1_dataset <- read.csv( here('outputs/survey/simulated_first_survey.csv'))
```

#q3 & 5
```{r,echo=FALSE,warning=FALSE}
t1<-simulated_survey1_dataset %>%
  tabyl(q1_city, q3_category)%>%
  adorn_totals("row", name = "Total Average")%>%
  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=1)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Category") %>% 
  rename(
    City = `City/Category`
  )
t1$Total <- NULL

t2<-simulated_survey1_dataset %>%
  tabyl(q1_city, q5_nature)%>%
  adorn_totals("row", name = "Total Average")%>%
  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=1)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Nature") %>% 
  rename(
    `Table Service` = `Table-service restaurant`,
    `Quick Service` = `Quick-service restaurant`
  )
t2$`City/Nature` <- NULL
t2$Total <- NULL
kable(
  list(t1, t2),
  caption = 'Category and Nature of Restarants',
  booktabs = TRUE, valign = 't', 
  align = "ccccc"
)

#Takeaway: similar category and nature for restaurants in Peterborough and Brantford
```

#q2

```{r,echo=FALSE}
#bar chart
#simulated_survey1_dataset%>%
#  ggplot(aes(q2_employees, fill =q1_city)) + 
#  geom_bar(position = "dodge")+
#  ylab("Number of responses")+
#  xlab("Number of employees")+
#  ggtitle('Number of employees in the two cities')+
#  theme_minimal()+
#  scale_x_discrete(limits = c("Less than 5", "5 -10", "10 - 30","30 - 50","Prefer not to say"))+
#  guides(fill=guide_legend(title="City"))

#table
t3<-simulated_survey1_dataset %>%
  tabyl(q1_city, q2_employees)%>%
#  adorn_totals("row", name ="Total Average")%>%
#  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=1)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Employees")

 kable(t3[,c(1,5,4,2,3,6)],caption = 'Number of Employees',
        booktabs=TRUE,valign='t', align = "cccccc")%>%
  kable_styling()

# Takeaways:
# From the bar chart, we can see a similar pattern in both cities-the more employees, the fewer restaurants. Most restaurants have between 5 and 10 employees.

#From table, restaurants in both cities are basically small and medium-sized, and most restaurants employ less than 30 employees.
```

#q4

```{r,echo=FALSE}
data.frame(table(simulated_survey1_dataset$q4_sales,simulated_survey1_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
    geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
   theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of Responses")+
  xlab("Sales amount")+
  ggtitle("Average monthly sales of restaurants")+
  guides(fill=guide_legend(title="City"))+
  scale_x_discrete(limits = c("$0 - $25,000", "$25,000 - $50,000", "$50,000 - $80,000","$80,000 - $110,000","$110,000 - $150,000","Prefer not to say"))+
  theme(axis.text.x=element_text(size=rel(0.8), angle=15))

#Takeaways:
#Similar pattern for two cities. The data mainly fall in the range of $0-$25,000 and $25,000 - $ 50,000. After that, the higher the sales, the fewer restaurants.

```

#q6

```{r,echo=FALSE}
simulated_survey1_dataset%>%
  ggplot(aes(q6_customers, fill =q1_city)) + 
  geom_bar(position = "dodge")+
  ylab("Number of responses")+
  xlab("Number of customers")+
  ggtitle('Number of customers served at the same time')+
  theme_minimal()+
  scale_x_discrete(limits = c("Less than 10","10 - 20", "20 - 40", "40 -70","70 -100","Prefer not to say"))+
  guides(fill=guide_legend(title="City"))+
  theme(axis.text.x=element_text(size=rel(0.8), angle=15))

#table
t4<-simulated_survey1_dataset %>%
  tabyl(q1_city, q6_customers)%>%
  adorn_totals("row")%>%
  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=1)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Customers")

 kable(t4[,c(1,6,2,3,4,5,7,8)],caption = 'Number of customers served at the same time',
        booktabs=TRUE,valign='t')%>%
  kable_styling()

 #Takeaways:
 # On average, restaurants in the two cities can serve 10 to 40 people at the same time.
```

```{r}
library(finalfit)
```
```{r}
#https://finalfit.org/articles/all_tables_examples.html

#https://stackoverflow.com/questions/32593434/r-change-row-order
tests <- simulated_survey1_dataset %>% 
  summary_factorlist("q1_city", c("q3_category","q5_nature","q2_employees","q4_sales","q6_customers"),
                     p = FALSE, 
                     add_dependent_label = TRUE,
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     total_col = FALSE) %>%
  rename(
    Responses = ` `
  ) #%>% 
 tests$q1_city <- NULL
#  tests$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
 tests <- tests[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
    mutate(group = c("Total Samples","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","",""))

tests %>% 
  kable(
    caption = "Test",
    booktabs = TRUE,
    linesep = "",
    col.names = 
  )
  mutate(group = c("","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","","")) #%>% 
  kable( tests[,c(4,1,2,3)],caption = "TEST CAPTION",
         booktabs = TRUE,
         valign='t')
    ) %>% 
  kable_styling()

```

### 2021-02-26 scripts/06_simulate_first_survey_response.R

@@ -1,17 +1,18 @@
 #### Preamble ####
-# Purpose: This script simulates the responses to a survey about restaurants in Toronto.
-# Author: Hong Shi, Yixin Guan, Babak Mokri, Hong Pan
-# Data:  "`r format(Sys.time(), '%d %B %Y')`"
-# Contact: lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca, hong.pan@mail.utoronto.ca
+# Purpose: This script simulates the responses of the first survey about restaurant business conditions 
+#          before implementing our experiment in Peterborough and Brantford
+# Author:  Hong Shi, Hong Pan, Yixin Guan, Babak Mokri
+# Data:  "25 February 2021"
+# Contact:  lancehong.shi@mail.utoronto.ca, hong.pan@mail.utoronto.ca , yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
 # - None
 
 
 #### Workspace setup ####
-#install.packages("tibble")
-library(tibble)
 
+library(tibble)
+library(here)
 
 #### Questions ####
 
@@ -32,18 +33,18 @@ library(tibble)
 
 ## Peterborough ##
 
-set.seed(1225)
-number_of_observation_P<-50
+set.seed(123)
+number_of_observation_P<-55
 
 peterborough_data<-tibble(
   q1_city=rep("Peterborough",number_of_observation_P),
-  q2_employees=sample(x=c("Less than 5","5 -10","10 - 30","30 - 50","Prefer not to say"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.35,0.2,0.1,0.1)),
+  q2_employees=sample(x=c("Less than 5","5 -10","10 - 30","30 - 50","Prefer not to say"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.35,0.2,0.05,0.15)),
   q3_category=sample(x=c("Fine Dining","Casual Dining"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.75)),
   q4_sales=sample(x=c("$0 - $25,000","$25,000 - $50,000","$50,000 - $80,000","$80,000 - $110,000","$110,000 - $150,000","$150,000 or above","Prefer not to say"),
[…]

### 2021-02-26 scripts/07_simulate_second_survey_responses.R

@@ -1,5 +1,6 @@
 #### Preamble ####
-# Purpose: This script simulates the responses to restaurant survey responses in Peterborough and Brantford.
+# Purpose: This script simulates the responses of the second survey about impact of COVID on restaurant business
+#          in Peterborough and Brantford after three months of reopening and shutdown, respectively.
 # Author:  Hong Pan, Hong Shi, Yixin Guan, Babak Mokri
 # Data:  "22 February 2021"
 # Contact:  hong.pan@mail.utoronto.ca， lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca
@@ -147,7 +148,7 @@ simulated_dataset <-
 
 #### Save and clean-up
 
-write.csv(simulated_dataset, here('outputs/survey/simulated_restaurant_data.csv'))
+write.csv(simulated_dataset, here('outputs/survey/simulated_second_survey.csv'))
 
 
 

### 2021-02-26 scripts/08_create_graphs_in_paper.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: This script create relavent graphs used in the paper.
+# Purpose: This script create relevant tables and graphs used in the paper.
 # Author:  Hong Pan, Hong Shi, Yixin Guan, Babak Mokri
-# Data:  "22 February 2021"
+# Data:  "25 February 2021"
 # Contact:  hong.pan@mail.utoronto.ca， lancehong.shi@mail.utoronto.ca, yixin.guan@mail.utoronto.ca, b.mokri@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have downloaded the "simulated_restaurant_data.csv" in "06_simulate_survey_responses.R" and saved it to outputs/survey
+# - Need to have downloaded the "simulated_first_survey.csv" in "06_simulate_first_survey_responses.R" and saved it to outputs/survey
+# - Need to have downloaded the "simulated_second_survey.csv" in "07_simulate_second_survey_responses.R" and saved it to outputs/survey
 
 
 
@@ -14,15 +15,52 @@
 
 library(here)
 library(tidyverse) # used for data manipulation
-library(ggpubr) ##for combing figures in one graph
+library(ggpubr) # for combing figures in one graph
 library(ggrepel)
 library(kableExtra)
 library(janitor)
 
+#install.packages("finalfit")
+
+library(finalfit)
 # Import Dataset
 
+# First Survey
+simulated_survey1_dataset <- read.csv( here('outputs/survey/simulated_first_survey.csv'))
 
-simulated_dataset<-read_csv(here('outputs/survey/simulated_restaurant_data.csv'))
+# Second Survey
+simulated_dataset<-read_csv(here('outputs/survey/simulated_second_survey.csv'))
+
+#################   First Survey   ###############
+
+# get the summary statistics of the first survey
+# Referenced the following link to create this amazing summary table: https://finalfit.org/articles/all_tables_examples.html
+# Referenced the following link to change the order of rows: https://stackoverflow.com/questions/32593434/r-change-row-order
+
+f_survey <- simulated_survey1_dataset %>% 
+  summary_factorlist("q1_city", c("q3_category","q5_nature","q2_employees","q4_sales","q6_customers"),
+                     p = FALSE, 
+                     add_dependent_label = TRUE,
+                     dependent_label_prefix = "",
+                     add_col_totals = TRUE,
+                     include_row_missing_col = FALSE,
[…]

### 2021-02-26 outputs/paper/paper.Rmd
Commit for modifications

@@
 The Canada Emergency Wage Subsidy (CEWS) [@cite_CEWS] as well as the Canada Emergency Rent Subsidy (CERS) [@cite_CERS] programs were enacted swiftly and served as much needed lifelines for businesses to survive.
-The Ontario government also provided a range of support such as provincial tax rebates, loans and debt relief interventions, utility bill payment reductions, business grants, and low-interest loans, etc[@cite_reopening].
+The Ontario government also provided a range of support such as provincial tax rebates, loans and debt relief interventions, utility bill payment reductions, business grants, and low-interest loans, etc [@cite_reopening].
 
@@
 &nbsp; &nbsp; Our data explores shutdown effects on restaurant businesses in Ontario.
-We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr`[@cite_stringr],  `here` [@cite_here], `ggpubr`[@cite_ggpubr], `janitor`[@cite_janitor] .
-We used R packages `cansim` [@cite_cansim], `httr`[@cite_httr], `xml2`[@cite_xml2] to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra`[@cite_kableextra], `ggrepel`[@cite_ggrepel], `finalfit`[@cite_finalfit] to format the document.
-We referenced `Impact Evaluation in Practice`[@cite_impact] and `Sampling Theory and Practice`[@cite_sampletheory] to design our experiment.
+We analyzed it using R [@citeR], and packages `tidyverse` [@cite_tidyverse], `stringr` [@cite_stringr],  `here` [@cite_here], `ggpubr` [@cite_ggpubr], `janitor` [@cite_janitor] .
+We used R packages `cansim` [@cite_cansim], `httr` [@cite_httr], `xml2` [@cite_xml2] to decide our intervention and sampling method, and packages `bookdown` [@cite_bookdown], `kableExtra` [@cite_kableextra], `ggrepel` [@cite_ggrepel], `finalfit` [@cite_finalfit] to format the document.
+We referenced `Impact Evaluation in Practice` [@cite_impact] and `Sampling Theory and Practice` [@cite_sampletheory] to design our experiment.
 
@@
 Therefore, we mindfully chose Peterborough, a relative small size Single-tier city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
-Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approach to examine the similarities of these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns.
+Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approaches to select these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns.
 In our experiment, we assigned restaurants in Peterborough as the treatment group and those in Brantford as the control group.
@@
 According to our intervention, the frame population are all restaurants in Peterborough and Brantford.
-And approaches to obtain the sampled population is described as follow:
+We used the following approaches to obtain the sampled population as below:
 
@@
 The telephone interview served as the primary channel and an online survey option was provided when respondents could not or prefer not to be interviewed over the phone.
-As shown in the above table (Table \@ref(tab:presamplingtable)), our sampled population included 50 valid responses in Brantford and 55 collected from Peterborough, among which, 7 were collected via the online survey in Brantford and 8 were collected via the online survey in Peterborough.
-Surveys that were not answered or have incomplete answers were treated as nonresponses and were not included in the dataset for further analysis.
-The surveys were administered in following steps:
+As shown in the above table (Table \@ref(tab:presamplingtable)), our sampled population included 50 valid responses in Brantford and 55 in Peterborough.
+And among which, 7 were collected via the online survey in Brantford and 8 were collected via the online survey in Peterborough.
+Surveys that were not answered or have incomplete answers were treated as nonresponses and were not included in the dataset for further analysis^[Exception for Question 6 of the first survey, which respondents could skip the question].
+The survey was administered in following steps:
 
@@
 4.
-To ensure the quality and accuracy of the data collection, the survey staff would ask if the respondent at the restaurant worked at a management-level position in the restaurant or was familiar with the restaurant’s sales performance.
+To ensure the quality and accuracy of data collection, survey staffs would ask if the respondent at the restaurant worked at a management-level position in the restaurant or was familiar with the restaurant’s sales performance.
 If the respondent answered no, the survey staff would ask the caller to pass the call to the relevant staff in the restaurant.
 If that staff was not available, the survey staff will schedule another call or provide the online questionnaire based on the preference identified by the respondent.
-Respondents who were interested in answering the questions via online questionnaires could leave their email addresses and have two weeks to complete the survey questions.
+Respondents who were interested in answering questions via online questionnaires could leave their email addresses and have two weeks to complete survey questions.
 
@@
 6.
-To address privacy concerns and to increase the response rate, the respondents were notified before the survey that all answers were recorded anonymously.
-The respondents were told at the beginning of the telephone survey that they could terminate the survey anytime if they want to.
-The respondents were also notified before the survey that they would have a chance to win a 50-dollar gift card if they fully participated.
+To address privacy concerns and to increase the response rate, respondents were notified before the survey that all answers were recorded anonymously.
+Respondents were told at the beginning of the telephone survey that they could terminate the survey anytime if they want to.
+Respondents were also notified before the survey that they would have a chance to win a 50-dollar gift card if they fully participated.
 ```{r survey1data, include=FALSE}
@@
   )
+# drop first column
 f_survey$q1_city <- NULL
-#  f_survey$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
+# Manually change the order of the factor levels to have a better visualization, 
+# since finalfit package display the response in first appearance of the dataset
  f_survey <- f_survey[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
@@
 ```
+&nbsp; &nbsp; From the summary statistics of the first survey as shown above (Table \@ref(tab:survey1), values inside the bracket represent percentage), we find that the distribution of category, nature, number of employees, average monthly sales and capacity of restaurants is closely identical between Peterborough and Brantford.
+These results confirm our initial assumptions that restaurants in these two cities are similar enough to implement our intervention of reopening the Peterborough.
 
-As shown in the chart below, the results for the presurvey confirmed our initial assumptions that the restururants in Peterborough and Brantford are similar enough for further study.
-Therefore, we implemented our intervention of reopening the resturuants in Peterborough.
+&nbsp; &nbsp; After three months of our intervention, we conducted the second survey on the same sampled population with same sampling methods.
+The second survey (Table \@ref(tab:samplingtable)) included 45 valid responses in Brantford and 48 in Peterborough.
+And among which, 5 were collected via the online survey in Brantford and 7 in Peterborough.
 
-After three months of our intervention, we conducted our formal survey using the same sampling frame and sampling methods.
-Please see the sampling details and the response rate in the table (Table \@ref(tab:presamplingtable)) below, our sampled population included 45 valid responses in Brantford and 48 collected from Peterborough, among which, 5 were collected via the online survey in Brantford and 7 were collected via the online survey in Peterborough.
-
-```{r samplingtable, fig.cap='Sampling Results Summary', echo=FALSE }
+```{r samplingtable, fig.cap='Sampling Summary of the Second Survey', echo=FALSE }
 tibble(
@@
 ) %>%
-  kbl(caption = 'Sampling Summary of the Second Summary',
+  kbl(caption = 'Sampling Summary of the Second Survey',
       align = "cccc") %>%
@@
 
-The two surveys incurred a total cost of \$15,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
+&nbsp; &nbsp; Two surveys incurred a total cost of \$15,000 CAD, which was mainly used to hire and train staff to conduct the telephone survey, collect data and administer the online survey if applicable.
 A small portion of the cost (\$500 CAD) was used for online survey technology support and database maintenance.
-We also gave out 50 gift cards with a total worth (\$500 CAD) as incentives for higher response rate.
+We also gave out 20 gift cards with a total worth (\$500 CAD) as incentives for higher response rate.
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
 
 ## Main Survey Results
+
+&nbsp; &nbsp; The second survey examined two parts of our interests: (1) Effects of the intervention on restaurant business conditions.
+(2) Effects of the government support during the intervention.
+Respondents answered survey questions based on the intervention period.
+Several key findings are discussed in the following:
+
+### Business Conditions
+
 ```{r, include=FALSE}
@@
 
-```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=7, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+
+# Question3 How many employees have you laid off because of COVID 19?
+
 data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
@@
 
-Compared to Peterborough, restaurants in Brantford have much higher number of laid-offs (Figure \@ref(fig:question3)), suggesting the continuing shutdown greatly affected the 
-The above figure (Figure \@ref(fig:question3)) shows that restaurants in Peterborough had lower rates of layoff compared to restaurants in Brantford, suggesting families in Peterborough to have experienced better financial situations and probably less stress.
+&nbsp; &nbsp; Compared to Peterborough, restaurants in Brantford have much higher number of layoffs (Figure \@ref(fig:question3)), suggesting that the continuing shutdown greatly affected the employment situation in Brantford.
+In Peterborough, there are considerable amount of restaurants with no layoffs, implying that restaurants would require certain number of staffs to operate the dine-in service after reopening.
 
 ```{r q4, fig.align='center', fig.cap="Total Sales Volume Change Oct to Dec vs July to Sept in 2020", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+
+# Question4 How was your total sales volume during Oct to Dec 2020 compared to July to Sept 2020?
 
@@
 ```
-From Figure \@ref(fig:q4), we notice a considerable increase in sales in Peterborough during the reopen period.
+&nbsp; &nbsp; From Figure \@ref(fig:q4), we notice a considerable increase in sales in Peterborough during the reopen period.
 This indicated that if restaurants were open, people would had used their dine-in services, regardless of potential pandemic risks.
-Besides, this result also corresponds with lower layoffs in Peterborough since restaurants need staff for their dine-in areas to operate.
 
-In contrast, continuing shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for those restaurants.
+&nbsp; &nbsp; In contrast, continuing shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for those restaurants.
 We propose possible reasons for the decrease in restaurant sales: (1) Residents in Brantford changed their mealing behaviors to cook more by themselves, instead of relying on meals from restaurants.
 (2) The continuing shutdown resulted in closures of other businesses, so these business staffs were not contributing for the restaurant sales anymore.
-
-The increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.
-This change admits that the restaurants probably should have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
-Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
-So we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
+(3) There exists some seasonal fluctuations on food service industries.
 
 ```{r q5, fig.align='center', fig.cap="Total Cost Volume Change Oct to Dec vs July to Sept in 2020", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
+
+#Question 5. How was your total costs volume during Oct to Dec 2020 compared to July to Sept 2020?
 
@@
 ```
-The following figure (\@ref(fig:q8)) demonstrates restaurant owners' opinions towards the expected survivability of their businesses.
-It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during these continuing shutdown period.
+
+&nbsp; &nbsp; Increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.
+This change admits that restaurants would have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
+Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
+So we consider the increased cost in restaurants during the reopening period as a good signal for economic wellbeing.
+
+&nbsp; &nbsp; The figure (\@ref(fig:q8)) shown below illustrates respondents' opinions towards the expected survivability of their businesses.
+It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during this continuing shutdown period.
 While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.
+
 ```{r q8, fig.align='center', fig.cap="Expected Survival Time if Current Situation Continues", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
-# Use
+# Question 8. If current conditions continue, how long do you expect your business to survive before you will have to close down permanently?
 
@@
 ```{r q10, fig.align='center', fig.cap="Expected Recovery Time Back to pre-COVID Situation", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
-# use
+# Question 10. If COVID-19 situation stops now, how many months do you expect your business to recover to the previous level?
+
 data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulated_dataset$q2_type))%>%
@@
 
-In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) illustrate that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, hold negative views to recover back to pre-COVID operating situation in a short period of time.
+&nbsp; &nbsp; In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) show that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, hold negative views to recover back to pre-COVID operating situation in a short period of time.
 For restaurants in Peterborough, despite some suspicions to recoup with the pre-COVID situation in more than a year, most of them expected to recovery in less than a year.
@@
 
-```{r q11, tab.cap="Satisfaction Level of Government Financial Support Programs on Restaurants", echo = FALSE, message = FALSE, warning=FALSE}
+### Government Support
+
+&nbsp; &nbsp; As agents to gather relevant feedbacks for the Ontario Government, we asked respondents' opinions towards the helpfulness of government financial support programs.
+Survey results (Table \@ref(tab:q11)) show that both cities generally treat support programs as helpful, especially in Brantford where the shutdown restriction was still implementing.
+From previous gloom results on restaurant business conditions, it is not a surprise that restaurants in Brantford require more government financial supports.
+
+```{r q11, tab.cap="Helpfulness of Government Financial Support Programs on Restaurants", echo = FALSE, message = FALSE, warning=FALSE}
+
+# Question 11 To what extent do you feel the government financial support programs helped your business survive? (1 being terrible, 5 being excellent.)
 simulated_dataset %>%
   tabyl(q1_city, q11_rate_support)%>%
-  adorn_totals("row")%>%
-  adorn_totals("col")%>%
+  adorn_totals("row", name = "Average")%>%
   adorn_percentages("row")%>%
@@
   ) %>% 
-  kable("html", align = 'ccccccc', caption = 'Satisfaction Level of Government Financial Support Programs on Restaurants') %>% 
-  kable_styling(full_width = F)
+  kable(align = 'ccccccc', caption = 'Helpfulness of Government Financial Support Programs on Restaurants') %>% 
+  kable_styling(latex_options = "hold_position")
 ```
 
- As agents to gather relevant feedbacks to the Ontario Government, we asked restaurants how they found the governmental support programs so far.
-The survey results (Table \@ref(tab:q11)) shows that both cities generally stated the effectiveness of the governmental support programs, **nevertheless, this figure  also implies to their satisfaction and also appreciation for these programs by business entities in both cities.**
+As shown in Figure \@ref(fig:q14), restaurants in Peterborough have applied more business loans than those in Brantford during the intervention.
+Since loans have to be paid back, businesses at low operating confidence are less likely to apply for loans.
+With increased business opportunities after reopening, respondents were more likely to invest for faster recovery, and this corresponds with our previous findings of longer expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) in Peterborough restaurants as mentioned before.
 
-```{r q14, fig.align='center', fig.cap="Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
-# use
-data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
-#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
+```{r q14, fig.align='center', fig.cap="Loans Applied for COVID-19 Related Reasons", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
   ggplot(aes(Var1, Freq,fill=Var2)) +
@@
   ylab("Number of responses")+
-  xlab("Options")+
-  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
+  xlab("Loan Amount")+
+  ggtitle("Loans Applied for COVID-19 Related Reasons")+
+  guides(fill=guide_legend(title="City"))+
+  theme_minimal()+
+  theme(axis.text.x = element_text(angle = 0))+
+  coord_flip()
+
+```
+
+In contrast, restaurants in Brantford generally receives more grants than those in Peterborough(Figure \@ref(fig:q14)).
+Since grants are non-repayable funds and need certain conditions to apply, restaurants in Peterborough with better business conditions may not be eligible to apply for grants.
+And restaurants that suffers more in Brantford could receive more grants during the shutdown.
+
+```{r q15, fig.align='center', fig.cap="Grants Received for COVID-19 Related Reasons", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
+
+# Question 15 Including the above governmental programs (if applicable), how much grants have you received for COVID related reasons?
+
+data.frame(table(simulated_dataset$q15_grants,simulated_dataset$q1_city))%>%
+  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $40,000","$20,000 ~ $40,000","$10,000 ~ $20,000","$0 ~ $10,000")) %>% 
+  ggplot(aes(Var1, Freq,fill=Var2)) +
+  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
+  ylab("Number of responses")+
+  xlab("Grant Amount")+
+  ggtitle("Grants Received for COVID-19 Related Reasons")+
   guides(fill=guide_legend(title="City"))+
@@
 
-According to figure 14, Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants.
-It is reasonable for Brantford restaurants to have utilized less of this grant because CEWS covers the wages partially and yet, the employer should pay the rest of the employee’s salary.
-This is also consistent with the results in figure 3 where they indicated to have had more layoffs.
-
-```{r q15, fig.align='center', fig.cap="Loan amount applied", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
-data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
-  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
-  ggplot(aes(Var1, Freq,fill=Var2)) +
-  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
-  ylab("Number of responses")+
-  xlab("Grant value")+
-  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
-  guides(fill=guide_legend(title="City"))+
-  theme_minimal()+
-  theme(axis.text.x = element_text(angle = 0))+
-  coord_flip()
-
-```
-As shown in figure 15, Peterborough restaurants have received more business loans than restaurants in Brantford.
-Since loans have to be paid back, businesses operating at low operating expectation are less likely to apply for the loans.
-And this corresponds with our previous findings of the expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) as mentioned before.
-
-**They probably see a brighter future for their business to think out their repayments accordingly.
-However, Brantford restaurants which according to figure 8 are less hopeful to their business in future, probably mutter “It is never too late to mend” and refrain adding to their liabilities, though the loan’s interest be very low.**
-
 # Discussion
@@
 ## Survey Results and Policy Implication
-Staffing implications 
-* Our survey found restaurants in Peterborough had lower rates of layoff compared to restaurants in Brantford, suggesting that reopening restaurants may lead to more employment in the industry. 
-*	Policy implications: The Government of Ontario should continue the existing supports provided to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
-Reopening the restaurants may lead to increased employment in the corresponding area.
-Restaurant sales implementation 
-* We found a considerable increase in sales in Peterborough during the reopening period and a slight decrease in Brantford, possibly due to seasonal fluctuations.
-The results showed that reopening could lead to more business revenue for the restaurants.
-*	Policy implication: The Government should expect better sales for reopened restaurants.
-However, it is important to acknowledge that the economy would take a long time to reach pre-pandemic performance.
-Continued support to restaurants may still be needed in the near future.
-Future projects of restaurants  
-* Restaurants in Peterborough showed more optimism about their future success, while restaurants in Brantford were less confident.
-The reopening and the subsequent increase in revenue had instilled hope for the businesses.
+
+### Staffing
+
+* Our survey found that restaurants in Peterborough had lower layoff compared to those in Brantford, suggesting that reopening restaurants may lead to more employment in the industry. 
+*	Policy implications: The Ontario government should continue existing supports to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
+Reopening restaurants may lead to increased employment in corresponding areas.
+
+### Restaurant Sales
+
+* We found a considerable increase in sales in Peterborough restaurants during the reopening period and a slight decrease in Brantford restaurants, suggesting that reopening could lead to more business revenues for better economic performance.
+*	Policy implication: The Ontario government should expect better sales for reopened restaurants.
+However, it is important to acknowledge that the economy would take a long time to reach pre-pandemic performance, and restaurants may still need continued government financial supports for future recovery.
+
+### Future Projects of Restaurants
+
+* Restaurants in Peterborough showed more optimism about future operations, while restaurants in Brantford were less confident to survive during the continuing shutdown.
+The reopening and the subsequent increase in revenue had instilled hope for food service businesses.
 * Government implication: Rebuilding business confidence is a crucial aspect of short-term business recovery and long-term economic stability.
-The Government should carefully monitor business projection and equip businesses with tailored supports based on their recovery needs.
-Dependence on government support 
-* Compared with Peterborough, Bradford restaurants showed higher dependence on government programs, possibly due to the lack of strong revenue streams.
-We also found that restaurants in Peterborough are leveraging the CEWS and government loan programs more, which may be a result of increased employment and confidence in their abililties to pay back the loans.
-* Policy implication: When implementing reopening policies, the government could leverage more direct non-repayable funding support and reasonably reduce the use of indirect low-interest loans for the reopened business.
-Striking a balance between COVID-19 cases
+The Ontario government should carefully monitor business projection and equip businesses with tailored supports based on their recovery needs.
+
+### Dependence on Government Support
+
+* Compared with Peterborough, Bradford restaurants showed higher dependence on government financial support programs, especially grants, possibly due to lack of strong revenue streams.  
+* Policy implication: When implementing reopening policies, the Ontario government could leverage more direct non-repayable funding support and reasonably reduce the use of indirect low-interest loans for the reopened business.
+
+### Tradeoff between Public Health and Economy
 
@@
 *	While reopening leads to increased employment, improved restaurant sales, positive business confidence, and ultimately increased government revenue, the impact of the reopening of restaurants needs to be assessed against the situation of the pandemic.
-By closely monitoring the development of confirmed COVID-19 cases during the intervention period, we found a more rapid spread of COVID-19 cases in Peterborough compared to Brantford (Figure).
-Although more quantitative and qualitative research needs to be conducted to determine if the surge is related to the reopening intervention, the results serve as an alarming-clock for policymakers and the public.
-*	The government should strike a balance between economic recovery and public health and safety.
-The health and safety of Ontarians should always be the top priority for the government.
-The Government should carefully monitor and assess the impact of COVID-19 cases and adjust its reopening policies accordingly.
-*	In the case of reopening and possible reclosing of restaurants in a region, the government should clearly and effectively communicate the risks and harms of COVID-19 resurgence and its willingness and devotion to addressing business concerns.
+By closely monitoring the confirmed COVID-19 cases during the intervention period, we found a much faster spread of COVID-19 cases in Peterborough compared to Brantford (Figure \@ref(fig:covidcase)).
+Since the dine-in option allows customers to take off masks for meals in the restaurant, such increasing chances of direct contacts among citizens could potentially fasten the spread of COVID.
+*	The Ontario government should strike a balance between economic recovery and public health and safety.
+The health and safety of Ontario citizens should always be the top priority for the government.
+The Ontario government should carefully monitor and assess the impact of COVID-19 cases and adjust its reopening policies accordingly.
+*	In the case of reopening and possible reclosure of restaurants in certain regions, the Ontario government should clearly and effectively communicate risks and harms of COVID-19 resurgence and its willingness and devotion of business concerns.
 
-## Limitations in Determine the Treatment Group and Control Group
+## City Selection
 
@@
 We used the employment by industry data and 2016 Census data available at Statistics Canada to identify cities with similar total employment on food service and population density.
-The above point graph(Figure \@ref(fig:selectplot)) indicates that Brantford and Peterborough have similar characteristics affecting the restaurant operations.
+The above point graph(Figure \@ref(fig:selectplot)) indicates that Brantford and Peterborough have similar characteristics affecting restaurant operations.
 In addition, the coefficient of the graph $$\frac{Population\:Density}{Total \:Employment}=\frac{Total\:Population/Total\:Land\:Area}{Total\:Employment}$$, which could be interpreted as the number of people served by a restaurant employee per square kilometers, helps to identify the restaurant operating situation in designated regions.
 Similar coefficients between Brantford and Peterborough (0.306 vs 0.308) also suggest close restaurant characteristics.
-Besides, there is neither significant demographics nor land areas difference between these two cities, so we consider these two cities as a valid comparison group and reopened Peterborough as the treatment group while maintaining Brantford shutdown as the control group.
+Besides, there is neither significant demographics nor land areas difference between these two cities, so we consider them as a valid comparison group and reopened Peterborough as the treatment group while maintaining Brantford shutdown as the control group.
 
@@
 
-## Limitations in Sampling Method
+## Concerns about Sampling Method
 
@@
 
-* The list of restaurants in Brantford and Peterborough may not be accurately represented on Yelp.
+* All restaurants in Brantford and Peterborough may not be accurately represented on Yelp.
 Some restaurants may not be registered on Yelp and some may not have updated their information on time.
 What is more, restaurants would only appear in the Yelp query when it has been reviewed by one of its users, which suggests that certain new restaurants may not be on the list.
-These limitations may result in the exclusion bias of our sample.
+These limitations may result in the exclusion bias of our frame population.
 
-* Since results of the first survey before implementing our experiment suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar **qualities**.
-However, the attributes of the restaurants (size, employments, service type, etc) were not controlled in our analysis.
+* Since results of the first survey before implementing our experiment suggest apparent similarities between restaurants in Peterborough and those in Brantford, we assume surveyed restaurants to have similar **qualities**.
+However, attributes of restaurants (capacity, employment, service type, etc) were not controlled in our analysis.
 In other words, we believe the response rate within the different restaurant subgroups to be the same.
-Variations in the actual response between restaurants in two cities are unknown and may impact the internal validity of the results.
+Variations in the actual response between restaurants in two cities are unknown and may impact the internal validity of results.
 
-* **The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations.
-Restaurants that lost their businesses during the pandemic could not be captured with the current method.
-However, these may be the ones that are most severely impacted.
-Another aspect of the survivorship bias involves the use of the same sampling frame for the presurvey and the formal survey.
-Since there is a three-month time lag, some restaurants may be closed during that time.**
+* Even though the size our sampled population is somehow small (100 restaurants each in Peterborough and Brantford), it has already captured more than half of our frame population (Therer are no more than 200 restaurants in each city).
+So we believe our sampling population could represent general characteristics of our frame population.
+
+* The sample suffered from survivorship bias as we only surveyed restaurants that were still in operations.
+Restaurants that lost their businesses during the pandemic before October in 2020 could not be captured with our intervention started in October, 2020, while these restaurants would be most impacted by the COVID shutdowns.
+Another aspect of the survivorship bias involves the use of the same frame population for the first survey and the second survey.
+The three-month intervention would also affect business operating situations of restaurants.
+And the decreased response rate of the second survey might also imply the survivorship bias of our experiment.
 
 * The sampling methods bore self-selection bias.
-From a psychological standpoint, respondents may have a stronger desire to respond to the survey if they have a strong opinion to express about their situations.
-The results showed that restaurant owners in Brantford faced a steeper sales decrease, and we expect that this may contribute to the higher survey response rate in Brantford.
+From a psychological standpoint, respondents may have a stronger desire to respond the survey if they have a strong opinion to express about their situations.
+Because of increasing of sales and  growing operation confidence during the intervention, respondents in Peterborough restaurants might be more willing to participate to our survey, leading to the higher response rate in Peterborough.
 
-* The accuracy of the responses may be hindered by the difficulties in reaching the management staff of restaurants.
+* The accuracy of responses may be hindered by difficulties in reaching the management staff of restaurants.
 The phone numbers scraped from Yelp was usually used for food ordering and the staff who picked up the phone may not know the sales status.
@@
 * Respondents may react differently in a phone interview compared to an online survey.
-The two methods may have the potential to produce significantly different results even when the two surveys have the same questions [@cite_surveycompare].
+These two methods may potentially produce significantly different results even when two surveys have same questions [@cite_surveycompare].
 People may be more comfortable answering a certain type of question online rather than by phone call, or vice versa.
 
-**High response rate:**
+* Compared to the average survey response rate around `33%` [@cite_responserate], the response rates of our surveys are relatively high (more than `50%` in the first survey and `40%` in the second survey).
+We credit our high response rates to efforts made in the following: (1) We spent a great amount of our budget to hire and train survey staffs to better approach our respondents.
+(2) We offered respondents chances to withdraw gift cards as incentives to answer our surveys.
+(3) We did not ask exact value of variables of our interest (e.g.
+Sales).
+Instead, we offer respondents several options to choose (e.g.
+`$0 ~ $10,000` ) so that respondents are more comfortable to participate in our survey.
 

### 2021-02-26 scripts/survey1_graphs.Rmd
Commit for modifications

@@
 #https://stackoverflow.com/questions/32593434/r-change-row-order
-tests <- simulated_survey1_dataset %>% 
+f_survey <- simulated_survey1_dataset %>% 
   summary_factorlist("q1_city", c("q3_category","q5_nature","q2_employees","q4_sales","q6_customers"),
@@
   ) #%>% 
- tests$q1_city <- NULL
-#  tests$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
- tests <- tests[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
-    mutate(group = c("Total Samples","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","",""))
+ f_survey$q1_city <- NULL
+#  f_survey$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
+ f_survey <- f_survey[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
+    mutate(` ` = c("Total Samples","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","",""))
 
-tests %>% 
+f_survey %>% 
   kable(
@@
   mutate(group = c("","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","","")) #%>%
-  kable( tests[,c(4,1,2,3)],caption = "TEST CAPTION",
+
+  kable( f_survey[,c(4,1,2,3)],caption = "Summary Statistics for First Survey",
          booktabs = TRUE,
-         valign='t')
-    ) %>% 
-  kable_styling()
+         valign='t'
+         ) 
+  #%>% 
+  #  kable_styling(latex_options = "hold_position", protect_latex = FALSE)
 

### 2021-02-26 scripts/04_get_restaurants_data.R

@@ -37,7 +37,7 @@ phoneNum <- vector()
 
 # Since each page only showed 50 results, and there are more resturuants in the two cities. We use "offset" to find all the records. 
 
-# Get all 133 restaurants in Peterborough
+# Get all 133 restaurants in Brantford
 for(n in seq(0, 133, 50)) {
   url <- modify_url(yelp, path = c("v3", "businesses", "search"),
                     query = list(term = term, location = Brantford_location, 

### 2021-02-26 scripts/06_simulate_first_survey_response.R

@@ -39,10 +39,10 @@ number_of_observation_P<-55
 peterborough_data<-tibble(
   q1_city=rep("Peterborough",number_of_observation_P),
   q2_employees=sample(x=c("Less than 5","5 -10","10 - 30","30 - 50","Prefer not to say"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.35,0.2,0.05,0.15)),
-  q3_category=sample(x=c("Fine Dining","Casual Dining"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.75)),
+  q3_category=sample(x=c("Fine dining","Casual dining"),size = number_of_observation_P,replace = TRUE,prob = c(0.25,0.75)),
   q4_sales=sample(x=c("$0 - $25,000","$25,000 - $50,000","$50,000 - $80,000","$80,000 - $110,000","$110,000 - $150,000","$150,000 or above","Prefer not to say"),
                   size = number_of_observation_P,replace = TRUE,prob = c(0.22,0.3,0.15,0.1,0.03,0.0,0.2)),
-  q5_nature=sample(x=c("Table-service restaurant","Quick-service restaurant"),size = number_of_observation_P,replace = TRUE, prob = c(0.5,0.5)),
+  q5_nature=sample(x=c("Table-service","Quick-service"),size = number_of_observation_P,replace = TRUE, prob = c(0.5,0.5)),
   q6_customers=sample(x=c("Less than 10","10 - 20","20 - 40","40 -70","70 -100","More than 100","Prefer not to say"),size = number_of_observation_P,replace = TRUE,
                       prob = c(0.1,0.25,0.32,0.1,0.08,0,0.15))
 )
@@ -56,10 +56,10 @@ number_of_observation_B<-50
 Brantford_data<-tibble(
   q1_city=rep("Brantford",number_of_observation_B),
   q2_employees=sample(x=c("Less than 5","5 -10","10 - 30","30 - 50","Prefer not to say"),size = number_of_observation_B,replace = TRUE,prob = c(0.25,0.35,0.2,0.05,0.15)),
-  q3_category=sample(x=c("Fine Dining","Casual Dining"),size = number_of_observation_B,replace = TRUE,prob = c(0.30,0.70)),
+  q3_category=sample(x=c("Fine dining","Casual dining"),size = number_of_observation_B,replace = TRUE,prob = c(0.30,0.70)),
[…]

### 2021-02-26 scripts/08_create_graphs_in_paper.R

@@ -77,6 +77,7 @@ data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
 
 # Referenced the following link to reorder responses
 #https://www.r-graph-gallery.com/267-reorder-a-variable-in-ggplot2.html
+
 # Question4 How was your total sales volume during Oct to Dec 2020 compared to July to Sept 2020?
 
 q4_table <- data.frame(table(simulated_dataset$q4_total_sales,simulated_dataset$q1_city))
@@ -112,7 +113,7 @@ q5_table%>%
   guides(fill=guide_legend(title="City"))+
   coord_flip()
 
-# Question 8: 8. If current conditions continue, how long do you expect your business to survive before you will have to close down permanently?
+# Question 8. If current conditions continue, how long do you expect your business to survive before you will have to close down permanently?
 
 data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
   mutate(Var1 = fct_relevel(Var1 ,"Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
@@ -141,7 +142,7 @@ data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulat
   guides(fill=guide_legend(title="City"))+
   coord_flip()
 
-# Question 11. To what extent do you feel the government financial support programs helped your business survive? (1 being bad, 5 being excellent.)
+# Question 11. To what extent do you feel the government financial support programs helped your business survive? (1 being terrible, 5 being excellent.)
 
 simulated_dataset %>%
   tabyl(q1_city, q11_rate_support)%>%
@@ -162,11 +163,24 @@ data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
   ggplot(aes(Var1, Freq,fill=Var2)) +
   geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
   ylab("Number of responses")+
-  xlab("Grant value")+
+  xlab("Loan value")+
   ggtitle("How much loans have you received for the COVID-19 related reasons?")+
   guides(fill=guide_legend(title="City"))+
   theme_minimal()+
   theme(axis.text.x = element_text(angle = 0))+
   coord_flip()
 
[…]

### 2021-02-26 outputs/paper/paper.Rmd
Commit for README and formatting

@@
 ```{r setup, include=FALSE}
-# May install the following displaying tables
+# May install the following to display tables
 # Reference: https://bookdown.org/yihui/bookdown/html-widgets.html
@@
 
-&nbsp; &nbsp; The first survey was conducted before the decision on intervention to ensure our assumptions about restaurant similarities between Peterborough and Brantford are based on concert evidence.
+&nbsp; &nbsp; The first survey was conducted before the decision on intervention to ensure our assumptions about restaurant similarities between Peterborough and Brantford.
 We asked selected respondents about the restaurants' employment, average monthly sales, nature and category of restaurant, restaurant capacity to examine restaurant similarities between these two cities.
@@
 And among which, 7 were collected via the online survey in Brantford and 8 were collected via the online survey in Peterborough.
-Surveys that were not answered or have incomplete answers were treated as nonresponses and were not included in the dataset for further analysis^[Exception for Question 6 of the first survey, which respondents could skip the question].
+Online surveys with no or incomplete answers were treated as nonresponses and were not included in the dataset for further analysis^[Exception for Question 6 of the first survey, which respondents could skip the question].
 The survey was administered in following steps:
@@
 2.
-Working from 2 pm to 4 pm, half of the survey staff called the Brantford restaurants, and the other half called the Peterborough restaurants simultaneously to avoid sampling bias.
+Working from 2 pm to 4 pm, half of survey staffs called the Brantford restaurants, and the other half called the Peterborough restaurants simultaneously.
 Each phone call took around 15 minutes to complete.
@@
 (2) Effects of the government support during the intervention.
-Respondents answered survey questions based on the intervention period.
+Respondents answered survey questions based on business situations during the intervention period.
 Several key findings are discussed in the following:
@@
 
-&nbsp; &nbsp; In contrast, continuing shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for those restaurants.
+&nbsp; &nbsp; In contrast, continuing shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for these restaurants.
 We propose possible reasons for the decrease in restaurant sales: (1) Residents in Brantford changed their mealing behaviors to cook more by themselves, instead of relying on meals from restaurants.
-(2) The continuing shutdown resulted in closures of other businesses, so these business staffs were not contributing for the restaurant sales anymore.
+(2) The continuing shutdown resulted in closures of other businesses, so these business staffs were not contributing for restaurant sales anymore.
 (3) There exists some seasonal fluctuations on food service industries.
@@
 Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
-So we consider the increased cost in restaurants during the reopening period as a good signal for economic wellbeing.
+So we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
 
-&nbsp; &nbsp; The figure (\@ref(fig:q8)) shown below illustrates respondents' opinions towards the expected survivability of their businesses.
+&nbsp; &nbsp; Figure \@ref(fig:q8) shown below illustrates respondents' opinions towards the expected survivability of their businesses.
 It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during this continuing shutdown period.
@@
 
-&nbsp; &nbsp; In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) show that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, hold negative views to recover back to pre-COVID operating situation in a short period of time.
+&nbsp; &nbsp; In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) show that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, hold negative views to recover back to pre-COVID operating situation in a short period.
 For restaurants in Peterborough, despite some suspicions to recoup with the pre-COVID situation in more than a year, most of them expected to recovery in less than a year.
@@
 Since loans have to be paid back, businesses at low operating confidence are less likely to apply for loans.
-With increased business opportunities after reopening, respondents were more likely to invest for faster recovery, and this corresponds with our previous findings of longer expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) in Peterborough restaurants as mentioned before.
+With increased business opportunities after reopening, restaurant owners were more likely to invest for faster recovery, and this corresponds with our previous findings of longer expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) in Peterborough restaurants as mentioned before.
 
@@
 
-In contrast, restaurants in Brantford generally receives more grants than those in Peterborough(Figure \@ref(fig:q14)).
+In contrast, restaurants in Brantford generally receives more grants than those in Peterborough(Figure \@ref(fig:q15)).
 Since grants are non-repayable funds and need certain conditions to apply, restaurants in Peterborough with better business conditions may not be eligible to apply for grants.
-And restaurants that suffers more in Brantford could receive more grants during the shutdown.
+And restaurants that suffer more in Brantford could receive more grants during the shutdown.
 
@@
 
-* Our survey found that restaurants in Peterborough had lower layoff compared to those in Brantford, suggesting that reopening restaurants may lead to more employment in the industry. 
+* Our survey found that restaurants in Peterborough had lower layoffs compared to those in Brantford, suggesting that reopening restaurants may lead to more employment in the industry. 
 *	Policy implications: The Ontario government should continue existing supports to restaurants during the lockdown and consider additional support measures to mitigate the risk of increased unemployment.
@@
 
-* Since results of the first survey before implementing our experiment suggest apparent similarities between restaurants in Peterborough and those in Brantford, we assume surveyed restaurants to have similar **qualities**.
+* Since results of the first survey before implementing our experiment suggest apparent similarities between restaurants in Peterborough and those in Brantford, we assume surveyed restaurants to have similar qualities.
 However, attributes of restaurants (capacity, employment, service type, etc) were not controlled in our analysis.
@@
 We credit our high response rates to efforts made in the following: (1) We spent a great amount of our budget to hire and train survey staffs to better approach our respondents.
-(2) We offered respondents chances to withdraw gift cards as incentives to answer our surveys.
+(2) We offered respondents chances to withdraw gift cards as incentives to participate our surveys.
 (3) We did not ask exact value of variables of our interest (e.g.
@@
 ```
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+
+&nbsp; &nbsp;
+&nbsp; &nbsp;
+&nbsp; &nbsp;
+&nbsp; &nbsp;
+&nbsp; &nbsp;
+&nbsp; &nbsp;
+&nbsp; &nbsp;
+&nbsp; &nbsp;
 

### 2021-02-27 outputs/paper/paper.Rmd
Proofreading

@@
 author: "Hong Shi, Hong Pan, Yixin Guan, Babak Mokri"
-date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "Due to the world-wide COVID-19 pandemic, shutdown restrictions on businesses and facilities have limited economic activities into a recession.
-This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months reopening.
-The survey result indicates that shutdown restrictions have negative impacts on restaurant employment, sales and operating confidence.
-However, the higher increased COVID cases in the reopened city sugguests the Ontario government to mindfully plan for futher policy decisions."
+date: "February 26 2021"
+abstract: "Due to the world-wide COVID-19 pandemic, shutdown restrictions on businesses and facilities have limited economic activities.
+This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months.
+The survey results indicate that shutdown restrictions have negative impacts on restaurant employment, sales and operating confidence.
+However, the more drastic increase in COVID-19 positive cases in the reopened city suggests the Ontario government to be conservative for further policy decisions."
 output:
@@
 We conducted an experiment by selecting two single tier cities, namely Peterborough and Brantford, ^[Ontario's Municipal Act, 2001 defines a single-tier municipality as "a municipality, other than an upper-tier municipality, that does not form part of an upper-tier municipality for municipal purposes"] with similar restaurant operating situations in Ontario and investigated how reopening the dine-in services for restaurants in Peterborough has prevailed over the state of continued shutdown in Brantford through surveys.
-The results showed that continuing shutdown has negatively impact the employment, sales volume and operating confidence on restaurant businesses in Brantford.
+The results showed that the reopening policy has positively impacted the employment, sales volume and operating confidence on restaurant businesses in Peterborough.
 In addition, the governmental support programs contributed substantially to restaurant businesses in both reopened and shutdown cities.
-However, the higher increased COVID cases in Peterborough demonstrates the drawback of the reopening, and the Ontario government should hold a clear measure between public health and economic recovery before further policy implementations.
+However, the more drastic increase in the COVID-19 positive cases in Peterborough demonstrated the public health concerns of the reopening, and the Ontario government should strike a balance between public health and economic recovery in further policy decisions.
 
@@
 And then, we discuss main findings from survey results.
-In Discussion section, we would elaborate on concerns about the intervention on city selections, sampling methods and survey methodologies.
+In Discussion section, we elaborate on concerns about the intervention on city selections, sampling methods and survey methodologies.
 And we also propose our thoughts on further policy implications.
@@
 
-&nbsp; &nbsp; Partnered with the Ontario government, we want to examine the shutdown effects on restaurant businesses in Ontario.
-The plan of the experimental design was to reopen all restaurants (i.e.
-enable the dine-in option) in particular Ontario regions, while enforcing current provincewide shutdown restrictions (i.e.
-disable the dine-in option) on restaurants in the rest of Ontario regions.
+&nbsp; &nbsp; We want to examine the shutdown effects on restaurant businesses in Ontario.
+The plan of the experimental design was to reopen all restaurants (i.e., enable the dine-in option) in particular Ontario regions, while enforcing current provincewide shutdown restrictions (i.e., disable the dine-in option while enable the take-out option) on restaurants in the rest of Ontario regions.
 And after the three-month reopening, we compare restaurant operating situations in reopened regions with those in shutdown regions through data collected from online surveys of restaurant owners.
 
-&nbsp; &nbsp; However, due to current COVID pandemic, any loosening of shutdown restrictions increases chances of COVID exposures, resulting in challenges on public health and healthcare of reopened regions.
+&nbsp; &nbsp; However, due to the current COVID-19 pandemic, any loosening of shutdown restrictions increases chances of COVID exposures, resulting in challenges on public health and safety of reopened regions.
 It is highly risky and hasty to reopen a large area of Ontario regions for the sole purpose of our experiment.
-Therefore, we mindfully chose Peterborough, a relative small size Single-tier city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario and then compared its restaurant operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
+Therefore, we mindfully chose Peterborough, a relatively small size Single-tier city 125 kilometers northeast of Toronto, as the only region to reopen in Ontario.
+We compared Peterborough's restaurants operating situations with those in Brantford, another Single-tier city 105 kilometers southwest of Toronto with similar population.
 Since demographics, land areas and more importantly, restaurant operating situations between these two cities are quite similar with each other^[Approaches to select these two cities are further introduced in the discussion section], we consider these two cities as valid comparison cities that could yield an accurate estimate of restaurant businesses shutdowns.
 In our experiment, we assigned restaurants in Peterborough as the treatment group and those in Brantford as the control group.
-We also ensured restaurants within these two cities to have equal opportunities receiving government support (e.g.
-subsidies, grants, etc.) to estimate the true impact of shutdown effects on restaurant businesses after three-month reopening in Peterborough.
+We also ensured restaurants within these two cities to have equal eligibilities to receive government supports with certain conditions(e.g.
+subsidies, grants, etc.) to estimate the real impact of shutdown effects on restaurant businesses after three-month reopening in Peterborough.
 
-&nbsp; &nbsp; In September, 2020, we at Petit Poll conducted the first survey on restaurants in Peterborough and Brantford to examine their business conditions before the experiment.
-Starting from October, 2020, the Ontario government reopened Peterborough while keeping shutdown restrictions on the rest of Ontario regions.
-After a three month period in January 2021, we at Petit Poll started to conduct survey on restaurants in Peterborough and Brantford about their business performance from October to December.
+&nbsp; &nbsp; In September 2020, Petit Poll conducted the first survey on restaurants in Peterborough and Brantford to examine their business conditions before the experiment.
+Starting from October 2020, the Ontario government reopened Peterborough while keeping shutdown restrictions on the rest of Ontario regions.
+After a three-month period in January 2021, Petit Poll started to conduct survey on restaurants in Peterborough and Brantford about their business performance from October to December 2020.
 Survey results were released in February 2021.
@@
 
-&nbsp; &nbsp; As we would like to understand the effect of COVID shutdowns on restaurant businesses in Ontario, we considered all restaurants in Ontario as our target population.
-According to our intervention, the frame population are all restaurants in Peterborough and Brantford.
+&nbsp; &nbsp; As we would like to understand the effect of COVID shutdown on restaurant businesses in Ontario, we considered all restaurants in Ontario as our target population.
+The frame population are all restaurants in Peterborough and Brantford.
 We used the following approaches to obtain the sampled population as below:
@@
 1.
-Scrape postal codes of all restaurants located within the circle of the Brantford City Centre to a 40 km radius on Yelp.
-And then apply the same method for Peterborough.^[Land areas of both Brantford and Peterborough are less than 100 kilometer squares, so searching restaurants 40 km within the city center almost ensures to include all restaurants in Peterborough and Brantford]
+Scraped postal codes of all restaurants located within the circle of the Brantford City Centre to a 40 km radius on Yelp.
+And then applied the same method for Peterborough.^[Land areas of both Brantford and Peterborough are less than 100 kilometer squares, so searching restaurants 40 km within the city center almost ensures to include all restaurants in Peterborough and Brantford]
 
-2. Acquire a list of postal codes in Brantford CMA and Peterborough CMA from the Postal Code Conversion File (PCCF) retrieved from the University of Toronto Library[@cite_uoftlibrary].
+2. Acquired a list of postal codes in Brantford and Peterborough from the Postal Code Conversion File (PCCF) retrieved from the University of Toronto Library[@cite_uoftlibrary].
 
-3.
-Compare these two lists and eliminate restaurants with postal codes outside of Peterborough CMA and Brantford CMA to get the list of all restaurants in Brantford and Peterborough as the frame population.
+3. Compared these two lists and eliminate restaurants with postal codes outside of Peterborough and Brantford to get the list of all restaurants in Brantford and Peterborough as the frame population.
 
-4. Randomly select 100 restaurants from Brantford and 100 restaurants from Peterborough to form the sampled population.
+4. Randomly selected 100 restaurants from Brantford and 100 restaurants from Peterborough to form the sampled population.
 
 &nbsp; &nbsp; The first survey was conducted before the decision on intervention to ensure our assumptions about restaurant similarities between Peterborough and Brantford.
-We asked selected respondents about the restaurants' employment, average monthly sales, nature and category of restaurant, restaurant capacity to examine restaurant similarities between these two cities.
+We asked respondents about the restaurants' employment, average monthly sales, nature and category of restaurant, restaurant capacity to examine restaurant similarities between these two cities.
 
@@
 The telephone interview served as the primary channel and an online survey option was provided when respondents could not or prefer not to be interviewed over the phone.
-As shown in the above table (Table \@ref(tab:presamplingtable)), our sampled population included 50 valid responses in Brantford and 55 in Peterborough.
-And among which, 7 were collected via the online survey in Brantford and 8 were collected via the online survey in Peterborough.
+As shown in the above table (Table \@ref(tab:presamplingtable)), our sampled population included 50 valid responses in Brantford and 55 in Peterborough.Among which, 7 were collected via online surveys in Brantford and 8 in Peterborough.
 Online surveys with no or incomplete answers were treated as nonresponses and were not included in the dataset for further analysis^[Exception for Question 6 of the first survey, which respondents could skip the question].
@@
 If the respondent answered no, the survey staff would ask the caller to pass the call to the relevant staff in the restaurant.
-If that staff was not available, the survey staff will schedule another call or provide the online questionnaire based on the preference identified by the respondent.
+If that staff was not available, the survey staff would schedule another call or provide the online questionnaire based on the preference identified by the respondent.
 Respondents who were interested in answering questions via online questionnaires could leave their email addresses and have two weeks to complete survey questions.
@@
 ```
-&nbsp; &nbsp; From the summary statistics of the first survey as shown above (Table \@ref(tab:survey1), values inside the bracket represent percentage), we find that the distribution of category, nature, number of employees, average monthly sales and capacity of restaurants is closely identical between Peterborough and Brantford.
-These results confirm our initial assumptions that restaurants in these two cities are similar enough to implement our intervention of reopening the Peterborough.
+&nbsp; &nbsp; From the summary statistics of the first survey as shown above (Table \@ref(tab:survey1), values inside the bracket represent percentage), we found that the distribution of category, nature, number of employees, average monthly sales and capacity of restaurants was similar between Peterborough and Brantford.
+These results confirm our initial assumptions that restaurants in these two cities are similar enough to implement our intervention of reopening Peterborough.
 
@@
 &nbsp; &nbsp; The second survey examined two parts of our interests: (1) Effects of the intervention on restaurant business conditions.
-(2) Effects of the government support during the intervention.
+(2) Effects of the the intervention on restaurants' dependency on government supports.
 Respondents answered survey questions based on business situations during the intervention period.
@@
 
-&nbsp; &nbsp; Compared to Peterborough, restaurants in Brantford have much higher number of layoffs (Figure \@ref(fig:question3)), suggesting that the continuing shutdown greatly affected the employment situation in Brantford.
-In Peterborough, there are considerable amount of restaurants with no layoffs, implying that restaurants would require certain number of staffs to operate the dine-in service after reopening.
+&nbsp; &nbsp; Compared to Peterborough, restaurants in Brantford had much higher number of layoffs (Figure \@ref(fig:question3)), suggesting that the continuing shutdown greatly affected the employment situation in Brantford.
+In Peterborough, there were considerable number of restaurants with no layoffs, possibly because restaurants required staffs to operate the dine-in service after reopening.
 
@@
 ```
-&nbsp; &nbsp; From Figure \@ref(fig:q4), we notice a considerable increase in sales in Peterborough during the reopen period.
-This indicated that if restaurants were open, people would had used their dine-in services, regardless of potential pandemic risks.
+&nbsp; &nbsp; From Figure \@ref(fig:q4), we noticed a considerable increase in sales in Peterborough during the reopen period.
+This indicated that when restaurants opened, some people would have used their dine-in services, regardless of potential pandemic risks.
 
-&nbsp; &nbsp; In contrast, continuing shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for these restaurants.
-We propose possible reasons for the decrease in restaurant sales: (1) Residents in Brantford changed their mealing behaviors to cook more by themselves, instead of relying on meals from restaurants.
-(2) The continuing shutdown resulted in closures of other businesses, so these business staffs were not contributing for restaurant sales anymore.
+&nbsp; &nbsp; In contrast, continued shutdown restrictions during October to December on Brantford resulted in a slight decrease in sales volume for these restaurants.
+Possible reasons for the decrease in restaurant sales included: (1) Residents in Brantford changed their preferences to cook more by themselves, instead of relying on meals from restaurants.
+(2) The continued shutdown resulted in closures of other businesses, therefore, minimizing their customer volume.
 (3) There exists some seasonal fluctuations on food service industries.
+People were more likely to stay at home when the weather was cold.
 
@@
 
-&nbsp; &nbsp; Increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.
-This change admits that restaurants would have preserved more of their staff and consumed more utility or housekeeping materials to maintain their dine-in area.
-Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs generate economic flow into local society and are vital for other business sectors to survive.
-So we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
+&nbsp; &nbsp; Increased costs of restaurants in Peterborough, as shown in Figure \@ref(fig:q5), demonstrated more activities in their restaurants.We expect the cost increase would likely be variable cost.
+This change suggested that restaurants would have spent more in hiring staff, utilities or housekeeping materials to maintain their dine-in area.
+Although increased operating cost would usually impact the business unit negatively, from a broader view, these costs could generate economic flow into local society and are vital for other business sectors to survive.
+Therefore, we consider the increased cost in restaurants during the reopening period as a good signal of economic wellbeing.
 
 &nbsp; &nbsp; Figure \@ref(fig:q8) shown below illustrates respondents' opinions towards the expected survivability of their businesses.
-It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during this continuing shutdown period.
-While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.
+Restaurants in Brantford were not as positive to continue their businesses for longer times, indicating a stressful operating situation during this continuing shutdown period.
+While on the other hand, restaurants in Peterborough generally expected to survive longer, showing stronger confidence to continue their businesses after the pandemic.
 
@@
 
-&nbsp; &nbsp; In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) show that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, hold negative views to recover back to pre-COVID operating situation in a short period.
+&nbsp; &nbsp; In addition, survey results about expected recovery time back to pre-COVID situation (Figure \@ref(fig:q10)) showed that even if the pandemic ends immediately, most restaurants in Brantford, especially quick-service restaurants, would hold negative views to recover back to pre-COVID operating situation in a short period.
 For restaurants in Peterborough, despite some suspicions to recoup with the pre-COVID situation in more than a year, most of them expected to recovery in less than a year.
-Therefore, we believe that the continuing shutdown in Brantford have harmed expectations of future operation possibilities in Brantford, while the reopening in Peterborough could build confidence to alleviate current operation difficulties.
+Therefore, we believe that the continuued shutdown in Brantford had harmed the business confidence of Brantford restaurants, while the reopening in Peterborough built confidence to alleviate current operation difficulties.
 
@@
 &nbsp; &nbsp; As agents to gather relevant feedbacks for the Ontario Government, we asked respondents' opinions towards the helpfulness of government financial support programs.
-Survey results (Table \@ref(tab:q11)) show that both cities generally treat support programs as helpful, especially in Brantford where the shutdown restriction was still implementing.
-From previous gloom results on restaurant business conditions, it is not a surprise that restaurants in Brantford require more government financial supports.
+Survey results (Table \@ref(tab:q11)) showed that both cities generally considered support programs helpful, especially in Brantford where the shutdown restriction was still being  implemented.
+From previous gloom results on restaurants' business conditions, it is not a surprise that restaurants in Brantford required more government financial supports.
 
@@
   tabyl(q1_city, q11_rate_support)%>%
-  adorn_totals("row", name = "Average")%>%
+  adorn_totals("row", name = "Total")%>%
   adorn_percentages("row")%>%
@@
 
-As shown in Figure \@ref(fig:q14), restaurants in Peterborough have applied more business loans than those in Brantford during the intervention.
-Since loans have to be paid back, businesses at low operating confidence are less likely to apply for loans.
+As shown in Figure \@ref(fig:q14), restaurants in Peterborough had applied more business loans than those in Brantford during the intervention.
+Since loans have to be paid back, businesses with low operating confidence were less likely to apply for loans.
 With increased business opportunities after reopening, restaurant owners were more likely to invest for faster recovery, and this corresponds with our previous findings of longer expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) in Peterborough restaurants as mentioned before.
@@
 
-In contrast, restaurants in Brantford generally receives more grants than those in Peterborough(Figure \@ref(fig:q15)).
-Since grants are non-repayable funds and need certain conditions to apply, restaurants in Peterborough with better business conditions may not be eligible to apply for grants.
-And restaurants that suffer more in Brantford could receive more grants during the shutdown.
+In contrast, restaurants in Brantford generally received more grants than those in Peterborough(Figure \@ref(fig:q15)).
+Since grants are non-repayable funds and require certain conditions to apply, restaurants in Peterborough with better business conditions may not be eligible to apply for grants.
+And restaurants that suffered more in Brantford could receive more grants during the shutdown.
 
@@
 
-To obtain an accurate estimate of the shutdown effect on restaurant businesses, average characteristics of restaurants in the reopening city and those in the shutdown city need to be identical in the absence of the reopen intervention under current COVID outbreak.
-Since businesses in the food service industry are highly labor intensive [@cite_labor], the `total employment` on food service between selected cities is preferred to be equal as the identical characteristic.
+To obtain an accurate estimate of the shutdown effect on restaurant businesses, average characteristics of restaurants in the reopening city and those in the shutdown city need to be identical (in theory) in the absence of the reopen intervention under current COVID outbreak.
+Since businesses in the food service industries are highly labor intensive [@cite_labor], the `total employment` in food service industries between selected cities is preferred to be as identical as possible.
 Besides, `population density` ( `Total Population`/ `Total Land Area in squared kilometers`) also has significant organizational life-cycle effects[@cite_density].
 At different population density levels, competitions for food services varies, leading to different restaurants mortality rates even without the reopen intervention.
-As a result, total employment on food service and population density serve as primary restaurant operation characteristics for the selection of treatment city and control city.
+As a result, total employment in food service and population density serve as the two primary restaurant operation characteristics for the selection of treatment city and control city.
 
@@
 
-We used the employment by industry data and 2016 Census data available at Statistics Canada to identify cities with similar total employment on food service and population density.
-The above point graph(Figure \@ref(fig:selectplot)) indicates that Brantford and Peterborough have similar characteristics affecting restaurant operations.
+We used the employment by industry data and 2016 Census data available at Statistics Canada to identify cities with similar total employment in food service industry and population density.
+The above point graph(Figure \@ref(fig:selectplot)) indicated that Brantford and Peterborough have similar characteristics affecting restaurant operations.
 In addition, the coefficient of the graph $$\frac{Population\:Density}{Total \:Employment}=\frac{Total\:Population/Total\:Land\:Area}{Total\:Employment}$$, which could be interpreted as the number of people served by a restaurant employee per square kilometers, helps to identify the restaurant operating situation in designated regions.
@@
 So there is less employment in food services.
-We took the convention that the ratio between the accommodation employment and the food service employment between Peterborough and Brantford is the same.
+We assume that the ratios between the accommodation employment and the food service employment between Peterborough and Brantford are the same.
 
@@
 However, residents in shutdown regions near Peterborough might go for dine-in meals, potentially increasing sales in Peterborough restaurants.
-The actual shutdown effect on restaurants could be overestimated due to possible increase in sales from nearby shutdown regions' residents.
+The actual reopening effect on restaurants could be overestimated due to possible increase in sales from nearby shutdown regions' residents that would not sustain once the reopen expanded to all Ontario regions.
 
@@
 ensures the internal validity of our experiment so that we could accurately estimate the true impact of shutdown restrictions on restaurant.
-However, our shutdown effect evaluations may not be generalized to the entire population of interest, i.e.
-all restaurants in Ontario such as township regions or cosmopolitan city Toronto due to different levels of competitions, operating costs, etc.
+However, our shutdown effect evaluations may not be generalized to the entire population of interest, i.e., all restaurants in Ontario such as township regions or cosmopolitan city Toronto due to different levels of competitions, operating costs, etc.
 
@@
 However, attributes of restaurants (capacity, employment, service type, etc) were not controlled in our analysis.
-In other words, we believe the response rate within the different restaurant subgroups to be the same.
+In other words, we assume the response rate within the different restaurant subgroups to be the same.
 Variations in the actual response between restaurants in two cities are unknown and may impact the internal validity of results.
 
-* Even though the size our sampled population is somehow small (100 restaurants each in Peterborough and Brantford), it has already captured more than half of our frame population (Therer are no more than 200 restaurants in each city).
-So we believe our sampling population could represent general characteristics of our frame population.
+* Even though the size of our sampled population is somehow small (100 restaurants each in Peterborough and Brantford), it has already captured more than half of our frame population (There are no more than 200 restaurants in each city).
+So we believe our sampling population could represent the general characteristics of our frame population.
 
 * The sample suffered from survivorship bias as we only surveyed restaurants that were still in operations.
-Restaurants that lost their businesses during the pandemic before October in 2020 could not be captured with our intervention started in October, 2020, while these restaurants would be most impacted by the COVID shutdowns.
+Restaurants that lost their businesses during the pandemic before October in 2020 could not be captured with our intervention started in October 2020, while these restaurants would be the most impacted by the COVID shutdowns.
 Another aspect of the survivorship bias involves the use of the same frame population for the first survey and the second survey.
@@
 From a psychological standpoint, respondents may have a stronger desire to respond the survey if they have a strong opinion to express about their situations.
-Because of increasing of sales and  growing operation confidence during the intervention, respondents in Peterborough restaurants might be more willing to participate to our survey, leading to the higher response rate in Peterborough.
+Because of increasing sales and growing operation confidence during the intervention, respondents in Peterborough restaurants might be more willing to participate to our survey, leading to the higher response rate in Peterborough.
 
@@
 
-* Compared to the average survey response rate around `33%` [@cite_responserate], the response rates of our surveys are relatively high (more than `50%` in the first survey and `40%` in the second survey).
+* Compared to the average survey response rate around `33%` [@cite_responserate], the response rates of our surveys are relatively higher (more than `50%` in the first survey and `40%` in the second survey).
 We credit our high response rates to efforts made in the following: (1) We spent a great amount of our budget to hire and train survey staffs to better approach our respondents.
 (2) We offered respondents chances to withdraw gift cards as incentives to participate our surveys.
-(3) We did not ask exact value of variables of our interest (e.g.
+(3) We did not ask exact value of queation of our interest (e.g.
 Sales).

### 2021-02-27 scripts/08_create_graphs_in_paper.R

@@ -146,15 +146,20 @@ data.frame(table(simulated_dataset$q10_recover,simulated_dataset$q1_city,simulat
 
 simulated_dataset %>%
   tabyl(q1_city, q11_rate_support)%>%
-  adorn_totals("row")%>%
-  adorn_totals("col")%>%
+  adorn_totals("row", name = "Total")%>%
   adorn_percentages("row")%>%
   adorn_pct_formatting(digits=2)%>%
   adorn_ns()%>%
   adorn_title("combined",row_name = "City", col_name = "Rating")%>%
-  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
-  kable_styling(full_width = F)
-
+  rename(
+    `Terrible` = `1`,
+    `Poor` = `2`,
+    `Fair` = `3`,
+    `Good` = `4`,
+    `Excellent` = `5`
+  ) %>% 
+  kable(align = 'ccccccc', caption = 'Helpfulness of Government Financial Support Programs on Restaurants') %>% 
+  kable_styling(latex_options = "hold_position")
 
 # Question 14 How much loans have you received for the COVID-19 related reasons ?
 

### 2021-03-01 scripts/04_get_restaurants_data.R
Commit for Yelp token

@@ -19,8 +19,7 @@ library(xml2)
 
 # In order to make an request using Yelp API, a Yelp developer account and a API Key have to be created. 
 
-token <- "shSjf2t4b6wdrVtwf4kGvhZtOkR5c01gStUBs5S4In7dU5heYqd0eIymikqX2v-xN7OEqY_AgfZ0d9CvXGVj5nUYAZ7A9rWjGOtL7qu6H5RlnrQaW_zuYMbTb7opYHYx"
-
+token <- "Please enter your own token here"
 # Setup for searching restaurants in Brantford, Ontario
 
 yelp <- "https://api.yelp.com"

### 2021-03-03 outputs/paper/paper.Rmd
Commit for minor modifications

@@
 
-As shown in Figure \@ref(fig:q14), restaurants in Peterborough had applied more business loans than those in Brantford during the intervention.
+&nbsp; &nbsp; As shown in Figure \@ref(fig:q14), restaurants in Peterborough had applied more business loans than those in Brantford during the intervention.
 Since loans have to be paid back, businesses with low operating confidence were less likely to apply for loans.
@@
 
-In contrast, restaurants in Brantford generally received more grants than those in Peterborough(Figure \@ref(fig:q15)).
+&nbsp; &nbsp; In contrast, restaurants in Brantford generally received more grants than those in Peterborough(Figure \@ref(fig:q15)).
 Since grants are non-repayable funds and require certain conditions to apply, restaurants in Peterborough with better business conditions may not be eligible to apply for grants.
@@
 
-To obtain an accurate estimate of the shutdown effect on restaurant businesses, average characteristics of restaurants in the reopening city and those in the shutdown city need to be identical (in theory) in the absence of the reopen intervention under current COVID outbreak.
+&nbsp; &nbsp; To obtain an accurate estimate of the shutdown effect on restaurant businesses, average characteristics of restaurants in the reopening city and those in the shutdown city need to be identical (in theory) in the absence of the reopen intervention under current COVID outbreak.
 Since businesses in the food service industries are highly labor intensive [@cite_labor], the `total employment` in food service industries between selected cities is preferred to be as identical as possible.
@@
 
-We used the employment by industry data and 2016 Census data available at Statistics Canada to identify cities with similar total employment in food service industry and population density.
+&nbsp; &nbsp; We used the employment by industry data and 2016 Census data available at Statistics Canada to identify cities with similar total employment in food service industry and population density.
 The above point graph(Figure \@ref(fig:selectplot)) indicated that Brantford and Peterborough have similar characteristics affecting restaurant operations.
-In addition, the coefficient of the graph $$\frac{Population\:Density}{Total \:Employment}=\frac{Total\:Population/Total\:Land\:Area}{Total\:Employment}$$, which could be interpreted as the number of people served by a restaurant employee per square kilometers, helps to identify the restaurant operating situation in designated regions.
+In addition, the coefficient of the graph, $$\frac{Population\:Density}{Total \:Employment}=\frac{Total\:Population/Total\:Land\:Area}{Total\:Employment}$$ which could be interpreted as the number of people served by a restaurant employee per square kilometers, helps to identify the restaurant operating situation in designated regions.
 Similar coefficients between Brantford and Peterborough (0.306 vs 0.308) also suggest close restaurant characteristics.
@@
 
-Link to access the first survey about restaurant business conditions conducted in September, 2020:
+&nbsp; &nbsp; Link to access the first survey about restaurant business conditions conducted in September, 2020:
 https://docs.google.com/forms/d/1Bl8CbJiN8sUbhsDdnzqP4ifIyE9KT8iJgYI9ldcR2g8
@@
 
-Link to access the second survey about impact of COVID-19 on restaurants conducted in January, 2021:
+&nbsp; &nbsp; Link to access the second survey about impact of COVID-19 on restaurants conducted in January, 2021:
 https://docs.google.com/forms/d/1FXSeKFkvCtM41k9xFYjQQ_eDGdBs9skVYZ3zU5LNRgY
